### 2024-12-10 manuscript.qmd
Prepare template

---
title: House price data in Brunei
authors:
  - name: Haziq Jamil
    orcid: 0000-0003-3298-1010
    email: haziq.jamil@ubd.edu.bn
    url: "https://haziqj.ml"
    # note: 
    # roles: writing
    corresponding: true
    affiliations:
      - name: Universiti Brunei Darussalam
        id: ubd
        department: Mathematical Sciences, Faculty of Science
        address: Universiti Brunei Darussalam, Jalan Tungku Link
        city: Bandar Seri Begawan
        country: Brunei
        postal-code: BE 1410
  - name: Hafeezul Waezz Rabu
    affiliations:
      - ref: ubd
  - name: Amira Barizah Noorosmawie
    affiliations:
      - ref: ubd
  - name: Lutfi Abdul Razak
    affiliations:
      - ref: ubd              
date-modified: last-modified
nocite: |
  @*
abstract: |
  Abstract here.
---

## References {.unnumbered}

:::{#refs}
:::

### 2024-12-10 manuscript.qmd
Update manuscript.qmd

@@
 
+> Data articles describe research data that the authors have made publicly available through a repository.
+These articles ensure that raw data, which is often buried in supplementary material, is peer-reviewed, curated, formatted, indexed, given a DOI and made publicly available upon publication.
+All data articles must link to a repository that stores data produced and owned by either the author or the author's institution.
+Since data articles are templated, we require that you complete and submit the template.
+Data in Brief will not accept any submissions that contain datasets with insufficient variables or samples.
+
+# Value of the Data
+
+This section states why these data are of value to the scientific community.
+Please provide between 3 and 6 bullet points and answer at least the questions below (delete the questions afterwards).
+Each bullet point should be a maximum of 150 words long, and should not include conclusions or inferences:
+
+- Why are these data valuable?
+- How can these data be reused by other researchers?
+- ...
+
+# Background
+
+Please describe your original motivation and context behind compiling this dataset.
+For example, briefly include information on the theoretical or methodological background against which you generated the data.
+Do not make concluding, interpretive, or otherwise inferential statements about the dataset.
+In case your data article is related to an original research article, please briefly describe how the data article adds value to the published article (Max.
+200 words).
+
+# Data Description
+
+> This section describes your dataset.
+Refer to all the data folders, subfolders, and files in the repository individually, irrespective of whether they relate to raw or analyzed data, and make sure that the reader can follow the structure of your dataset.
+> Please use visual aids (such as tables, graphs, or figures with captions) to familiarize the reader with your dataset, but do not offer background, interpretations, or conclusions.
+
+To simplify matters, the dataset has been curated into a single `.csv` file.
+
+# Experimental Design, Materials and Methods
+
+> This section describes how you acquired the data.
+Provide a complete description of the experimental design and methods used to acquire these data.
+For example, include all code (files) and software used for data analysis or data generation, and describe tools, instruments, and experimental conditions.
+> 
+> It is important that this section is as comprehensive as possible.
+There is no character limit, and you may use illustrative figures or tables; however, please do not offer background, interpretations, or conclusions.
+
+## Data sources
+
+1. Newspaper and magazine clippings
+  a. Physically archived newspapers (1993-20xx) available from The National Archive, Brunei.
+  b. Digitally archived newspapers available freely online.
+  c. Digitally archived magazines available freely online.
+
+2. Web scraping of online property agent listings
+
+TODO:
+- Describe the typical workflow. 
+- Describe the LLM data cleaning process.
+
+# Limitations
+
+> Describe any limitations related to the data described in this article.
+These could be any problems you faced during data collection or curation, limited quality or size of dataset, data biases, etc., but should not include limitations of analysis conducted or interpretation (Max.
+200 words).
+If there are none, please write ‘None’ or ‘Not applicable’.
+
+- While effort has been made to ensure duplicate listings are removed, there is a slight possibility that some have slipped through the cracks.
+- Data coverage. Only popular advertisements listed... So not a lot in Temburong or Tutong.
+
+# Ethics
+
+> Data in Brief’s Guide for Authors contains detailed information on the ethical guidelines with which all authors must comply.
+In addition, we ask you to complete the relevant statement(s) below.
+Please delete those which are not relevant for your data.
+> If your work involved human subjects, please include a statement here confirming that the relevant informed consent was obtained from those subjects, if the research was carried out in accordance with the Declaration of Helsinki, and if it includes the Ethical committee approval and the protocol number.
+A copy of the consent form (in English) can be submitted either in a data repository or under the section ‘Consent form’ while submitting the manuscript to the system.
+>
+> If your work involved animal experiments, please include a statement here confirming that those experiments complied with the ARRIVE guidelines and were carried out in accordance with the U.K.
+Animals (Scientific Procedures) Act, 1986 and associated guidelines; EU Directive 2010/63/EU for animal experiments; or the National Institutes of Health guide for the care and use of laboratory animals (NIH Publications No.
+8023, revised 1978).
+Note, the sex of the animals must be indicated, and, where appropriate, the influence (or association) of sex on the results of the study.
+> 
+> If your work involved data collected from social media platforms, please include a statement here confirming that a) informed consent was obtained from participants or that participant data has been fully anonymized, and b) the platform(s)’ data redistribution policies were complied with.
+> 
+> If none of the above, please include a statement confirming that the authors have read and follow the ethical requirements for publication in Data in Brief and confirming that the current work does not involve human subjects, animal experiments, or any data collected from social media platforms.
+
+# CRediT Author Statement
+
+https://www.elsevier.com/researcher/author/policies-and-guidelines/credit-author-statement
+
+# Acknowledgements
+
+The authors gratefully acknowledge the contributions of Atikah Farhain Yahya, Nurulhanisah Abdul Manan, and Nina Zuhairi towards the collection and processing of the data contained within.
+
+<!-- In this section, mention all contributors who do not meet the criteria for authorship.  -->
+<!-- In addition, please list any funding sources in this section. List funding sources in the standard way to facilitate compliance to funder's requirements. -->
+<!-- If no funding has been provided for the research, please include the following sentence: -->
+<!-- This research did not receive any specific grant from funding agencies in the public, commercial, or not-for-profit sectors. -->
+
+# Declaration of Competing Interests
+
+The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.
+
 ## References {.unnumbered}

### 2024-12-12 analysis.qmd
Render manuscript

---
title: Plots and data summaries for manuscript
author: Haziq Jamil
page-layout: full
grid:
  sidebar-width: 0px
editor_options: 
  chunk_output_type: console
html-table-processing: none
---

```{r}
library(tidyverse)
library(bruneimap)
library(gt)
library(gtsummary)
library(lubridate)
hsp <- 
  read_csv("data/hspbn_2024-12-12.csv") |>
  mutate(
    type = factor(type, levels = c("Detached", "Semi-Detached", "Terrace",
                                   "Apartment", "Land")),
    tenure = factor(tenure, levels = c("Freehold", "Leasehold", "Strata")),
    status = factor(status, levels = c("Proposed", "New", "Resale")),
    date = as.Date(date, format = "%d/%m/%y"),
    quarter = zoo::as.yearqtr(quarter)
  )
rppi <- 
  read_csv("data/rppi.csv") |>
  mutate(
    quarter = zoo::as.yearqtr(quarter),
    rppi = rppi / 100
  )
```

## Glimpse

```{r}
glimpse(hsp)
```

## Summary of variables

```{r}
#| label: tbl-summary
#| tbl-cap: Summary of housing data
hsp |>
  mutate(
    price = price / 1000,
    storeys = factor(
      ifelse(storeys >= 3, "3+", as.character(storeys)),
      levels = c("1", "2", "3+")
    )
  ) |>
  tbl_summary(
    include = c(price:baths),
    by = district,
    missing = "no", 
    type = all_continuous() ~ "continuous2",
    statistic = list(
      all_continuous2() ~ c("{mean} ({sd})", Range = "{min} - {max}", "{median} ({p25}, {p75})")
    ),
    label = list(
      price = "Price (BND 1,000)",
      type = "Property type",
      plot_area = "Plot area (acres)",
      floor_area = "Floor area (sq. ft.)",
      storeys = "Number of storeys",
      status = "Development status",
      tenure = "Land tenure",    
      beds = "Number of bedrooms",
      baths = "Number of bathrooms"
    ),
    digits = list(
      baths = 1,
      beds = 1
    )
  ) |>
  add_overall() |>
  add_n() |>
  modify_header(label ~ "**Variable**") 
```

## Data availability by year

```{r}
#| label: tbl-avail
#| tbl-cap: Data availability by year
hsp |>
  mutate(
    year = year(date),
    missing_price = is.na(price),
    missing_type = is.na(type),
    missing_tenure = is.na(tenure),
    missing_status = is.na(status),
    missing_plot_area = is.na(plot_area),
    missing_floor_area = is.na(floor_area),
    missing_storeys = is.na(storeys),
    missing_beds = is.na(beds),
    missing_baths = is.na(baths),
    missing_housechar = missing_plot_area & missing_floor_area & missing_beds & missing_baths,
    year = year(quarter),
  ) |>
  summarise(
    count = n(),
    spatial = length(unique(mukim)) / nrow(bruneimap::mkm_sf),
    # price = sum(missing_price),
    type = sum(missing_type),
    house_char = sum(missing_housechar),
    source = list(unique(method)),
    .by = year
  ) |>
  mutate(
    `nat-archive` = map_chr(source, ~ ifelse("nat-archive" %in% .x, "/", "")),
    `online-archive` = map_chr(source, ~ ifelse("online-archive" %in% .x, "/", "")),
    `web-scrape` = map_chr(source, ~ ifelse("web-scrape" %in% .x, "/", "")),
    llm = map_chr(source, ~ ifelse("web-scrape-llm" %in% .x, "/", ""))
  ) |> 
  select(-source) |>
  mutate(across(type:house_char, \(x) x / count)) |>
  gt() |>
  tab_spanner(
    label = "Data source",
    columns = `nat-archive`:`web-scrape`
  ) |>
  tab_spanner(
    label = "Missing data severity",
    columns = type:house_char
  ) |>
  fmt_percent(
    spatial:house_char,
    decimals = 1
  ) |>
  cols_label(
    year ~ "Year",
    count ~ "Count",
    spatial ~ "Spatial coverage (mukim)",
    type ~ "Property Type",
    house_char ~ "Property Characteristics",
    `nat-archive` ~ "National Archive",
    `online-archive` ~ "Online Archive",
    `web-scrape` ~ "Web Scraping",
    llm ~ "LLM post-processing"
  ) |>
  tab_footnote(
    footnote = paste0("Number of mukims in Brunei = ", nrow(bruneimap::mkm_sf), "."),
    locations = cells_column_labels(columns = spatial)
  ) |>
  tab_footnote(
    footnote = "Missing all of plot area, floor area, beds, and baths variables.",
    locations = cells_column_labels(columns = house_char)
  ) |>
  tab_options(
    quarto.disable_processing = TRUE
  )
```

## Spatial distribution

```{r}
#| label: fig-spatial
#| fig-cap: Spatial distribution of median property prices by mukim.
#| message: false
#| warning: false
hsp_mkm <-
  hsp |>
  summarise(
    price = median(price, na.rm = TRUE, trim = 0.05),
    .by = mukim
  ) |>
  left_join(x = bruneimap::mkm_sf)

ggplot(hsp_mkm) +
  geom_sf(aes(fill = price), col = "gray50", linewidth = 0.5) +
  scale_fill_viridis_c(
    option = "cividis",
    na.value = "transparent",
    labels = scales::dollar,
    trans = scales::pseudo_log_trans(sigma = 0.001),
    name = "Median\nprice"
  ) +
  ggrepel::geom_label_repel(
    data = drop_na(hsp_mkm, price) |> mutate(mukim = gsub("Mukim ", "", mukim)),
    aes(label = mukim, geometry = geometry),
    size = 2.7,
    stat = "sf_coordinates",
    max.overlaps = Inf,
    min.segment.length = 0,       # Allow longer segments
    segment.size = 0.3,           # Adjust the thickness of lines
    segment.curvature = 0.1,      # Add curvature if needed
    force = 5                     # Increase force to spread labels
  ) +
  labs(x = NULL, y = NULL) +
  theme_bw()
```

## Price evolution

```{r}
#| label: fig-price-evolution
#| fig-cap: "Median smoothed prices per square foot by property type using a 12-month rolling window."
#| message: false
#| out-width: 100%
#| fig-height: 5
#| fig-width: 9
hsp_noland <- filter(hsp, type != "Land")
hsp_all <- hsp_noland
hsp_all$type <- "Overall"
hsp_sld <- 
  bind_rows(hsp_noland, hsp_all) |> 
  arrange(date) |> 
  drop_na(type) |>
  mutate(
    # date = case_when(
    #   year(date) <= 2002 ~ zoo::as.Date(quarter),
    #   TRUE ~ date
    # ),
    price_per_sqft = price / floor_area
  ) |>
  filter(price_per_sqft < 350)

slider::slide_period_dfr(hsp_sld, hsp_sld$date, "month", \(df) {
    df |>
    drop_na(type) |>
      summarise(
        date = min(date), 
        price = median(price, na.rm = TRUE),
        plot_area = median(plot_area, na.rm = TRUE),
        floor_area = median(floor_area, na.rm = TRUE),
        .by = type
      )
  }, .before = 6, .after = 6) |>
  distinct(date, type, .keep_all = TRUE) |>
  mutate(
    price_per_sqft = price / floor_area,
    type = factor(type, levels = c("Detached", "Semi-Detached", "Terrace",
                                   "Apartment", "Overall")) 
  ) |>  ggplot(aes(x = date, y = price_per_sqft, col = type)) +
  geom_line(aes(linewidth = type)) +
  scale_x_date(
    breaks = scales::breaks_width("1 year"), 
    labels = scales::label_date("%Y"),
    name = NULL
  ) +
  scale_y_continuous(
    labels = scales::dollar,
    name = "Price per square foot (BND)"
  ) +
  scale_colour_manual(values = c(RColorBrewer::brewer.pal(4, "Set1"), "black")) +
  scale_linewidth_manual(values = c(rep(0.6, 4), 1.2)) +
  labs(
    col = NULL,
    linewidth = NULL
    # caption = "Median smoothed prices using a 12-month rolling window."
  ) +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "top"
  ) 
```

## RPPI Comparison

```{r}
#| label: fig-rppi
#| fig-cap: "Comparison of quarterly median price per square foot indices (Median PPSF) and the official Residential Property Price Index (RPPI) from Brunei Darussalam Central Bank (BDCB)."
#| message: false
#| out-width: 100%
#| fig-height: 5
#| fig-width: 9
hsp_rppi <- filter(hsp_sld, type == "Overall")

slider::slide_period_dfr(hsp_rppi, hsp_rppi$date, "month", \(df) {
    df |>
    drop_na(type) |>
      summarise(
        quarter = min(quarter), 
        price = median(price, na.rm = TRUE),
        plot_area = median(plot_area, na.rm = TRUE),
        floor_area = median(floor_area, na.rm = TRUE)
      )
  }, .before = 1, .after = 1) |>
  summarise(across(price:floor_area, median), .by = quarter) |>
  mutate(
    price_per_sqft = price / floor_area,
    index = price_per_sqft / price_per_sqft[quarter == "2015 Q1"],
  ) |>
  right_join(rppi) |>
  pivot_longer(c(index, rppi), names_to = "series", values_to = "value") |>
  # mutate(series = factor(series, labels = c("PPS", "RPPI (BDCB)"))) |>
  ggplot(aes(x = quarter, y = value, col = series)) +
  geom_hline(yintercept = 1, linetype = "dashed") +
  geom_line(linewidth = 0.8) +
  scale_colour_brewer(palette = "Set1") +
  scale_y_continuous(labels = scales::percent, name = "Index") +
  zoo::scale_x_yearqtr(
    format = "%Y-Q%q", name = NULL, #expand = c(0, 0),
    breaks = seq(2015, 2024.5, by = 0.25)
  ) +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "none"
  ) +
  geom_text(
    data = tibble(
      quarter = c(2024.25, 2024.25),
      series = c("index", "rppi"),
      value = c(0.935, 0.955),
      label = c("Median PPSF", "RPPI (BDCB)")
    ),
    aes(label = label),
    hjust = 0
  ) +
  # directlabels::geom_dl(aes(label = series), method = "last.points") +
  coord_cartesian(xlim = c(2015, 2025))
```

### 2024-12-12 manuscript.qmd
Render manuscript

@@
         postal-code: BE 1410
-  - name: Hafeezul Waezz Rabu
+  - name: Amira Barizah Noorosmawie
     affiliations:
       - ref: ubd        
-  - name: Amira Barizah Noorosmawie
+  - name: Hafeezul Waezz Rabu
     affiliations:
@@
 
+:::{.column-page}
+
+{{< embed analysis.qmd#tbl-summary >}}
+
+:::
+
 # Experimental Design, Materials and Methods
@@
 There is no character limit, and you may use illustrative figures or tables; however, please do not offer background, interpretations, or conclusions.
+
+{{< embed analysis.qmd#fig-spatial >}}
+
+{{< embed analysis.qmd#fig-price-evolution >}}
+
+{{< embed analysis.qmd#fig-rppi >}}
 
@@
 TODO:
+
 - Describe the typical workflow. 
 - Describe the LLM data cleaning process.
+
+:::{.column-page}
+
+{{< embed analysis.qmd#tbl-avail >}}
+
+:::
 

### 2024-12-12 analysis.qmd
Update manuscript

@@
   modify_header(label ~ "**Variable**")
+  # as_gt() |>
+  # tab_options(
+  #   quarto.disable_processing = TRUE
+  # )
 ```
@@
   ggrepel::geom_label_repel(
-    data = drop_na(hsp_mkm, price) |> mutate(mukim = gsub("Mukim ", "", mukim)),
+    data = drop_na(hsp_mkm, price) |> 
+      mutate(mukim = gsub("Mukim ", "", mukim)),
     aes(label = mukim, geometry = geometry),

### 2024-12-12 manuscript.qmd
Update manuscript

@@
 
-:::{.column-page}
+:::{.content-visible when-format="html"}
 
+::: {.column-page }
 {{< embed analysis.qmd#tbl-summary >}}
+:::
+:::
 
+:::{.content-visible unless-format="html"}
+{{< embed analysis.qmd#tbl-summary >}}
 :::
@@
 
-:::{.column-page}
+:::{.content-visible when-format="html"}
+::: {.column-page }
+{{< embed analysis.qmd#tbl-avail >}}
+:::
+:::
 
+::: {.content-visible unless-format="html"}
 {{< embed analysis.qmd#tbl-avail >}}
-
 :::

### 2024-12-13 analysis.qmd
Update manuscript

@@
 ```{r}
+## ----- Libraries -------------------------------------------------------------
 library(tidyverse)
@@
 library(lubridate)
+library(GGally)
+
+## ----- Load data sets --------------------------------------------------------
 hsp <- 
@@
 
+## Correlations
+
+```{r}
+#| label: fig-corr
+#| fig-cap: Pairwise correlation plot of continuous variables.
+#| warning: false
+#| message: false
+#| fig-width: 7.5
+#| fig-height: 7.5
+#| out-width: 100%
+
+my_fn <- function(data, mapping, method = "lm", ...) {
+  ggplot(data = data, mapping = mapping) + 
+    geom_point(alpha = 0.5) + 
+    geom_smooth(method = method, formula = y ~ x, se = FALSE,
+                col = RColorBrewer::brewer.pal(3, "Set1")[2], ...)
+  }
+
+pm <-
+  hsp |>
+  mutate(
+    logprice = log(price),
+    price = price / 1000
+  ) |>
+  select(
+    `Plot area` = plot_area,
+    `Floor area` = floor_area,
+    Beds = beds,
+    Baths = baths,
+    `Price (BND 1,000)` = price,
+    `Log Price` = logprice
+  ) |>
+  ggpairs(
+    progress = FALSE,
+    lower = list(continuous = my_fn)
+  ) +
+  theme_bw() +
+  scale_x_continuous(labels = scales::number) +
+  scale_y_continuous(labels = scales::number) +
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1)
+  )
+pm[6,5] <- pm[5, 6] <- NULL
+pm
+```
+
 ## Data availability by year
@@
   mutate(
-    `nat-archive` = map_chr(source, ~ ifelse("nat-archive" %in% .x, "/", "")),
-    `online-archive` = map_chr(source, ~ ifelse("online-archive" %in% .x, "/", "")),
-    `web-scrape` = map_chr(source, ~ ifelse("web-scrape" %in% .x, "/", "")),
-    llm = map_chr(source, ~ ifelse("web-scrape-llm" %in% .x, "/", ""))
+    `nat-archive` = map_chr(source, ~ ifelse("nat-archive" %in% .x, "✔", "")),
+    `online-archive` = map_chr(source, ~ ifelse("online-archive" %in% .x, "✔", "")),
+    `web-scrape` = map_chr(source, ~ ifelse("web-scrape" %in% .x, "✔", "")),
+    llm = map_chr(source, ~ ifelse("web-scrape-llm" %in% .x, "✔", ""))
   ) |> 
@@
   mutate(across(type:house_char, \(x) x / count)) |>
-  gt() |>
+  gt(rowname_col = "year") |>
+  cols_align(
+    align = "center",
+    columns = `nat-archive`:llm
+  ) |>
   tab_spanner(
@@
   ) |>
+  grand_summary_rows(
+    columns = count:house_char,
+    fns = list(Mean = "mean"),
+    fmt = list(
+      ~ fmt_number(., decimals = 0, columns = "count"),
+      ~ fmt_percent(., decimals = 1, columns = c("spatial", "type", "house_char"))
+    )
+  ) |>
   tab_footnote(
-    footnote = paste0("Number of mukims in Brunei = ", nrow(bruneimap::mkm_sf), "."),
+    footnote = paste0("Total number of mukims in Brunei = ", nrow(bruneimap::mkm_sf), "."),
     locations = cells_column_labels(columns = spatial)
+  ) |>
+  tab_footnote(
+    footnote = "Unknown property type.",
+    locations = cells_column_labels(columns = type)
   ) |>
@@
   tab_options(
-    quarto.disable_processing = TRUE
+    quarto.disable_processing = TRUE,
+    grand_summary_row.text_transform = "capitalize"
   ) 
@@
 #| label: fig-price-evolution
-#| fig-cap: "Median smoothed prices per square foot by property type using a 12-month rolling window."
+#| fig-cap: "Median smoothed prices per square foot by property type using a 24-month (8-quarter) rolling window."
 #| message: false
@@
 #| fig-width: 9
-hsp_noland <- filter(hsp, type != "Land")
+hsp_noland <- 
+  filter(hsp, type != "Land") |>
+  drop_na(type)
 hsp_all <- hsp_noland
@@
   bind_rows(hsp_noland, hsp_all) |> 
-  arrange(date) |> 
-  drop_na(type) |>
-  mutate(
-    # date = case_when(
-    #   year(date) <= 2002 ~ zoo::as.Date(quarter),
-    #   TRUE ~ date
-    # ),
-    price_per_sqft = price / floor_area
-  ) |>
-  filter(price_per_sqft < 350)
+  arrange(date)
 
@@
       )
-  }, .before = 6, .after = 6) |>
+  }, .before = 18, .after = 6) |>
   distinct(date, type, .keep_all = TRUE) |>
@@
                                    "Apartment", "Overall")) 
-  ) |>  ggplot(aes(x = date, y = price_per_sqft, col = type)) +
+  ) |>
+  ggplot(aes(x = date, y = price_per_sqft, col = type)) +
   geom_line(aes(linewidth = type)) +
@@
 #| fig-width: 9
-hsp_rppi <- filter(hsp_sld, type == "Overall")
+hsp_rppi <- hsp_noland |>
+  drop_na(floor_area)
 
@@
   }, .before = 1, .after = 1) |> 
-  summarise(across(price:floor_area, median), .by = quarter) |>
+  summarise(across(price:floor_area, \(x) median(x, na.rm = TRUE)), .by = quarter) |>
   mutate(
@@
     data = tibble(
-      quarter = c(2024.25, 2024.25),
+      quarter = c(2024.3, 2024.3),
       series = c("index", "rppi"),
-      value = c(0.935, 0.955),
+      value = c(0.941, 0.955),
       label = c("Median PPSF", "RPPI (BDCB)")

### 2024-12-13 manuscript.qmd
Update manuscript

@@
     url: "https://haziqj.ml"
-    # note: 
-    # roles: writing
     corresponding: true
@@
   - name: Lutfi Abdul Razak
+    orcid: 0000-0003-1681-0895
+    email: lutfi.razak@ubd.edu.bn
     affiliations:
@@
 :::
+
+{{< embed analysis.qmd#fig-corr >}}
 

### 2024-12-13 _cleanup.R

@@ -1,0 +1,12 @@
+# Cleanup script for Quarto
+files_to_remove <- c("elsarticle-num.bst", "manuscript.spl", "elsarticle.cls")
+
+# Iterate over files and delete them if they exist
+for (file in files_to_remove) {
+  if (file.exists(file)) {
+    file.remove(file)
+    cat("Deleted:", file, "\n")
+  } else {
+    cat("File not found:", file, "\n")
+  }
+}

### 2024-12-14 analysis.qmd
Update code

@@
 
-```{r}
-## ----- Libraries -------------------------------------------------------------
-library(tidyverse)
-library(bruneimap)
-library(gt)
-library(gtsummary)
-library(lubridate)
-library(GGally)
-
-## ----- Load data sets --------------------------------------------------------
-hsp <- 
-  read_csv("data/hspbn_2024-12-12.csv") |>
-  mutate(
-    type = factor(type, levels = c("Detached", "Semi-Detached", "Terrace",
-                                   "Apartment", "Land")),
-    tenure = factor(tenure, levels = c("Freehold", "Leasehold", "Strata")),
-    status = factor(status, levels = c("Proposed", "New", "Resale")),
-    date = as.Date(date, format = "%d/%m/%y"),
-    quarter = zoo::as.yearqtr(quarter)
-  )
-rppi <- 
-  read_csv("data/rppi.csv") |>
-  mutate(
-    quarter = zoo::as.yearqtr(quarter),
-    rppi = rppi / 100
-  )
-```
-
-## Glimpse
+## Load data
 
 ```{r}
-glimpse(hsp)
+#| echo: true
+#| eval: true 
+#| file: data.R
 ```
@@
   modify_header(label ~ "**Variable**")
-  # as_gt() |>
-  # tab_options(
-  #   quarto.disable_processing = TRUE
-  # )
 ```
@@
 #| warning: false
-hsp_mkm <-
-  hsp |>
-  summarise(
-    price = median(price, na.rm = TRUE, trim = 0.05),
-    .by = mukim
-  ) |>
-  left_join(x = bruneimap::mkm_sf)
-
 ggplot(hsp_mkm) +
@@
     max.overlaps = Inf,
-    min.segment.length = 0,       # Allow longer segments
-    segment.size = 0.3,           # Adjust the thickness of lines
-    segment.curvature = 0.1,      # Add curvature if needed
-    force = 5                     # Increase force to spread labels
+    min.segment.length = 0,       
+    segment.size = 0.3,           
+    segment.curvature = 0.1,      
+    force = 5                     
   ) +
@@
 #| fig-width: 9
-hsp_noland <- 
-  filter(hsp, type != "Land") |>
-  drop_na(type)
-hsp_all <- hsp_noland
-hsp_all$type <- "Overall"
-hsp_sld <- 
-  bind_rows(hsp_noland, hsp_all) |> 
-  arrange(date)
-
-slider::slide_period_dfr(hsp_sld, hsp_sld$date, "month", \(df) {
+slider::slide_period_dfr(hsp_all, hsp_all$date, "month", \(df) {
   df |>
-    drop_na(type) |>
+    filter(type != "Land") |>
     summarise(
@@
 #| fig-width: 9
-hsp_rppi <- hsp_noland |>
-  drop_na(floor_area)
 
-slider::slide_period_dfr(hsp_rppi, hsp_rppi$date, "month", \(df) {
-    df |>
-    drop_na(type) |>
-      summarise(
-        quarter = min(quarter),
-        price = median(price, na.rm = TRUE),
-        plot_area = median(plot_area, na.rm = TRUE),
-        floor_area = median(floor_area, na.rm = TRUE)
-      )
-  }, .before = 1, .after = 1) |> 
-  summarise(across(price:floor_area, \(x) median(x, na.rm = TRUE)), .by = quarter) |>
-  mutate(
-    price_per_sqft = price / floor_area,
-    index = price_per_sqft / price_per_sqft[quarter == "2015 Q1"],
-  ) |> 
-  right_join(rppi) |>  
+hsp_rppi |>  
   pivot_longer(c(index, rppi), names_to = "series", values_to = "value") |>
-  # mutate(series = factor(series, labels = c("PPS", "RPPI (BDCB)"))) |>
   ggplot(aes(x = quarter, y = value, col = series)) +
@@
   zoo::scale_x_yearqtr(
-    format = "%Y-Q%q", name = NULL, #expand = c(0, 0),
+    format = "%Y-Q%q", 
+    name = NULL, 
     breaks = seq(2015, 2024.5, by = 0.25)
@@
   ) +
-  # directlabels::geom_dl(aes(label = series), method = "last.points") +
   coord_cartesian(xlim = c(2015, 2025))

### 2024-12-14 manuscript.qmd
Update code

@@
   Abstract here.
+engine: knitr
 ---
+
+```{r}
+#| echo: false
+#| eval: true 
+#| file: data.R
+```
 
@@
 
-:::{.content-visible when-format="html"}
-
-::: {.column-page }
+::: {.content-visible when-format="html"}
+::: {.column-page}
 {{< embed analysis.qmd#tbl-summary >}}
@@
 
-:::{.content-visible unless-format="html"}
+::: {.content-visible unless-format="html"}
 {{< embed analysis.qmd#tbl-summary >}}
@@
 
-:::{.content-visible when-format="html"}
-::: {.column-page }
+::: {.content-visible when-format="html"}
+::: {.column-page}
 {{< embed analysis.qmd#tbl-avail >}}

### 2024-12-14 _cleanup.R

@@ -10,3 +10,27 @@ for (file in files_to_remove) {
     cat("File not found:", file, "\n")
   }
 }
+
+# Fix the alignment of tfoot in the Quarto-generated HTML
+
+# Path to the HTML file
+html_file <- "docs/index.html"
+
+# Check if the file exists
+if (file.exists(html_file)) {
+  # Read the file content
+  html_content <- readLines(html_file)
+  
+  # Locate the line with <tfoot class="gt_footnotes">
+  html_content <- gsub(
+    pattern = '<tfoot class="gt_footnotes">',
+    replacement = '<tfoot class="gt_footnotes" style="text-align: left;">',
+    x = html_content
+  )
+  
+  # Write the updated content back to the file
+  writeLines(html_content, html_file)
+  cat("Updated text alignment in:", html_file, "\n")
+} else {
+  cat("File not found:", html_file, "\n")
+}

### 2024-12-14 data.R

@@ -1,0 +1,81 @@
+library(tidyverse)
+library(bruneimap)
+library(gt)
+library(gtsummary)
+library(lubridate)
+library(GGally)
+
+## -----------------------------------------------------------------------------
+#| label: data
+
+# Main data set
+hsp <- 
+  read_csv("data/hspbn_2024-12-12.csv") |>
+  mutate(
+    type = factor(type, levels = c("Detached", "Semi-Detached", "Terrace",
+                                   "Apartment", "Land")),
+    tenure = factor(tenure, levels = c("Freehold", "Leasehold", "Strata")),
+    status = factor(status, levels = c("Proposed", "New", "Resale")),
+    date = as.Date(date, format = "%d/%m/%y"),
+    quarter = zoo::as.yearqtr(quarter)
+  )
+
+# RPPI from BDCB
+rppi <- 
+  read_csv("data/rppi.csv") |>
+  mutate(
+    quarter = zoo::as.yearqtr(quarter),
+    rppi = rppi / 100
+  )
+
+# To create median price per square foot, need to filter out "Land" types as
+# well as missing property types. Then create an "Overall" type.
+hsp_all <- 
+  bind_rows(
+    hsp, 
+    mutate(hsp, type = "Overall")
+  ) |> 
+  arrange(date) 
+
+# Create a median price per square foot index
+hsp_rppi <-
+  slider::slide_period_dfr(hsp, hsp$date, "month", \(df) {
+    df |>
+      filter(type != "Land") |>
+      drop_na(floor_area) |>
+      summarise(
+        quarter = first(quarter),
+        price = median(price, na.rm = TRUE),
+        # plot_area = median(plot_area, na.rm = TRUE),
+        floor_area = median(floor_area, na.rm = TRUE)
+      )
+  }, .before = 1, .after = 1) |>
+  summarise(across(price:floor_area, \(x) median(x, na.rm = TRUE)), .by = quarter) |> 
+  drop_na(quarter) |>
+  mutate(
+    price_per_sqft = price / floor_area,
+    index = price_per_sqft / price_per_sqft[quarter == "2015 Q1"],
+  ) |>
+  right_join(rppi, by = join_by(quarter)) 
+
+rppi_mae <-
+  hsp_rppi |>
+  summarise(
+    rmse = (mean( abs(rppi - index) ^ 1)),
[…]

### 2024-12-14 analysis.qmd
Write data description section

@@
 #| label: tbl-summary
-#| tbl-cap: Summary of housing data
+#| tbl-cap: Summary of housing data.
 hsp |>
@@
 #| label: tbl-avail
-#| tbl-cap: Data availability by year
+#| tbl-cap: Data availability by year.
 hsp |>
@@
 #| label: fig-price-evolution
-#| fig-cap: "Median smoothed prices per square foot by property type using a 24-month (8-quarter) rolling window."
+#| fig-cap: Median smoothed prices per square foot by property type using a 24-month (8-quarter) rolling window.
 #| message: false
@@
 #| label: fig-rppi
-#| fig-cap: "Comparison of quarterly median price per square foot indices (Median PPSF) and the official Residential Property Price Index (RPPI) from Brunei Darussalam Central Bank (BDCB)."
+#| fig-cap: Comparison of quarterly median price per square foot indices (Median PPSF) and the official Residential Property Price Index (RPPI) from Brunei Darussalam Central Bank (BDCB).
 #| message: false

### 2024-12-14 manuscript.qmd
Write data description section

@@
 date-modified: last-modified
-nocite: |
-  @*
 abstract: |
@@
 
-> Data articles describe research data that the authors have made publicly available through a repository.
+<!-- > Data articles describe research data that the authors have made publicly available through a repository.
 These articles ensure that raw data, which is often buried in supplementary material, is peer-reviewed, curated, formatted, indexed, given a DOI and made publicly available upon publication.
@@
 Data in Brief will not accept any submissions that contain datasets with insufficient variables or samples.
+-->
 
@@
 
-This section states why these data are of value to the scientific community.
+<!-- This section states why these data are of value to the scientific community.
 Please provide between 3 and 6 bullet points and answer at least the questions below (delete the questions afterwards).
-Each bullet point should be a maximum of 150 words long, and should not include conclusions or inferences:
+Each bullet point should be a maximum of 150 words long, and should not include conclusions or inferences: -->
 
-- Why are these data valuable?
-- How can these data be reused by other researchers?
-- ...
+<!-- - Why are these data valuable? -->
+<!-- - How can these data be reused by other researchers? -->
+<!-- - ... -->
+
+- {{< lipsum 1 >}}
+- {{< lipsum 1 >}}
+- {{< lipsum 1 >}}
 
@@
 
-Please describe your original motivation and context behind compiling this dataset.
+<!-- Please describe your original motivation and context behind compiling this dataset.
 For example, briefly include information on the theoretical or methodological background against which you generated the data.
@@
 200 words).
+-->
+
+The housing market is a key indicator of economic health and social well-being, yet comprehensive and publicly accessible datasets in Brunei remain limited.
+To our knowledge, this is the first dataset of its kind in Brunei, motivated by the need to fill the gap in publicly available data on the local housing market.
+
+Currently, the Brunei Darussalam Central Bank (BDCB) produces a Residential Property Price Index (RPPI) using data sourced from financial institutions, such as bank loan datasets.
+While the RPPI is published quarterly, the underlying raw data is not publicly available due to privacy restrictions.
+This limits research opportunities and transparency in understanding broader housing market trends.
+Furthermore, the RPPI only began in 2015, leaving a significant gap in historical housing data.
+
+Our dataset addresses these challenges by providing a cost-effective and timely means to collect and analyze housing market data.
+Covering records from 1993 onward, it offers historical depth that complements and extends beyond the RPPI.
+It is valuable not only for tracking property price trends but also for advancing research in economics, urban planning, and real estate, supporting informed decision-making across sectors.
 
@@
 
-> This section describes your dataset.
+<!-- > This section describes your dataset.
 Refer to all the data folders, subfolders, and files in the repository individually, irrespective of whether they relate to raw or analyzed data, and make sure that the reader can follow the structure of your dataset.
-> Please use visual aids (such as tables, graphs, or figures with captions) to familiarize the reader with your dataset, but do not offer background, interpretations, or conclusions.
+-->
+<!-- > Please use visual aids (such as tables, graphs, or figures with captions) to familiarize the reader with your dataset, but do not offer background, interpretations, or conclusions. -->
 
-To simplify matters, the dataset has been curated into a single `.csv` file.
+```{r}
+#| include: false
+years <- lubridate::year(hsp$date)
+max(years) - min(years) + 1
+
+```
+
+The data has been curated into a single Comma-Separated Values (CSV) file named `hspbn_2024-12-12.csv`. 
+The dataset contains `{r} scales::comma(nrow(hsp))` property listing records which are enriched with area-level geotagged spatial information, spanning a period of `{r} max(years) - min(years) + 1` years from `{r} format(min(hsp$date), "%b %Y")` to `{r} format(max(hsp$date), "%b %Y")`.
+The `{r} scales::comma(ncol(hsp))` columns of this dataset capture information for each property listing as detailed in @tbl-codebook below.
+
+```{r}
+#| label: tbl-codebook
+#| tbl-cap: Codebook for the house price dataset.
+readxl::read_xlsx("data/codebook.xlsx") |>
+  rownames_to_column("No.") |>
+  gt(rowname_col = "No.") |>
+  fmt_markdown("Variable")
+```
+
+## Property Characteristics
+
+The dataset includes a range of property characteristics suitable for exploring the relationship between property attributes and prices.
+This section clarifies and provides context for the key variables in the dataset.
+
+Brunei’s private residential property market offers a variety of options, including detached houses, townhouses, and apartments [@hassan2023sociocultural].
+Based on this, property types have been categorised into four main groups --
+Detached, Semi-Detached, Terrace, and Apartment -- to accurately reflect the diversity of property types in Brunei.
+Additionally, there are a small number of records that reflect land sales, which are categorised accordingly as "Land".
+
+Property tenure refers to the legal terms under which a person holds ownership or occupancy rights to a property. 
+In Brunei, property tenure can be classified into three main categories: 
+Freehold (in perpetuity), Leasehold, and Strata.
+The latter of which refers to a form of ownership where individuals own a portion of a property, such as an apartment, and share ownership of common areas.
+
+The dataset also includes information on the status of the property listing, indicating whether the advertisement refers to a proposed development, a newly completed development, or a property being resold.
+This categorical variable may be useful for analyzing price differences across different types of listings.
+
+The numerical variables in the dataset are plot area, floor area, storeys, beds, and baths, each providing information on the physical attributes of the property. 
+Note that plot area is measured in acres, while floor area is in square feet, as these are the common units of measurement used in Brunei. 
+Users of this dataset may choose to convert these units as needed for their analysis.
+
+Finally, metadata about the property is included for transparency and informational purposes. 
+The variable agent specifies the (anonymised) identifier of the real estate agent or agency responsible for the listing, while source identifies the platform or medium from which the listing was obtained, such as a newspaper, magazine, or website.
+The method variable details the data collection approach, which is further elaborated in the section below.
 
@@
 
-{{< embed analysis.qmd#fig-corr >}}
+<!-- {{< embed analysis.qmd#fig-corr >}} -->
+
+## Spatial Information
+
+In Brunei Darussalam, the administrative areas are organised hierarchically into three levels.
+At the smallest level is the *kampong*, which refers to a village or neighbourhood.
+Several kampongs grouped together form a *mukim*, which serves as a sub-district administrative area.
+Finally, multiple mukims are nested within a *district*, the largest administrative unit, of which Brunei has four: Brunei-Muara, Belait, Tutong, and Temburong.
+In our dataset, each property listing is associated with a specific kampong, mukim, and district, allowing for spatial analysis at different scales.
+
+Importantly, the names of the kampongs, mukims, and districts have been harmonised with a standardised naming convention to ensure consistency across the dataset.
+This also allows for ease of integration into Geographic Information Systems (GIS) software for spatial analysis and visualisation, namely the `{bruneimap}` R package [@jamil2024bruneimap].
+
+{{< embed analysis.qmd#fig-spatial >}}
+
+## Listing Dates
+
+The date variable in the dataset refers to the date on which the property listing was obtained. 
+It is important to note that this is not the date the property was sold, nor does it necessarily reflect the precise timing of other transactions related to the property. 
+Users should set their expectations accordingly, as the primary purpose of the date is to capture the state of the housing market at a specific point in time.
+
+For analysis, we recommend aggregating data by quarters, as represented by the quarter variable. 
+This aggregation helps address potential issues like missing data (see section below) and provides a more stable and robust representation of market trends, making it suitable for temporal analysis of the housing market.
+
+{{< embed analysis.qmd#fig-price-evolution >}}
+
+## Missing Values
+
+The dataset contains missing values across various property characteristics including type, tenure, status, plot area, floor area, storeys, beds, and baths.
+This is due to the nature of the property listings, which may not always include complete information when advertised.
+Missing values are represented by blank cells in the CSV file.
+The severity of missing values is summarised in @tbl-avail.
+Users of our dataset may wish to treat missing values in different ways depending on their research objectives.
 
@@
 
-> This section describes how you acquired the data.
+<!-- > This section describes how you acquired the data.
 Provide a complete description of the experimental design and methods used to acquire these data.
 For example, include all code (files) and software used for data analysis or data generation, and describe tools, instruments, and experimental conditions.
-> 
-> It is important that this section is as comprehensive as possible.
+-->
+<!-- >  -->
+<!-- > It is important that this section is as comprehensive as possible.
 There is no character limit, and you may use illustrative figures or tables; however, please do not offer background, interpretations, or conclusions.
+-->
 
-{{< embed analysis.qmd#fig-spatial >}}
+<!-- {{< embed analysis.qmd#fig-rppi >}} -->
 
-{{< embed analysis.qmd#fig-price-evolution >}}
+{{< embed analysis.qmd#tbl-avail >}}
 
-{{< embed analysis.qmd#fig-rppi >}}
-
-## Data sources
+## Manual Data Collection
 
@@
 
-2. Web scraping of online property agent listings
+## Automated Web Scraping
 
-TODO:
+Web scraping of online property agent listings
 
-- Describe the typical workflow. 
-- Describe the LLM data cleaning process.
+## LLM Data Cleaning
 
-::: {.content-visible when-format="html"}
-::: {.column-page}
-{{< embed analysis.qmd#tbl-avail >}}
-:::
-:::
+A test on 329 randomly selected data points found that 306 were "correct" (93.0% accuracy), i.e.
+usable in the sense that either the details were extracted correctly or correctly identified "non listings".
 
-::: {.content-visible unless-format="html"}
-{{< embed analysis.qmd#tbl-avail >}}
-:::
+## Spatial Data Harmonisation
 
@@
 
-> Describe any limitations related to the data described in this article.
+<!-- > Describe any limitations related to the data described in this article.
 These could be any problems you faced during data collection or curation, limited quality or size of dataset, data biases, etc., but should not include limitations of analysis conducted or interpretation (Max.
@@
 If there are none, please write ‘None’ or ‘Not applicable’.
+-->
 
@@
 - Data coverage. Only popular advertisements listed... So not a lot in Temburong or Tutong.
+- Missing data.
 
@@
 
-## References {.unnumbered}
+# References {.unnumbered}
 

### 2024-12-14 data.R

@@ -5,9 +5,6 @@ library(gtsummary)
 library(lubridate)
 library(GGally)
 
-## -----------------------------------------------------------------------------
-#| label: data
-
 # Main data set
 hsp <- 
   read_csv("data/hspbn_2024-12-12.csv") |>

### 2024-12-14 manuscript.qmd
Add more writing

@@
 This is due to the nature of the property listings, which may not always include complete information when advertised.
+It is noted, however, that there are no missing values for price and spatial information.
 Missing values are represented by blank cells in the CSV file.
 The severity of missing values is summarised in @tbl-avail.
-Users of our dataset may wish to treat missing values in different ways depending on their research objectives.
+In summary, 10.5% of the records contain missing values for all key house characteristics (i.e.
+plot area, floor area, beds, and baths), which, depending on the research question, may necessitate imputation or exclusion of these records.
 
@@
 
-<!-- {{< embed analysis.qmd#fig-rppi >}} -->
-
 {{< embed analysis.qmd#tbl-avail >}}
@@
 
-1. Newspaper and magazine clippings
-  a. Physically archived newspapers (1993-20xx) available from The National Archive, Brunei.
-  b. Digitally archived newspapers available freely online.
-  c. Digitally archived magazines available freely online.
+Early years data collection was conducted manually, involving the transcription of property listing details from advertisements into a digital tabular format. 
+This process was carried out by two of the authors over a period of nine months, from October 2023 to July 2024. 
+The primary sources of the property listings were local newspapers and magazines. 
+Physical copies were accessed through the National Archive of Brunei Darussalam, while digital versions, which are digitized replicas of the physical newspapers, were obtained online. 
+These digital formats could not be scraped due to their lack of structured data, necessitating manual transcription.
 
-## Automated Web Scraping
+Daily newspapers from 1993 onward were available at the National Archive.
+However, reviewing every single daily edition was not practical and would increase the likelihood of recording duplicate listings, thus necessating a sampling strategy.
+The sampling was done as follows.
+Three newspaper edition per week was selected at random, and the classifieds section was reviewed for property listings. 
+When a listing was found, it was recorded after careful filtering to ensure it was unique. 
+This manual filtering process involved cross-checking based on the real estate agent, house characteristics, price, location, and date proximity. 
+To avoid duplication, the same house listing was typically not recorded more than once within a quarter. 
+This strategy aimed to achieve a target quota of 300–500 unique listings per year.
+
+## Web Scraping
 
@@
 ## Spatial Data Harmonisation
+
+## Comparison with RPPI
+
+{{< embed analysis.qmd#fig-rppi >}}
 

### 2024-12-15 manuscript.qmd
Write web scraping procedure

@@
 ::: {.content-visible unless-format="html"}
+::: {.landscape}
 {{< embed analysis.qmd#tbl-summary >}}
+::: 
 :::
@@
 
+In this section we describe the data collection process, which involved either a manual transcription of property listings from newspapers, or web scraping of online property agent listings.
+In the later years, a large language model (LLM) was also employed to perform data cleaning on the web scraped data.
+The data collection method varied over the years due to the availability of data sources and the evolution of technology.
+@tbl-avail details which method was used for each year in the dataset, and whether the data was subjected to LLM post-processing.
+
+All analyses were conducted using the R programming language [@rcoreteam2024language], with specific packages used described in each subsection below.
+
 {{< embed analysis.qmd#tbl-avail >}}
@@
 
-Daily newspapers from 1993 onward were available at the National Archive.
+Although daily newspapers from 1993 onward were available at the National Archive, the classified sections were not always present.
+From 1993 to 1999, property advertisements were found only in Friday editions, and occasionally on Saturdays.
+Thus, newspapers from both these days were reviewed weekly to capture the listings data.
+This yielded roughly between 300 and 700 listings per year.
+
+From the year 2000 onwards, property advertisements were published daily in the classifieds section.
 However, reviewing every single daily edition was not practical and would increase the likelihood of recording duplicate listings, thus necessating a sampling strategy.
 The sampling was done as follows.
-Three newspaper edition per week was selected at random, and the classifieds section was reviewed for property listings. 
+Three newspaper editions per week were selected, and the classifieds section was reviewed for property listings. 
 When a listing was found, it was recorded after careful filtering to ensure it was unique. 
@@
 To avoid duplication, the same house listing was typically not recorded more than once within a quarter. 
-This strategy aimed to achieve a target quota of 300–500 unique listings per year.
+This process yielded roughly the same number of listings per year as the earlier years.
 
@@
 
-Web scraping of online property agent listings
+To compile additional property data for the study beyond manual data collection, web scraping was employed using the R programming language, leveraging the `{rvest}` package [@wickham2024rvest]. 
+This method enabled the systematic extraction of structured information from various local property listing websites such as panvilla.com (now defunct), bruhome.com, and bruneiproperty.com.bn.
+Such websites provide extensive details on properties listed as "for sale" in Brunei, aggregating advertisements from real estate agents and property developers.
+
+::: {#fig-web-scrape layout-ncol=1}
+
+::: {#fig-mockup-listing}
+![A mockup of the structure of property listing showing various HTML elements.](figures/house-mockup1.png)
+:::
+
+::: {#fig-mockup-table}
+![Example paragraph containing description within the "See Details" link for each property.](figures/house-mockup2.png)
+:::
+
+Illustration of a property listing from a typical Bruneian property portal. Attribution: Freepik.
+:::
+
+The process began by identifying the structure of the target websites, focusing on the HTML tags and classes containing the relevant information. 
+The goal here is to programmatically pinpoint and collect specific information like text, links, or attributes.
+For example, elements such as property prices, number of bedrooms, bathrooms, location, and other features were enclosed within specific HTML elements, which `{rvest}` functions like `html_elements()` and `html_text2()` could target and extract efficiently.
+@fig-mockup-listing illustrates the structure of a typical property listing showing the various HTML elements to target.
+Example code to perform this task in available in the repository.
+
+Each webpage displayed a fixed number of listings (e.g., 128 per page). 
+To scrape all pages, a loop was created to iterate through each page by modifying the URL (such as with an `&offset=<number>` parameter, where `<number>` represented the cumulative number of listings already scraped).
+
+Extracted data required some cleaning to standardize formats for analysis. 
+For instance:
+
+- `price` varibales were cleaned by removing non-numeric characters and converted to integers.
+- `beds` and `baths` were converted to integers.
+- `date` variables were formatted properly as `Date` objects.
+- Locations were stored as text strings. See the subsection below on spatial data harmonisation for more details.
+- Any additional information was extracted from the property descriptions, which were often unstructured and contained valuable insights not captured in the primary fields.
+
+<!-- The typical workflow for extracting data from a single property listing involved: -->
+
+<!-- 1.	Read the HTML: The read_html() function from {rvest} was used to load webpage content. -->
+<!-- 2.	Extract Key Elements: Functions like html_elements() and html_text2() targeted specific tags to extract data such as prices, beds, baths, and locations. -->
+<!-- 3.	Clean and Standardize: Extracted data were cleaned and converted to appropriate formats (e.g., numeric for prices, integers for bedrooms and bathrooms). -->
+<!-- 4.	Iterate Through Pages: A looping mechanism was employed to access subsequent pages by dynamically appending the offset parameter to the URL. -->
+<!-- 5.	Extract Additional Information: For individual property pages, a custom function was created to navigate links and extract further details using a mapping function (map()). -->
+
+Combining the workflow with a looping mechanism allowed for the systematic extraction of data from multiple pages and websites, and thus the automated scraping process enabled efficient data collection over time.
+This process however was highly contingent on the consistency of the structure of the websites being scraped from.
+Over time, some websites shut down, while others changed their structure, requiring adjustments to the scraping scripts.
+The web scraping process began in January 2022 and was conducted intermittently.
+Data from 2012 up until the present (December 2024) were managed to be collected using this method, averaging around 1,500 listings per year.
 

### 2024-12-15 analysis.qmd
Continue writing spatial and limitation section

@@
     format = "%Y-Q%q", 
+    expand = c(0, 0.1),
     name = NULL, 
@@
   ) +
-  coord_cartesian(xlim = c(2015, 2025))
+  coord_cartesian(xlim = c(2015, 2025.5))
 ```

### 2024-12-15 manuscript.qmd
Continue writing spatial and limitation section

@@
 - {{< lipsum 1 >}}
+- Allow missing data in house characteristics... but compelte data is provided for price, date, and spatial information.
 
@@
 - Locations were stored as text strings. See the subsection below on spatial data harmonisation for more details.
-- Any additional information was extracted from the property descriptions, which were often unstructured and contained valuable insights not captured in the primary fields.
+- Any additional information was extracted from the property descriptions and saved as a character vector. This very often contained valuable insights not captured in the primary fields.
 
@@
 
-A test on 329 randomly selected data points found that 306 were "correct" (93.0% accuracy), i.e.
-usable in the sense that either the details were extracted correctly or correctly identified "non listings".
+As mentioned, the web scraping process also captured unstructured information from the property descriptions, which often contained valuable details not captured in the primary fields.
+In this subsection, we detail the data cleaning process using a pre-trained large language model (LLM) to extract structured information from the unstructured text.
+The LLM used was Llama 3.1 with 8B parameters [@grattafiori2024llama], accessed using the `{tidychatmodels}` R package [@rapp2024tidychatmodels] via the Ollama^[<https://github.com/ollama/ollama>] API, a local interface platform to the LLM.
+
+The primary goal was to extract the house characteristics of interest, specifically variables 7 to 15 as per @tbl-codebook, from the unstructured verbose descriptions scraped from property listing websites.
+Each description was processed with a carefully designed prompt (@fig-llm-prompt) to ensure consistent output. 
+This prompt instructed the model to return only the required information in a semicolon-separated format, while handling edge cases such as missing descriptions, non-residential (commercial) properties, or rental property advertisements.
+
+::: {#fig-llm-prompt}
+```{r}
+#| echo: true
+#| eval: false
+#| code-overflow: wrap
+"The following is the description from a property sale listing in Brunei.
+This description will contain the information about the property, including its characteristics, price, and location.
+However, some of these descriptions may not contain property listings, and instead contain other or no information at all.
+
+In the case where this description is in fact a property listing, I would like you to extract the following information:
+
+1. Location / area of the property in Brunei, CHARACTER.
+2. Price of the property in Brunei Dollars, NUMERIC.
+3. Type of property, CHARACTER -- select from Detached, Semi-Detached, Terrace, Apartment, or Land.
+4. Land tenure, CHARACTER -- select from Freehold, Leasehold, or Strata. If other than this, return 'NA'.
+5. Status of the property, CHARACTER -- select from Proposed, Under Construction, New, or Resale.
+6. Land area in acres, NUMERIC.
+7. Built up area in square feet, NUMERIC.
+8. Number of storeys, INTEGER.
+9. Number of bedrooms, INTEGER.
+10. Number of bathrooms, INTEGER.
+
+Further instructions:
+
+- Please return **semicolon** separated values like this:
+
+  Kg Tanah Jambu; 250000; Detached ; Freehold ; New     ; 0.3 ; 2500; 2;  3; 3
+  Kg Tungku     ; 300000; Terrace  ; Leasehold; Resale  ; 0.25; 1700; 2;  3; 2 
+  Kg Kiarong    ; 200000; Apartment; Strata   ; Proposed; 0.1 ; 1000; NA; 2; 2
+  etc.
+  NUMBERS SHOULD NOT CONTAIN comma (,) for thousands separator
+
+- If any of the 10 values are missing, please return 'NA' for that value.
+
+- If the description does not contain a property listing (for example, it is a rental property advertisement), return 'NA' for all 10 values.
+
+- DO NOT RESPOND WITH ANYTHING ELSE OTHER THAN THE REQUIRED INFORMATION."
+```
+
+The LLM prompt to clean descriptions obtained from web scraping.
+
+:::
+
+The unstructured descriptions were fed into the model one at a time using a loop, with the LLM extracting and returning the relevant details. 
+Note that this loop was not parallelided due to the computational resources required by the LLM.
+The cleaned results were then parsed and stored in a data frame, which was then subjected to data-type validation to ensure conformity with the existing dataset.
+It takes on average 2.12 seconds to process a single description running on Apple MacBook Air M2 Silicon on Chip (SoC) and System in Chip (SiP) processors with 16GB RAM.
+We processed 4,820 descriptions in total from 2020 to 2024 using this method, with a runtime of approximately three hours.
+
+To test the accuracy of the LLM, a random sample of 329 descriptions was selected and manually verified for correctness.
+Of these, 306 were deemed correct (correct entries or identified "non-listings" correctly), resulting in an accuracy rate of 93.0%.
+Rare errors were spotted due to model hallucinations (despite setting the LLM temperature to the lowest setting), but these are typically minor and unlikely to significantly impact the overall analysis.
+Large errors on the other hand were corrected manually, by filtering for outliers or inconsistencies in the variables.
+Overall, the LLM was found to be a valuable tool for extracting structured information from unstructured text, significantly reducing the time and effort required for data cleaning.
+Users may wish to exclude these records from their analysis if they are concerned about the accuracy of the extracted data.
 
@@
 
-## Comparison with RPPI
+Whether the data was collected manually, through web scraping, or cleaned using the LLM, the spatial information extracted was often inconsistent in terms of naming conventions and granularity.
+To address this, a spatial data harmonisation process was conducted to standardise the names of the kampongs (villages) in the data set to the format used by Department of Economic Planning and Statistics (DEPS), Ministry of Finance and Economy, Brunei Darussalam as per the most recent census [@deps2022population].
+This is the same format used by the R package `{bruneimap}` [@jamil2024bruneimap].
+The CSV file `bn_kpg_level_data.csv` obtained from this package was used as a reference to standardise the kampong names in the dataset, which conveniently also included the mukim and district names for each kampong.
 
-{{< embed analysis.qmd#fig-rppi >}}
+The majority of house listings in Brunei specify the property location using the kampong name, the smallest administrative unit in the country. 
+The task in hand was then to match these kampong names in the dataset with the standardised names in the reference file. 
+Several challenges were encountered during this process, including:
+
+1. Spelling variations or misspellings, though these were relatively straightforward to correct.
+2. Unknown entries, where the correct kampong could sometimes be inferred from the geographical context; otherwise, these were set to `NA`.
+3.
+Multiple matches, occurring when two or more kampongs shared the same name (e.g., Kampong Panchor in Mukim Mentiri and Kampong Panchor in Mukim Lumapas).
+Additional information from the listing was used to determine the correct match, but where this was not possible, these entries were also set to `NA`.
+
+This process was carried out manually using data filtering features in Microsoft Excel. 
+Once completed, all entries marked as `NA` were removed so as to provide complete spatial information for each listing.
 
@@
 
-- While effort has been made to ensure duplicate listings are removed, there is a slight possibility that some have slipped through the cracks.
-- Data coverage. Only popular advertisements listed... So not a lot in Temburong or Tutong.
-- Missing data.
+Despite efforts to ensure data quality, some limitations remain. 
+While duplicate listings were carefully reviewed and removed, there remains a slight possibility that a duplicated records still exist in the dataset. 
+Additionally, the spatial data coverage is heavily skewed towards the Brunei-Muara district, which accounts for `{r} scales::percent(prop.table(table(hsp$district))[2], accuracy = 0.1)` of the listings.
+This simply reflects the district’s higher population and greater volume of property transactions [@jamil2024spatiotemporal] which could bias analyses toward this region.
+
+Missing data in house characteristics is another limitation, although this should be seen as an opportunity for further research to develop imputation methods or alternative analytical approaches. 
+Minor inaccuracies were also observed in the LLM-based data cleaning process, but these issues are infrequent and can be mitigated by subsetting or refining the affected entries.
+
+Finally, while significant effort was made to harmonise spatial data, the matching of kampong names to standardised references may not be entirely error-free. 
+However, aggregation to the mukim level provides a reliable alternative for spatial analyses, ensuring that the dataset remains valuable for research and analysis.
+
+<!-- To alleviate concerns regarding data quality due to the limitations discussed above, we can compare the dataset with the Residential Property Price Index (RPPI) [@bdcb2021technical]  published by the Brunei Darussalam Central Bank (BDCB).
+-->
+<!-- A simple median price per square foot (PPSF) index can be calculated by aggregating the date by quarters. -->
+<!-- In so doing, missing values do not pose a significant issue as the index is calculated at the aggregate level. -->
+<!-- @fig-rppi shows the comparison between the RPPI and the PPSF index calculated from our dataset. -->
+<!-- The mean absolute error (MAE) between the two indices is calculated to be `{r} scales::percent(rppi_mae[1], accuracy = 0.01)`, indicating a high level of agreement between the two datasets. -->
+
+<!-- {{< embed analysis.qmd#fig-rppi >}} -->
 

### 2024-12-15 data.R

@@ -12,7 +12,7 @@ hsp <-
     type = factor(type, levels = c("Detached", "Semi-Detached", "Terrace",
                                    "Apartment", "Land")),
     tenure = factor(tenure, levels = c("Freehold", "Leasehold", "Strata")),
-    status = factor(status, levels = c("Proposed", "New", "Resale")),
+    status = factor(status, levels = c("Proposed", "Under Construction", "New", "Resale")),
     date = as.Date(date, format = "%d/%m/%y"),
     quarter = zoo::as.yearqtr(quarter)
   )

### 2024-12-15 manuscript.qmd
Complete draft manuscript

@@
 
-- {{< lipsum 1 >}}
-- {{< lipsum 1 >}}
-- {{< lipsum 1 >}}
-- Allow missing data in house characteristics... but compelte data is provided for price, date, and spatial information.
+- **First of its kind for Brunei**.
+This dataset enables comprehensive spatial and temporal analysis of the Brunei housing market.
+To our knowledge, no other publicly available dataset exists for this purpose, making it a significant contribution to the field.
+Previous studies on Brunei's housing have been limited to recent or non-spatial data [@shabunko2014developing;@ng2022characterising;@jamil2025leveraging], or qualitative in nature due to the lack of a structured dataset [@hassan2011cultural;@hassan2023sociocultural].
+This aligns with the growing trend of using data analytics in the real estate industry [@braesemann2020proptech;@delisle2020big].
+
+- **Historical and spatial insights**.
+Covering data from 1993 to 2024, this dataset allows for the study of long-term housing trends in Brunei.
+Its detailed spatial information enables analysis at various levels, from kampong to mukim, providing insights into local patterns and urban development over time.
+This historical depth is particularly valuable given the lack of previous data before the establishment of the Residential Property Price Index (RPPI) [@bdcb2021technical] in 2015.
+
+- **Influence on economic and monetary policies**.
+Analysing the real estate market is crucial because the RPPI plays a key role in shaping monetary policy and assessing economic stability.
+Changes in RPPI signal inflationary pressures, guiding central bank decisions on interest rates.
+Developing a house price index using advertised prices, as explored by @rachman2019residential, aligns with practices in other countries, such as the UK’s RightMove House Price Index [@hmlandregistry2023comparing; @europeancommission.eurostat.2013handbook].
+This dataset demonstrates how programmatic methods can automate what is typically a time-consuming and labor-intensive process.
+
+- **Opportunities for handling of missing data**.
+While the dataset has complete information for key variables such as price, date, and spatial variables, missing information on house characteristics creates opportunities for further research.
+Evidently, house characteristics are inherently correlated (see [@fig-corr]), so imputation from observed correlations seems highly promising.
+With the spatial information present, this opens avenues for developing methodological approaches for handling missing data.
+Rather than being a limitation, the incomplete data in some variables encourages methodological innovation and exploration.
+
+- **Application of Large Language Models (LLMs)**.
+This project highlights an innovative use of Large Language Models (LLMs) for data cleaning.
+The LLM was employed to extract structured information from unstructured text descriptions, achieving an accuracy rate of 93%.
+This method significantly reduced the time and effort required for data cleaning.
+It can also be applied to other datasets with unstructured text, such as social media or document archives, to extract valuable information for analysis.
 
@@
 
-Currently, the Brunei Darussalam Central Bank (BDCB) produces a Residential Property Price Index (RPPI) using data sourced from financial institutions, such as bank loan datasets.
+Currently, the Brunei Darussalam Central Bank (BDCB) produces a Residential Property Price Index (RPPI) [@bdcb2021technical] using data sourced from financial institutions, such as bank loan datasets.
 While the RPPI is published quarterly, the underlying raw data is not publicly available due to privacy restrictions.
@@
 max(years) - min(years) + 1
-
 ```
@@
 
-<!-- {{< embed analysis.qmd#fig-corr >}} -->
-
 ## Spatial Information
@@
 
-The dataset contains missing values across various property characteristics including type, tenure, status, plot area, floor area, storeys, beds, and baths.
-This is due to the nature of the property listings, which may not always include complete information when advertised.
-It is noted, however, that there are no missing values for price and spatial information.
-Missing values are represented by blank cells in the CSV file.
-The severity of missing values is summarised in @tbl-avail.
+This dataset endeavours to provide complete information regarding the listing date, spatial information, advertised price, and metadata.
+Nonetheless, we hereby report that missing values are present across various **property characteristics**, including type, tenure, status, plot area, floor area, storeys, beds, and baths.
+The reason for this is due to the nature of the property advertisements, which may not always include complete information when advertised by the real estate agents.
+Missing values are represented by blank cells in the CSV file, and the severity of missing values is summarised in @tbl-avail.
 In summary, 10.5% of the records contain missing values for all key house characteristics (i.e.
 plot area, floor area, beds, and baths), which, depending on the research question, may necessitate imputation or exclusion of these records.
+
+## Comparison to RPPI Data
+
+To demonstrate the quality of the dataset, we compared it with the Residential Property Price Index (RPPI) [@bdcb2021technical]  published by the Brunei Darussalam Central Bank (BDCB).
+A simple median price per square foot (PPSF) index can be calculated by aggregating the date by quarters.
+In so doing, missing values do not pose a significant issue as the index is calculated at the aggregate level.
+@fig-rppi shows the comparison between the RPPI and the PPSF index calculated from our dataset.
+The mean absolute error (MAE) between the two indices is calculated to be `{r} scales::percent(rppi_mae[1], accuracy = 0.01)`, indicating a high level of agreement between the two datasets.
+
+{{< embed analysis.qmd#fig-rppi >}}
 
@@
 
-<!-- To alleviate concerns regarding data quality due to the limitations discussed above, we can compare the dataset with the Residential Property Price Index (RPPI) [@bdcb2021technical]  published by the Brunei Darussalam Central Bank (BDCB).
--->
-<!-- A simple median price per square foot (PPSF) index can be calculated by aggregating the date by quarters. -->
-<!-- In so doing, missing values do not pose a significant issue as the index is calculated at the aggregate level. -->
-<!-- @fig-rppi shows the comparison between the RPPI and the PPSF index calculated from our dataset. -->
-<!-- The mean absolute error (MAE) between the two indices is calculated to be `{r} scales::percent(rppi_mae[1], accuracy = 0.01)`, indicating a high level of agreement between the two datasets. -->
-
-<!-- {{< embed analysis.qmd#fig-rppi >}} -->
-
 # Ethics
 
-> Data in Brief’s Guide for Authors contains detailed information on the ethical guidelines with which all authors must comply.
+<!-- > Data in Brief’s Guide for Authors contains detailed information on the ethical guidelines with which all authors must comply.
 In addition, we ask you to complete the relevant statement(s) below.
 Please delete those which are not relevant for your data.
-> If your work involved human subjects, please include a statement here confirming that the relevant informed consent was obtained from those subjects, if the research was carried out in accordance with the Declaration of Helsinki, and if it includes the Ethical committee approval and the protocol number.
+-->
+<!-- > If your work involved human subjects, please include a statement here confirming that the relevant informed consent was obtained from those subjects, if the research was carried out in accordance with the Declaration of Helsinki, and if it includes the Ethical committee approval and the protocol number.
 A copy of the consent form (in English) can be submitted either in a data repository or under the section ‘Consent form’ while submitting the manuscript to the system.
->
-> If your work involved animal experiments, please include a statement here confirming that those experiments complied with the ARRIVE guidelines and were carried out in accordance with the U.K.
+-->
+<!-- > -->
+<!-- > If your work involved animal experiments, please include a statement here confirming that those experiments complied with the ARRIVE guidelines and were carried out in accordance with the U.K.
 Animals (Scientific Procedures) Act, 1986 and associated guidelines; EU Directive 2010/63/EU for animal experiments; or the National Institutes of Health guide for the care and use of laboratory animals (NIH Publications No.
@@
 Note, the sex of the animals must be indicated, and, where appropriate, the influence (or association) of sex on the results of the study.
-> 
-> If your work involved data collected from social media platforms, please include a statement here confirming that a) informed consent was obtained from participants or that participant data has been fully anonymized, and b) the platform(s)’ data redistribution policies were complied with.
-> 
-> If none of the above, please include a statement confirming that the authors have read and follow the ethical requirements for publication in Data in Brief and confirming that the current work does not involve human subjects, animal experiments, or any data collected from social media platforms.
+-->
+<!-- >  -->
+<!-- > If your work involved data collected from social media platforms, please include a statement here confirming that a) informed consent was obtained from participants or that participant data has been fully anonymized, and b) the platform(s)’ data redistribution policies were complied with.
+-->
+<!-- >  -->
+<!-- > If none of the above, please include a statement confirming that the authors have read and follow the ethical requirements for publication in Data in Brief and confirming that the current work does not involve human subjects, animal experiments, or any data collected from social media platforms.
+-->
+
+The authors confirm that the current work does not involve human subjects, animal experiments, or data collected from social media platforms. 
+The data described in this article were obtained from publicly available, non-personal, and factual sources, including physical and digital newspapers and magazines.
+
+Web scraping from local property listings websites was conducted in compliance with ethical and legal considerations. 
+Specifically, data were not collected from behind login barriers, and the terms of service (ToS) for the websites did not explicitly prohibit web scraping. 
+Furthermore, the `robots.txt` files for the websites were reviewed, and any policies outlined there were adhered to.
+No social media data was used in this study.
+
+The data collected consisted exclusively of non-copyrightable factual information, such as property characteristics and spatial locations, and excluded any potentially copyrighted content such as images.
+To ensure privacy, no personally identifiable information, including specific property addresses, was scraped nor included in the dataset. 
+To this end, data from the description fields processed by the LLM are not included in the dataset, as they may contain sensitive information such as contact details and names of companies.
+Furthermore, we have ananoymised the real estate agents and agencies in the dataset.
 
@@
 
-https://www.elsevier.com/researcher/author/policies-and-guidelines/credit-author-statement
+<!-- https://www.elsevier.com/researcher/author/policies-and-guidelines/credit-author-statement  -->
+
+- **Haziq Jamil**: Conceptualization, Methodology, Software, Formal analysis, Data curation, Writing - Original Draft, Visualization, Supervision, Project administration, Funding acquisition.
+- **Amira Barizah Noorosmawie**: Software, Data curation, Writing - Original Draft.
+- **Hafeezul Waezz Rabu**: Software, Data curation, Writing - Original Draft.
+- **Lutfi Abdul Razak**: Conceptualization, Validation, Supervision, Funding acquisition.
 
 # Acknowledgements
-
-The authors gratefully acknowledge the contributions of Atikah Farhain Yahya, Nurulhanisah Abdul Manan, and Nina Zuhairi towards the collection and processing of the data contained within.
 
@@
 <!-- This research did not receive any specific grant from funding agencies in the public, commercial, or not-for-profit sectors. -->
+
+The authors gratefully acknowledge the contributions of Atikah Farhain Yahya, Nurulhanisah Abdul Manan, and Nina Zuhairi towards the collection and processing of the data contained within.
 
@@
 :::
+
+# Appendix {.unnunmbered}
+
+## Pairwise Correlation Plot of Numeric Variables
+
+{{< embed analysis.qmd#fig-corr >}}

### 2024-12-15 manuscript.qmd
Add abstract

@@
 abstract: |
-  Abstract here.
-engine: knitr
+  This article introduces the first publicly available dataset for analyzing the Brunei housing market, covering 31,495 property listings from 1993 to 2024.
+The dataset, curated from property advertisements in newspapers and online platforms, includes key attributes such as price, location, property type, and physical characteristics, enriched with area-level spatial information.
+Comprehensive and historical, it complements the Brunei Darussalam Central Bank’s Residential Property Price Index (RPPI), addressing the limitations of restricted access to raw RPPI data and its relatively short timeline since 2015.
+Data collection involved manual transcription from archival sources and automated web scraping using programmatic methods, supported by innovative cleaning with large language models (LLMs) to structure unformatted text.
+The dataset enables spatial and temporal analysis, with potential applications in economics, urban planning, and real estate research.
+While minor limitations exist, such as potential missing values and spatial coverage bias toward the Brunei-Muara district, this dataset provides a robust foundation for exploring housing market trends and informing policy decisions.
 ---
@@
 Changes in RPPI signal inflationary pressures, guiding central bank decisions on interest rates.
-Developing a house price index using advertised prices, as explored by @rachman2019residential, aligns with practices in other countries, such as the UK’s RightMove House Price Index [@hmlandregistry2023comparing; @europeancommission.eurostat.2013handbook].
+Developing a house price index using advertised prices, as explored by @rachman2019residential, aligns with practices in other countries, such as the UK’s RightMove House Price Index [@hmlandregistry2023comparing; @europeancommission.eurostat2013handbook].
 This dataset demonstrates how programmatic methods can automate what is typically a time-consuming and labor-intensive process.

### 2024-12-15 analysis.qmd
Add relevant R files (#2) and edit cleanup script

@@
 ---
-title: Plots and data summaries for manuscript
+title: Plots and Data Summaries
 author: Haziq Jamil

### 2024-12-15 manuscript.qmd
Add relevant R files (#2) and edit cleanup script

@@
 ---
-title: House price data in Brunei
+title: "From Archives to AI: A Dataset of Residential Property Listings in Brunei Darussalam"
 authors:
@@
 Combining the workflow with a looping mechanism allowed for the systematic extraction of data from multiple pages and websites, and thus the automated scraping process enabled efficient data collection over time.
+REWORD / REMOVE
 This process however was highly contingent on the consistency of the structure of the websites being scraped from.
 Over time, some websites shut down, while others changed their structure, requiring adjustments to the scraping scripts.
+[THAT'S WHY WE THOUGHT OF THE LLM THING...] 
 The web scraping process began in January 2022 and was conducted intermittently.
@@
 The primary goal was to extract the house characteristics of interest, specifically variables 7 to 15 as per @tbl-codebook, from the unstructured verbose descriptions scraped from property listing websites.
+FOR THE REST OF THE VARIABLES, THIS CAN BE DONE SYSTEMATICALLY (e.g. dates and other metadata like agent name).
 Each description was processed with a carefully designed prompt (@fig-llm-prompt) to ensure consistent output. 

### 2024-12-15 _cleanup.R

@@ -1,5 +1,7 @@
 # Cleanup script for Quarto
-files_to_remove <- c("elsarticle-num.bst", "manuscript.spl", "elsarticle.cls")
+files_to_remove <- list.files(
+  pattern = "\\.(bst|spl|cls|ipynb)$"
+)
 
 # Iterate over files and delete them if they exist
 for (file in files_to_remove) {

### 2024-12-15 llm.R

@@ -1,0 +1,111 @@
+library(tidyverse)
+# remotes::install_github("AlbertRapp/tidychatmodels")
+library(tidychatmodels)
+
+# Note: Before starting, ensure to install Ollama (https://ollama.com), and use
+# the terminal to download the model you wish to use. Here, we use llama3.1.
+
+# Sample description
+x <- "
+🌟 MODERN DOUBLE STOREY DETACHED HOUSE FOR SALE — TUNGKU 🌟
+
+🏡 Prime Location: Nestled in the heart of Kampong Tungku, just a 5-minute drive to The Mall Gadong, this property offers a blend of modern design and urban convenience.
+
+✨ Property Details:
+	•	Land Title: In-Perpetuity
+	•	Selling Price: $350,000
+	•	Land Size: 0.15 acre
+	•	House Size: 3,000 sq. ft
+	•	Bedrooms: 4
+	•	Bathrooms: 4
+	
+✨ House Features:
+	•	Ground Floor: Spacious Living & Dining Area, Wet & Dry Kitchen, 1 Guest Bedroom (en-suite), Guest Toilet, Laundry Room.
+	•	First Floor: Master Bedroom (en-suite with walk-in closet + balcony), 2 Bedrooms (en-suite).
+	
+🚗 Parking: Car porch fits 2 cars.
+🌳 Nearby Amenities: Schools, hospitals, cafes, and parks all within a 10-minute radius.
+
+📲 Contact Us Today!
+For viewing and further details, please contact:
+📞 +673 xxxxxxx | 📱 WhatsApp: +673 xxxxxxx
+📧 email@example.com
+
+🛠️ Services We Provide:
+	•	🏦 Bank Loan Application Assistance
+	•	📑 Legal Documentation Support
+	
+AGENT 🏘️ – Your Trusted Real Estate Partner
+"
+
+# The prompt
+the_prompt <- "
+The following is the description from a property sale listing in Brunei. This description will contain the information about the property, including its characteristics, price, and location. However, some of these descriptions may not contain property listings, and instead contain other or no information at all.
+
+In the case where this description is in fact a property listing, I would like you to extract the following information:
+
+1. Location / area of the property in Brunei, CHARACTER.
+2. Price of the property in Brunei Dollars, NUMERIC.
+3. Type of property, CHARACTER -- select from Detached, Semi-Detached, Terrace, Apartment, or Land.
[…]

### 2024-12-15 webscrape.R

@@ -1,0 +1,66 @@
+library(tidyverse)
+library(rvest)
+
+# This is how you get read the HTML into R
+url <- "https://BRUNEIPROPERTYLISTINGWEBSITE.COM/blablabla"  # change this to the actual URL
+html <- read_html(url)
+
+# Extract the house prices
+prices <-
+  html |>
+  html_elements(".property-price") |>
+  html_text2()
+
+# Clean up
+prices <- 
+  str_remove_all(prices, "[^0-9]") |>  # Remove non-numeric characters
+  as.integer()
+
+# Do same thing for number of beds, baths, location, and other remarks
+beds <-
+  html |>
+  html_elements(".property-bed") |>
+  html_text2() |>
+  as.integer()
+
+baths <-
+  html |>
+  html_elements(".property-bath") |>
+  html_text2() |>
+  as.integer()
+
+location <-
+  html |>
+  html_elements(".property-address") |>
+  html_text2()
+
+# Put it all in a data frame
+hsp_df <- tibble(
+  location = location
+  price = prices,
+  beds = beds,
+  baths = baths,
+)
+
+# Some pages require you to click a "load more" button to see more data
+links <-
+  html |>
+  html_elements(".property-link") |>
+  html_attr("href")
+
+# Create a function that can extract the info I want from a single page
+extract_info <- function(i) {
+  link <- paste0("https://BRUNEIPROPERTYLISTINGWEBSITE.COM", properties[i])  # change this URL
+  html <- read_html(link)
+  out <-
+    html |>
+    html_elements("p") |>  # The descriptions are the .p element
+    html_text2()
+  out[1]
+}
+
+res <- map(
+  .x = seq_along(properties),
+  .f = extract_info,
+  .progress = TRUE
+)

### 2024-12-15 manuscript.qmd
Tweaks to manuscript metadata

@@
 ---
-title: "From Archives to AI: A Dataset of Residential Property Listings in Brunei Darussalam"
+title: "From Archives to AI: Residential Property Listings Across Three Decades in Brunei Darussalam"
 authors:
@@
 While minor limitations exist, such as potential missing values and spatial coverage bias toward the Brunei-Muara district, this dataset provides a robust foundation for exploring housing market trends and informing policy decisions.
+keywords:
+  - Housing Market
+  # - Real Estate
+  - Brunei
+  - Property Listings
+  # - Advertisements
+  - Spatial Data
+  - Web Scraping
+  - Large Language Models
 ---

### 2024-12-15 llm.R

@@ -5,7 +5,7 @@ library(tidychatmodels)
 # Note: Before starting, ensure to install Ollama (https://ollama.com), and use
 # the terminal to download the model you wish to use. Here, we use llama3.1.
 
-# Sample description
+# Sample description (artificially created)
 x <- "
 🌟 MODERN DOUBLE STOREY DETACHED HOUSE FOR SALE — TUNGKU 🌟
 
@@ -85,6 +85,13 @@ clean_desc <- function(caption) {
     dplyr::pull(message)
 }
 
+# Test Ollama works
+create_chat("ollama") |>
+  add_model("llama3.1") |>
+  add_message("Hello, how are you?") |>
+  perform_chat() |>
+  extract_chat()
+
 # Test the function
 tictoc::tic()
 y <- clean_desc(x)
@@ -101,7 +108,8 @@ tictoc::toc()
 
 # In any case, to convert the (cleaned) character vector to a data frame, we
 # separate the strings by ';' as follows:
-tibble(clean = y) |>
+df <-
+  tibble(clean = y) |>
   separate(
     clean,
     into = c("location", "price", "type", "tenure", "status", "plot_area", "floor_area", "storeys", "beds", "baths"),

### 2024-12-15 analysis.qmd
Rearrange districts

@@
       levels = c("1", "2", "3+")
-    )
+    ),
+    district = gsub("Brunei Muara", "Brunei-Muara", district),
+    district = factor(district, levels = c("Brunei-Muara", "Belait", "Tutong", "Temburong"))
   ) |>

### 2025-01-15 manuscript.qmd
Update manuscript

@@
 Covering data from 1993 to 2024, this dataset allows for the study of long-term housing trends in Brunei.
-Its detailed spatial information enables analysis at various levels, from kampong to mukim, providing insights into local patterns and urban development over time.
+The spatial information available enables analysis at various administrative levels, providing insights into local patterns and urban development over time.
 This historical depth is particularly valuable given the lack of previous data before the establishment of the Residential Property Price Index (RPPI) [@bdcb2021technical] in 2015.
@@
 - **Influence on economic and monetary policies**.
-Analysing the real estate market is crucial because the RPPI plays a key role in shaping monetary policy and assessing economic stability.
-Changes in RPPI signal inflationary pressures, guiding central bank decisions on interest rates.
+Analysing the real estate market is crucial because the RPPI can potentially play a key role in shaping monetary policy and assessing economic stability.
+Changes in RPPI signal inflationary pressures, providing guidance to the central bank decisions.
 Developing a house price index using advertised prices, as explored by @rachman2019residential, aligns with practices in other countries, such as the UK’s RightMove House Price Index [@hmlandregistry2023comparing; @europeancommission.eurostat2013handbook].
-This dataset demonstrates how programmatic methods can automate what is typically a time-consuming and labor-intensive process.
+This dataset demonstrates how programmatic methods can automate what is typically a time-consuming and labour-intensive process.
 
@@
 To demonstrate the quality of the dataset, we compared it with the Residential Property Price Index (RPPI) [@bdcb2021technical]  published by the Brunei Darussalam Central Bank (BDCB).
-A simple median price per square foot (PPSF) index can be calculated by aggregating the date by quarters.
-In so doing, missing values do not pose a significant issue as the index is calculated at the aggregate level.
+A simple median price per square foot (PPSF) index can be calculated by aggregating the data by quarters.
+<!-- @fig-rppi shows the median smoothed PPSF by property type using a 24-month (8-quarter) rolling window. -->
+<!-- Generally the property price trends reflect macroeconomic conditions. -->
+This approach minimises the impact of missing values, as the index is based on aggregated data.
 @fig-rppi shows the comparison between the RPPI and the PPSF index calculated from our dataset.
@@
 Rare errors were spotted due to model hallucinations (despite setting the LLM temperature to the lowest setting), but these are typically minor and unlikely to significantly impact the overall analysis.
-Large errors on the other hand were corrected manually, by filtering for outliers or inconsistencies in the variables.
+Large errors on the other hand were corrected manually, by filtering for outliers (values exceeding three standard deviations from the mean in magnitude) or inconsistencies in the variables.
 Overall, the LLM was found to be a valuable tool for extracting structured information from unstructured text, significantly reducing the time and effort required for data cleaning.
@@
 This simply reflects the district’s higher population and greater volume of property transactions [@jamil2024spatiotemporal] which could bias analyses toward this region.
+While confidence in the data quality is high from 2015 to 2024, property price trends between 1993 and 2014 cannot be fully verified. 
+Nonetheless, this study serves as a valuable starting point, but access to administrative transaction data would significantly enhance future research.
 

### 2025-01-16 manuscript.qmd
Finish reviewing manuscript for submission

@@
 abstract: |
-  This article introduces the first publicly available dataset for analyzing the Brunei housing market, covering 31,495 property listings from 1993 to 2024.
-The dataset, curated from property advertisements in newspapers and online platforms, includes key attributes such as price, location, property type, and physical characteristics, enriched with area-level spatial information.
+  This article introduces the first publicly available data set for analyzing the Brunei housing market, covering 31,495 property listings from 1993 to 2024.
+The data set, curated from property advertisements in newspapers and online platforms, includes key attributes such as price, location, property type, and physical characteristics, enriched with area-level spatial information.
 Comprehensive and historical, it complements the Brunei Darussalam Central Bank’s Residential Property Price Index (RPPI), addressing the limitations of restricted access to raw RPPI data and its relatively short timeline since 2015.
 Data collection involved manual transcription from archival sources and automated web scraping using programmatic methods, supported by innovative cleaning with large language models (LLMs) to structure unformatted text.
-The dataset enables spatial and temporal analysis, with potential applications in economics, urban planning, and real estate research.
-While minor limitations exist, such as potential missing values and spatial coverage bias toward the Brunei-Muara district, this dataset provides a robust foundation for exploring housing market trends and informing policy decisions.
+The data set enables spatial and temporal analysis, with potential applications in economics, urban planning, and real estate research.
+While minor limitations exist, such as potential missing values and spatial coverage bias toward the Brunei-Muara district, this data set provides a robust foundation for exploring housing market trends and informing policy decisions.
 keywords:
   - Housing Market
-  # - Real Estate
   - Brunei
   - Property Listings
-  # - Advertisements
   - Spatial Data
@@
 Since data articles are templated, we require that you complete and submit the template.
-Data in Brief will not accept any submissions that contain datasets with insufficient variables or samples.
+Data in Brief will not accept any submissions that contain data sets with insufficient variables or samples.
 -->
@@
 Each bullet point should be a maximum of 150 words long, and should not include conclusions or inferences: -->
-
 <!-- - Why are these data valuable? -->
@@
 - **First of its kind for Brunei**.
-This dataset enables comprehensive spatial and temporal analysis of the Brunei housing market.
-To our knowledge, no other publicly available dataset exists for this purpose, making it a significant contribution to the field.
-Previous studies on Brunei's housing have been limited to recent or non-spatial data [@shabunko2014developing;@ng2022characterising;@jamil2025leveraging], or qualitative in nature due to the lack of a structured dataset [@hassan2011cultural;@hassan2023sociocultural].
-This aligns with the growing trend of using data analytics in the real estate industry [@braesemann2020proptech;@delisle2020big].
+This data set enables comprehensive spatial and temporal analysis of the Brunei housing market.
+To our knowledge, no other publicly available data set exists for this purpose, making it a significant contribution to housing market research.
+Previous studies on Brunei's housing have been limited to recent or non-spatial data [@shabunko2014developing; @ng2022characterising; @jamil2025leveraging], or qualitative in nature due to the lack of a structured data set [@hassan2011cultural; @hassan2023sociocultural].
+This aligns with the growing trend of using data analytics in the real estate industry [@braesemann2020proptech; @delisle2020big].
 
 - **Historical and spatial insights**.
-Covering data from 1993 to 2024, this dataset allows for the study of long-term housing trends in Brunei.
+Covering data from 1993 to 2024, this data set allows for the study of long-term housing trends in Brunei.
 The spatial information available enables analysis at various administrative levels, providing insights into local patterns and urban development over time.
@@
 Changes in RPPI signal inflationary pressures, providing guidance to the central bank decisions.
-Developing a house price index using advertised prices, as explored by @rachman2019residential, aligns with practices in other countries, such as the UK’s RightMove House Price Index [@hmlandregistry2023comparing; @europeancommission.eurostat2013handbook].
-This dataset demonstrates how programmatic methods can automate what is typically a time-consuming and labour-intensive process.
+Developing a house price index using advertised prices, as explored by @rachman2019residential, aligns with practices in other countries, such as the UK’s House Price Index developed by Rightmove PLC [@hmlandregistry2023comparing; @europeancommission.eurostat2013handbook].
+This data set demonstrates how computational methods can automate what is typically a time-consuming and labour-intensive process.
 
 - **Opportunities for handling of missing data**.
-While the dataset has complete information for key variables such as price, date, and spatial variables, missing information on house characteristics creates opportunities for further research.
+While the data set has complete information for key variables such as price, date, and spatial variables, missing information on house characteristics creates opportunities for further research.
 Evidently, house characteristics are inherently correlated (see [@fig-corr]), so imputation from observed correlations seems highly promising.
-With the spatial information present, this opens avenues for developing methodological approaches for handling missing data.
-Rather than being a limitation, the incomplete data in some variables encourages methodological innovation and exploration.
+With the spatial information present, this opens avenues for developing methodological approaches for handling missing data, encouraging innovation and exploration in this area.
 
@@
 This method significantly reduced the time and effort required for data cleaning.
-It can also be applied to other datasets with unstructured text, such as social media or document archives, to extract valuable information for analysis.
+It can also be applied to other data sets with unstructured text, such as social media or document archives, to extract valuable information for analysis.
 
@@
 
-<!-- Please describe your original motivation and context behind compiling this dataset.
+<!-- Please describe your original motivation and context behind compiling this data set.
 For example, briefly include information on the theoretical or methodological background against which you generated the data.
-Do not make concluding, interpretive, or otherwise inferential statements about the dataset.
+Do not make concluding, interpretive, or otherwise inferential statements about the data set.
 In case your data article is related to an original research article, please briefly describe how the data article adds value to the published article (Max.
@@
 
-The housing market is a key indicator of economic health and social well-being, yet comprehensive and publicly accessible datasets in Brunei remain limited.
-To our knowledge, this is the first dataset of its kind in Brunei, motivated by the need to fill the gap in publicly available data on the local housing market.
+The housing market is a key indicator of economic health and social well-being, yet comprehensive and publicly accessible data sets in Brunei remain limited. 
+As far as we are aware, this is the first data set of its kind in Brunei, motivated by the need to fill the gap in publicly available data on the local housing market.
 
-Currently, the Brunei Darussalam Central Bank (BDCB) produces a Residential Property Price Index (RPPI) [@bdcb2021technical] using data sourced from financial institutions, such as bank loan datasets.
+Currently, the Brunei Darussalam Central Bank (BDCB) produces a Residential Property Price Index (RPPI) [@bdcb2021technical] using data sourced from financial institutions, such as bank loan data sets.
 While the RPPI is published quarterly, the underlying raw data is not publicly available due to privacy restrictions. 
 This limits research opportunities and transparency in understanding broader housing market trends. 
-Furthermore, the RPPI only began in 2015, leaving a significant gap in historical housing data.
+Furthermore, since the RPPI only began in 2015, historical housing data for Brunei is lacking.
 
-Our dataset addresses these challenges by providing a cost-effective and timely means to collect and analyze housing market data.
-Covering records from 1993 onward, it offers historical depth that complements and extends beyond the RPPI.
+We address these challenges by providing a cost-effective and timely means to collect and analyse housing market data. 
+Covering records from 1993 onward, it offers historical depth that complements–and extends beyond–the RPPI. 
 It is valuable not only for tracking property price trends but also for advancing research in economics, urban planning, and real estate, supporting informed decision-making across sectors.
@@
 
-<!-- > This section describes your dataset.
-Refer to all the data folders, subfolders, and files in the repository individually, irrespective of whether they relate to raw or analyzed data, and make sure that the reader can follow the structure of your dataset.
+<!-- This section describes your data set.
+Refer to all the data folders, subfolders, and files in the repository individually, irrespective of whether they relate to raw or analyzed data, and make sure that the reader can follow the structure of your data set.
 -->
-<!-- > Please use visual aids (such as tables, graphs, or figures with captions) to familiarize the reader with your dataset, but do not offer background, interpretations, or conclusions. -->
+<!-- Please use visual aids (such as tables, graphs, or figures with captions) to familiarize the reader with your data set, but do not offer background, interpretations, or conclusions. -->
 
@@
 The data has been curated into a single Comma-Separated Values (CSV) file named `hspbn_2024-12-12.csv`. 
-The dataset contains `{r} scales::comma(nrow(hsp))` property listing records which are enriched with area-level geotagged spatial information, spanning a period of `{r} max(years) - min(years) + 1` years from `{r} format(min(hsp$date), "%b %Y")` to `{r} format(max(hsp$date), "%b %Y")`.
-The `{r} scales::comma(ncol(hsp))` columns of this dataset capture information for each property listing as detailed in @tbl-codebook below.
+The data set contains `{r} scales::comma(nrow(hsp))` property listing records which are enriched with area-level geotagged spatial information, spanning a period of `{r} max(years) - min(years) + 1` years from `{r} format(min(hsp$date), "%b %Y")` to `{r} format(max(hsp$date), "%b %Y")`.
+The `{r} scales::comma(ncol(hsp))` columns of this data set capture information for each property listing as detailed in @tbl-codebook below.
 
@@
 #| label: tbl-codebook
-#| tbl-cap: Codebook for the house price dataset.
+#| tbl-cap: Codebook for the house price data set.
 readxl::read_xlsx("data/codebook.xlsx") |>
@@
 
-The dataset includes a range of property characteristics suitable for exploring the relationship between property attributes and prices.
-This section clarifies and provides context for the key variables in the dataset.
+The data set includes a range of property characteristics suitable for exploring the relationship between property attributes and prices. 
+This section clarifies and provides context for the key variables in the data set.
 
 Brunei’s private residential property market offers a variety of options, including detached houses, townhouses, and apartments [@hassan2023sociocultural]. 
-Based on this, property types have been categorised into four main groups --
-Detached, Semi-Detached, Terrace, and Apartment -- to accurately reflect the diversity of property types in Brunei.
-Additionally, there are a small number of records that reflect land sales, which are categorised accordingly as "Land".
+Based on this, property types have been categorised into four main groups–Detached, Semi-Detached, Terrace, and Apartment–to accurately reflect the diversity of property types in Brunei.
+Additionally, there are a small number of records that reflect listings for land, which are categorised accordingly as "Land".
 
 Property tenure refers to the legal terms under which a person holds ownership or occupancy rights to a property. 
-In Brunei, property tenure can be classified into three main categories: 
-Freehold (in perpetuity), Leasehold, and Strata.
-The latter of which refers to a form of ownership where individuals own a portion of a property, such as an apartment, and share ownership of common areas.
+In Brunei, property tenure can be classified into three main categories: Freehold (in perpetuity), Leasehold, and Strata. 
+The latter two refer to a limited time-limited ownership, although details about the remaining duration of the tenure are almost never included in property listings. 
+Strata titles differ from Leasehold titles in that they grant ownership of a specific portion of a property, such as an apartment, while sharing ownership of common areas.
 
-The dataset also includes information on the status of the property listing, indicating whether the advertisement refers to a proposed development, a newly completed development, or a property being resold.
-This categorical variable may be useful for analyzing price differences across different types of listings.
+The data set also includes information on the status of the property listing, indicating whether the advertisement refers to a proposed development, a newly completed development, or a property being resold.
+This categorical variable may be useful for analysing price differences across different types of listings. 
+While the exact age of properties being resold would be invaluable for such analyses, this information is rarely included in advertisements. 
+Instead, the listing status may serve as a useful proxy for property age.
 
-The numerical variables in the dataset are plot area, floor area, storeys, beds, and baths, each providing information on the physical attributes of the property. 
-Note that plot area is measured in acres, while floor area is in square feet, as these are the common units of measurement used in Brunei. 
-Users of this dataset may choose to convert these units as needed for their analysis.
+The numerical variables in the data set are plot area, floor area, storeys, beds, and baths, each providing information on the physical attributes of the property. 
+Note that plot area is measured in acres, while floor area in square feet, as these are the units most familiar and commonly used in Brunei. 
+Users of this data set may choose to convert these units as needed for their analysis.
 
@@
 
-::: {.content-visible when-format="html"}
-::: {.column-page}
+:::: {.content-visible when-format="html"}
+::: column-page
 {{< embed analysis.qmd#tbl-summary >}}
 :::
-:::
+::::
 
-::: {.content-visible unless-format="html"}
-::: {.landscape}
+:::: {.content-visible unless-format="html"}
+::: landscape
 {{< embed analysis.qmd#tbl-summary >}}
 :::
-:::
+::::
 
@@
 In Brunei Darussalam, the administrative areas are organised hierarchically into three levels. 
-At the smallest level is the *kampong*, which refers to a village or neighbourhood.
-Several kampongs grouped together form a *mukim*, which serves as a sub-district administrative area.
-Finally, multiple mukims are nested within a *district*, the largest administrative unit, of which Brunei has four: Brunei-Muara, Belait, Tutong, and Temburong.
-In our dataset, each property listing is associated with a specific kampong, mukim, and district, allowing for spatial analysis at different scales.
+At the smallest level is the *kampong*, the Malay word for village.
+While a typical village refers to a traditional rural settlement, it is also used to describe an urbanised area located within or near the capital city or a town. 
+It may even refer to a part of public housing estates. Several kampongs grouped together form a *mukim*, which serves as a sub-district administrative area. 
+Finally, multiple mukims are nested within a *district*, the largest administrative unit, of which Brunei has four:
+Brunei-Muara, Belait, Tutong, and Temburong. 
+In our data set, each property listing is associated with a specific kampong, mukim, and district, allowing for spatial analysis at different scales.
 
-Importantly, the names of the kampongs, mukims, and districts have been harmonised with a standardised naming convention to ensure consistency across the dataset.
+Importantly, the names of the kampongs, mukims, and districts have been harmonised with a standardised naming convention to ensure consistency across the data set. 
 This also allows for ease of integration into Geographic Information Systems (GIS) software for spatial analysis and visualisation, namely the `{bruneimap}` R package [@jamil2024bruneimap].
@@
 
-The date variable in the dataset refers to the date on which the property listing was obtained. 
+The date variable in the data set refers to the date on which the property listing was obtained. 
 It is important to note that this is not the date the property was sold, nor does it necessarily reflect the precise timing of other transactions related to the property. 
@@
 For analysis, we recommend aggregating data by quarters, as represented by the quarter variable. 
-This aggregation helps address potential issues like missing data (see section below) and provides a more stable and robust representation of market trends, making it suitable for temporal analysis of the housing market.
+This aggregation helps address potential issues like missing data (see subsection below) and provides a more stable and robust representation of market trends, making it suitable for temporal analysis of the housing market.
 
@@
 
-This dataset endeavours to provide complete information regarding the listing date, spatial information, advertised price, and metadata.
+This data set endeavours to provide complete information regarding the listing date, spatial information, advertised price, and metadata. 
 Nonetheless, we hereby report that missing values are present across various **property characteristics**, including type, tenure, status, plot area, floor area, storeys, beds, and baths. 
@@
 
-To demonstrate the quality of the dataset, we compared it with the Residential Property Price Index (RPPI) [@bdcb2021technical]  published by the Brunei Darussalam Central Bank (BDCB).
+To demonstrate the quality of the data set, we compared it with the Residential Property Price Index (RPPI) [@bdcb2021technical] published by the Brunei Darussalam Central Bank (BDCB). 
 A simple median price per square foot (PPSF) index can be calculated by aggregating the data by quarters. 
@@
 This approach minimises the impact of missing values, as the index is based on aggregated data. 
-@fig-rppi shows the comparison between the RPPI and the PPSF index calculated from our dataset.
-The mean absolute error (MAE) between the two indices is calculated to be `{r} scales::percent(rppi_mae[1], accuracy = 0.01)`, indicating a high level of agreement between the two datasets.
+@fig-rppi shows the comparison between the RPPI and the PPSF index calculated from our data set. 
+The mean absolute error (MAE) between the two indices is calculated to be `{r} scales::percent(rppi_mae[1], accuracy = 0.01)`, indicating a good level of agreement between the two data sets.
 
@@
 
-<!-- > This section describes how you acquired the data.
+<!-- This section describes how you acquired the data.
 Provide a complete description of the experimental design and methods used to acquire these data.
@@
 -->
-<!-- >  -->
-<!-- > It is important that this section is as comprehensive as possible.
+<!-- It is important that this section is as comprehensive as possible.
 There is no character limit, and you may use illustrative figures or tables; however, please do not offer background, interpretations, or conclusions.
@@
 In this section we describe the data collection process, which involved either a manual transcription of property listings from newspapers, or web scraping of online property agent listings. 
-In the later years, a large language model (LLM) was also employed to perform data cleaning on the web scraped data.
 The data collection method varied over the years due to the availability of data sources and the evolution of technology. 
-@tbl-avail details which method was used for each year in the dataset, and whether the data was subjected to LLM post-processing.
+For the later years, a large language model (LLM) was also employed to perform data cleaning on the web scraped data. 
+@tbl-avail details which method was used for each year in the data set, and whether the data was subjected to LLM post-processing.
 
@@
 The primary sources of the property listings were local newspapers and magazines. 
-Physical copies were accessed through the National Archive of Brunei Darussalam, while digital versions, which are digitized replicas of the physical newspapers, were obtained online. 
+Physical copies were accessed through the National Archive of Brunei Darussalam, while digital versions, which are digitised replicas of the physical newspapers, were obtained online. 
 These digital formats could not be scraped due to their lack of structured data, necessitating manual transcription.
@@
 However, reviewing every single daily edition was not practical and would increase the likelihood of recording duplicate listings, thus necessating a sampling strategy. 
-The sampling was done as follows.
-Three newspaper editions per week were selected, and the classifieds section was reviewed for property listings. 
+The sampling was done as follows. Three newspaper editions per week were selected, and the classifieds section was reviewed for property listings. 
 When a listing was found, it was recorded after careful filtering to ensure it was unique. 
 This manual filtering process involved cross-checking based on the real estate agent, house characteristics, price, location, and date proximity. 
-To avoid duplication, the same house listing was typically not recorded more than once within a quarter. 
+To avoid duplication, the same house listing was not recorded more than once within a quarter. 
 This process yielded roughly the same number of listings per year as the earlier years.
@@
 
-To compile additional property data for the study beyond manual data collection, web scraping was employed using the R programming language, leveraging the `{rvest}` package [@wickham2024rvest]. 
+To compile additional property data for the study beyond manual data collection, web scraping was employed using the R programming language, making use of the `{rvest}` package [@wickham2024rvest].
 This method enabled the systematic extraction of structured information from various local property listing websites such as panvilla.com (now defunct), bruhome.com, and bruneiproperty.com.bn.
@@
 
-::: {#fig-web-scrape layout-ncol=1}
-
+::::: {#fig-web-scrape layout-ncol="1"}
 ::: {#fig-mockup-listing}
@@
 Illustration of a property listing from a typical Bruneian property portal. Attribution: Freepik.
-:::
+:::::
 
@@
 
-Each webpage displayed a fixed number of listings (e.g., 128 per page). 
+Each webpage displayed a fixed number of listings (e.g. 128 per page). 
 To scrape all pages, a loop was created to iterate through each page by modifying the URL (such as with an `&offset=<number>` parameter, where `<number>` represented the cumulative number of listings already scraped).
 
-Extracted data required some cleaning to standardize formats for analysis. 
-For instance:
+Extracted data required some cleaning to standardise formats for analysis. 
+Specifically:
 
-- `price` varibales were cleaned by removing non-numeric characters and converted to integers.
+- `price` variables were cleaned by removing non-numeric characters and converted to integers.
 - `beds` and `baths` were converted to integers.
@@
 
-<!-- The typical workflow for extracting data from a single property listing involved: -->
-
-<!-- 1.	Read the HTML: The read_html() function from {rvest} was used to load webpage content. -->
-<!-- 2.	Extract Key Elements: Functions like html_elements() and html_text2() targeted specific tags to extract data such as prices, beds, baths, and locations. -->
-<!-- 3.	Clean and Standardize: Extracted data were cleaned and converted to appropriate formats (e.g., numeric for prices, integers for bedrooms and bathrooms). -->
-<!-- 4.	Iterate Through Pages: A looping mechanism was employed to access subsequent pages by dynamically appending the offset parameter to the URL. -->
-<!-- 5.	Extract Additional Information: For individual property pages, a custom function was created to navigate links and extract further details using a mapping function (map()). -->
-
-Combining the workflow with a looping mechanism allowed for the systematic extraction of data from multiple pages and websites, and thus the automated scraping process enabled efficient data collection over time.
-REWORD / REMOVE
-This process however was highly contingent on the consistency of the structure of the websites being scraped from.
-Over time, some websites shut down, while others changed their structure, requiring adjustments to the scraping scripts.
-[THAT'S WHY WE THOUGHT OF THE LLM THING...] 
-The web scraping process began in January 2022 and was conducted intermittently.
 Data from 2012 up until the present (December 2024) were managed to be collected using this method, averaging around 1,500 listings per year. 
+While highly efficient, this process relied heavily on the consistency of the site structure of the source webpages.
+Changes to website layouts or closures over time required significant updates to the scraping scripts.
+To overcome these issues, alternative approaches, such as using Large Language Models (LLMs) were considered. 
+This is explained in the next subsection.
 
@@
 
-As mentioned, the web scraping process also captured unstructured information from the property descriptions, which often contained valuable details not captured in the primary fields.
+As previously mentioned, the web scraping process also captured unstructured information from the property descriptions, which often contained valuable details not captured in the primary fields. 
 In this subsection, we detail the data cleaning process using a pre-trained large language model (LLM) to extract structured information from the unstructured text. 
-The LLM used was Llama 3.1 with 8B parameters [@grattafiori2024llama], accessed using the `{tidychatmodels}` R package [@rapp2024tidychatmodels] via the Ollama^[<https://github.com/ollama/ollama>] API, a local interface platform to the LLM.
+The LLM used was Llama 3.1 with 8B parameters [@grattafiori2024llama], accessed using the `{tidychatmodels}` R package [@rapp2024tidychatmodels] via the Ollama[^1] API, a local interface platform to the LLM.
+
+[^1]: <https://github.com/ollama/ollama>
 
 The primary goal was to extract the house characteristics of interest, specifically variables 7 to 15 as per @tbl-codebook, from the unstructured verbose descriptions scraped from property listing websites.
-FOR THE REST OF THE VARIABLES, THIS CAN BE DONE SYSTEMATICALLY (e.g. dates and other metadata like agent name).
 Each description was processed with a carefully designed prompt (@fig-llm-prompt) to ensure consistent output. 
@@
 The LLM prompt to clean descriptions obtained from web scraping.
-
 :::
 
-The unstructured descriptions were fed into the model one at a time using a loop, with the LLM extracting and returning the relevant details. 
-Note that this loop was not parallelided due to the computational resources required by the LLM.
-The cleaned results were then parsed and stored in a data frame, which was then subjected to data-type validation to ensure conformity with the existing dataset.
-It takes on average 2.12 seconds to process a single description running on Apple MacBook Air M2 Silicon on Chip (SoC) and System in Chip (SiP) processors with 16GB RAM.
+The verbose descriptions were fed into the model one at a time using a loop, with the LLM extracting and returning the relevant details. 
+Note that this loop was not parallelised due to the computational resources required by the LLM. 
+The cleaned results were then parsed and stored in a data frame, which was then subjected to manual data-type validation to ensure conformity with the existing data set. 
+It takes, on average, 2.12 seconds to process a single description running on Apple MacBook Air M2 Silicon on Chip (SoC) and System in Chip (SiP) processors with 16GB RAM. 
 We processed 4,820 descriptions in total from 2020 to 2024 using this method, with a runtime of approximately three hours.
@@
 This is the same format used by the R package `{bruneimap}` [@jamil2024bruneimap].
-The CSV file `bn_kpg_level_data.csv` obtained from this package was used as a reference to standardise the kampong names in the dataset, which conveniently also included the mukim and district names for each kampong.
+The CSV file `bn_kpg_level_data.csv` obtained from this package was used as a reference to standardise the kampong names in the data set, which conveniently also included the mukim and district names for each kampong.
 
 The majority of house listings in Brunei specify the property location using the kampong name, the smallest administrative unit in the country. 
-The task in hand was then to match these kampong names in the dataset with the standardised names in the reference file. 
+The task in hand was then to match these kampong names in the data set with the standardised names in the reference file. 
 Several challenges were encountered during this process, including:
@@
 
-<!-- > Describe any limitations related to the data described in this article.
-These could be any problems you faced during data collection or curation, limited quality or size of dataset, data biases, etc., but should not include limitations of analysis conducted or interpretation (Max.
+<!-- Describe any limitations related to the data described in this article.
+These could be any problems you faced during data collection or curation, limited quality or size of data set, data biases, etc., but should not include limitations of analysis conducted or interpretation (Max.
 200 words).
@@
 Despite efforts to ensure data quality, some limitations remain.
-While duplicate listings were carefully reviewed and removed, there remains a slight possibility that a duplicated records still exist in the dataset. 
-Additionally, the spatial data coverage is heavily skewed towards the Brunei-Muara district, which accounts for `{r} scales::percent(prop.table(table(hsp$district))[2], accuracy = 0.1)` of the listings.
-This simply reflects the district’s higher population and greater volume of property transactions [@jamil2024spatiotemporal] which could bias analyses toward this region.
-While confidence in the data quality is high from 2015 to 2024, property price trends between 1993 and 2014 cannot be fully verified. 
-Nonetheless, this study serves as a valuable starting point, but access to administrative transaction data would significantly enhance future research.
+Duplicate listings were carefully reviewed and removed, though there remains a slight possibility that duplicated records still exist in the data set.
+The spatial data coverage is also heavily skewed towards the Brunei-Muara district, which accounts for `{r} scales::percent(prop.table(table(hsp$district))[2], accuracy = 0.1)` of the listings. 
+This is a reflection of the district’s higher population and greater volume of property transactions [@jamil2024spatiotemporal], which may bias analyses toward this region. 
+Furthermore, while we have confidence in the data quality from 2015 to 2024, property price trends between 1993 and 2014 cannot be fully verified.
+Nonetheless, this study serves as a valuable starting point.
+Future research could benefit greatly from access to administrative transaction data, which would allow for more comprehensive and accurate analyses.
 
@@
 Finally, while significant effort was made to harmonise spatial data, the matching of kampong names to standardised references may not be entirely error-free. 
-However, aggregation to the mukim level provides a reliable alternative for spatial analyses, ensuring that the dataset remains valuable for research and analysis.
+However, aggregation to the mukim level provides a reliable alternative for spatial analyses, ensuring that the data set remains valuable for research and analysis.
 
@@
 
-<!-- > Data in Brief’s Guide for Authors contains detailed information on the ethical guidelines with which all authors must comply.
+<!-- Data in Brief’s Guide for Authors contains detailed information on the ethical guidelines with which all authors must comply.
 In addition, we ask you to complete the relevant statement(s) below.
@@
 -->
-<!-- > If your work involved human subjects, please include a statement here confirming that the relevant informed consent was obtained from those subjects, if the research was carried out in accordance with the Declaration of Helsinki, and if it includes the Ethical committee approval and the protocol number.
+<!-- If your work involved human subjects, please include a statement here confirming that the relevant informed consent was obtained from those subjects, if the research was carried out in accordance with the Declaration of Helsinki, and if it includes the Ethical committee approval and the protocol number.
 A copy of the consent form (in English) can be submitted either in a data repository or under the section ‘Consent form’ while submitting the manuscript to the system.
 -->
-<!-- > -->
-<!-- > If your work involved animal experiments, please include a statement here confirming that those experiments complied with the ARRIVE guidelines and were carried out in accordance with the U.K.
+<!-- If your work involved animal experiments, please include a statement here confirming that those experiments complied with the ARRIVE guidelines and were carried out in accordance with the U.K.
 Animals (Scientific Procedures) Act, 1986 and associated guidelines; EU Directive 2010/63/EU for animal experiments; or the National Institutes of Health guide for the care and use of laboratory animals (NIH Publications No.
@@
 -->
-<!-- >  -->
-<!-- > If your work involved data collected from social media platforms, please include a statement here confirming that a) informed consent was obtained from participants or that participant data has been fully anonymized, and b) the platform(s)’ data redistribution policies were complied with.
+<!-- If your work involved data collected from social media platforms, please include a statement here confirming that a) informed consent was obtained from participants or that participant data has been fully anonymized, and b) the platform(s)’ data redistribution policies were complied with.
 -->
-<!-- >  -->
-<!-- > If none of the above, please include a statement confirming that the authors have read and follow the ethical requirements for publication in Data in Brief and confirming that the current work does not involve human subjects, animal experiments, or any data collected from social media platforms.
+<!-- If none of the above, please include a statement confirming that the authors have read and follow the ethical requirements for publication in Data in Brief and confirming that the current work does not involve human subjects, animal experiments, or any data collected from social media platforms.
 -->
@@
 Furthermore, the `robots.txt` files for the websites were reviewed, and any policies outlined there were adhered to.
-No social media data was used in this study.
 
 The data collected consisted exclusively of non-copyrightable factual information, such as property characteristics and spatial locations, and excluded any potentially copyrighted content such as images.
-To ensure privacy, no personally identifiable information, including specific property addresses, was scraped nor included in the dataset. 
-To this end, data from the description fields processed by the LLM are not included in the dataset, as they may contain sensitive information such as contact details and names of companies.
-Furthermore, we have ananoymised the real estate agents and agencies in the dataset.
+To ensure privacy, no personally identifiable information, including specific property addresses, was scraped nor included in the data set. 
+To this end, data from the description fields processed by the LLM are not included in the data set, as they may contain sensitive information such as contact details and names of companies. 
+Furthermore, we have anonymised the names of the real estate agents and companies in the data set.
 
@@
 
-- **Haziq Jamil**: Conceptualization, Methodology, Software, Formal analysis, Data curation, Writing - Original Draft, Visualization, Supervision, Project administration, Funding acquisition.
-- **Amira Barizah Noorosmawie**: Software, Data curation, Writing - Original Draft.
-- **Hafeezul Waezz Rabu**: Software, Data curation, Writing - Original Draft.
-- **Lutfi Abdul Razak**: Conceptualization, Validation, Supervision, Funding acquisition.
+-   **Haziq Jamil**: Conceptualisation, Methodology, Software, Formal analysis, Data curation, Writing-Original Draft, Visualisation, Supervision, Project administration, Funding acquisition.
+-   **Amira Barizah Noorosmawie**: Software, Data curation, Writing-Original Draft.
+-   **Hafeezul Waezz Rabu**: Software, Data curation, Writing-Original Draft.
+-   **Lutfi Abdul Razak**: Conceptualisation, Validation, Supervision, Funding acquisition.
 
@@
 
-:::{#refs}
+::: {#refs}
 :::

### 2025-01-16 manuscript.qmd
The article title must include the word ‘data’ or ‘dataset’; Also amend abstract

@@
 ---
-title: "From Archives to AI: Residential Property Listings Across Three Decades in Brunei Darussalam"
+title: "From Archives to AI: Residential Property Data Across Three Decades in Brunei Darussalam"
 authors:
@@
 The data set, curated from property advertisements in newspapers and online platforms, includes key attributes such as price, location, property type, and physical characteristics, enriched with area-level spatial information.
-Comprehensive and historical, it complements the Brunei Darussalam Central Bank’s Residential Property Price Index (RPPI), addressing the limitations of restricted access to raw RPPI data and its relatively short timeline since 2015.
-Data collection involved manual transcription from archival sources and automated web scraping using programmatic methods, supported by innovative cleaning with large language models (LLMs) to structure unformatted text.
+Comprehensive and historical, it complements the Brunei Darussalam Central Bank’s Residential Property Price Index (RPPI), addressing the limitations of restricted access to raw RPPI data and its relatively short timeline since its inception in 2015.
+Data collection involved manual transcription from archival sources and automated web scraping using programmatic methods, supported by innovative cleaning with Large Language Models (LLMs) to structure unformatted text.
 The data set enables spatial and temporal analysis, with potential applications in economics, urban planning, and real estate research.
-While minor limitations exist, such as potential missing values and spatial coverage bias toward the Brunei-Muara district, this data set provides a robust foundation for exploring housing market trends and informing policy decisions.
+While minor limitations exist, such as missing values and spatial coverage bias toward the Brunei-Muara district, this data set provides a robust foundation for exploring housing market trends and informing policy decisions.
 keywords:

### 2025-01-16 manuscript.qmd
Cleanup

@@
 From the year 2000 onwards, property advertisements were published daily in the classifieds section. 
-However, reviewing every single daily edition was not practical and would increase the likelihood of recording duplicate listings, thus necessating a sampling strategy. 
+However, reviewing every single daily edition was not practical and would increase the likelihood of recording duplicate listings, thus necessitating a sampling strategy. 
 The sampling was done as follows. Three newspaper editions per week were selected, and the classifieds section was reviewed for property listings. 

### 2025-01-16 analysis.qmd
Formatting tweaks to pdf

--- 2024-12-15 analysis.qmd
@@
 #| tbl-cap: Summary of housing data.
+#| html-table-processing: none
 hsp |>
@@
   add_n() |>
-  modify_header(label ~ "**Variable**")
+  modify_header(label ~ "**Variable**") |>
+  as_gt()
 ```

### 2025-01-16 manuscript.qmd
Formatting tweaks to pdf

@@
 ```{r}
-#| echo: false
+#| include: false
 #| eval: true 
@@
 ```{r}
-#| label: tbl-codebook
-#| tbl-cap: Codebook for the house price data set.
+#| include: false
+codebook_gt <-
   readxl::read_xlsx("data/codebook.xlsx") |>
@@
   gt(rowname_col = "No.") |>
-  fmt_markdown("Variable")
+  fmt_markdown(c("Variable", "Details"))
 ```
+
+::: {#tbl-codebook}
+
+::: {.content-visible unless-format="pdf"}
+```{r}
+#| html-table-processing: none
+codebook_gt
+```
+:::
+
+::: {.content-visible when-format="pdf"}
+```{r}
+codebook_gt |>
+  tab_options(table.font.size = 12) |>
+  cols_width(Details ~ px(400)) |>
+  as_latex()
+```
+:::
+
+Codebook for the house price data set.
+:::
 
@@
 #| code-overflow: wrap
-"The following is the description from a property sale listing in Brunei.
-This description will contain the information about the property, including its characteristics, price, and location.
-However, some of these descriptions may not contain property listings, and instead contain other or no information at all.
+"The following is the description from a property sale listing in Brunei. This 
+description will contain the information about the property, including its 
+characteristics, price, and location. However, some of these descriptions may 
+not contain property listings, and instead contain other or no information at 
+all.
 
-In the case where this description is in fact a property listing, I would like you to extract the following information:
+In the case where this description is in fact a property listing, I would like 
+you to extract the following information:
 
@@
 2. Price of the property in Brunei Dollars, NUMERIC.
-3. Type of property, CHARACTER -- select from Detached, Semi-Detached, Terrace, Apartment, or Land.
-4. Land tenure, CHARACTER -- select from Freehold, Leasehold, or Strata. If other than this, return 'NA'.
-5. Status of the property, CHARACTER -- select from Proposed, Under Construction, New, or Resale.
+3. Type of property, CHARACTER -- select from Detached, Semi-Detached, Terrace, 
+Apartment, or Land.
+4. Land tenure, CHARACTER -- select from Freehold, Leasehold, or Strata. If 
+other than this, return 'NA'.
+5. Status of the property, CHARACTER -- select from Proposed, Under 
+Construction, New, or Resale.
 6. Land area in acres, NUMERIC.
@@
 
-- If the description does not contain a property listing (for example, it is a rental property advertisement), return 'NA' for all 10 values.
+- If the description does not contain a property listing (for example, it is a 
+rental property advertisement), return 'NA' for all 10 values.
 

### 2025-01-16 llm.R
Update LLM

@@ -93,9 +93,10 @@ create_chat("ollama") |>
   extract_chat()
 
 # Test the function
-tictoc::tic()
-y <- clean_desc(x)
-tictoc::toc()
+microbenchmark::microbenchmark(
+  y <- clean_desc(x),
+  times = 10
+)
 
 # Next, might want to map this function to a column of descriptions in a data
 # frame, like so:

### 2025-01-16 manuscript.qmd
For submission

@@
 Each webpage displayed a fixed number of listings (e.g. 128 per page). 
-To scrape all pages, a loop was created to iterate through each page by modifying the URL (such as with an `&offset=<number>` parameter, where `<number>` represented the cumulative number of listings already scraped).
+To scrape all pages, a loop was created to iterate through each page by modifying the URL (such as with an `&offset=<number>` parameter, where `<number>` represents the cumulative number of listings already scraped).
 

### 2025-02-17 missing.qmd
Add missing data pattern qmd

---
title: Missing Data Patterns
author: Haziq Jamil
page-layout: full
grid:
  sidebar-width: 0px
editor_options: 
  chunk_output_type: console
html-table-processing: none
---

## Load data

```{r}
#| echo: true
#| eval: true 
#| file: data.R
```

## Missing data patterns

Let's take a look at the missing data patterns in the housing data.
For simplicity, we focus on the year 2024 and houses in the Brunei-Muara district.

```{r}
hsp24 <- 
  hsp |>
  filter(year(date) == 2024, district == "Brunei Muara") |>
  select(price, mukim, plot_area, floor_area, beds, baths)
glimpse(hsp24)
```

There are a total of `r nrow(hsp24)` houses in the Brunei-Muara district in 2024.
There are a couple of missing values in the data set, `r sum(is.na(hsp24))` to be exact.
We can visualise this using the `{mice}` and `{ggmice}` package.

```{r}
library(mice)
library(ggmice)
```

Let's take a look at the missing data patterns in the housing data.

```{r}
plot_pattern(hsp24, square = !TRUE, rotate = !TRUE) 
```

We first note that in this instance, there are no missing values for price and spatial location.
However, there is a pattern in the missing data, so the missingness mechanism is not *completely* at random. 
It seems to be the case that the missing data is *at random* (MAR), which means that the missing data is dependent on the observed data.
We can test this using a logistic regression.

```{r}
hsp24 |>
  mutate(across(everything(), is.na)) |>
  glm(formula = beds ~ plot_area + floor_area + baths, family = binomial) |>
  summary()
```

What we can see is that the `beds` variable missingness is dependent on the `bath` missingness, which means that if the number of bathrooms is missing, the number of bedrooms is also likely to be missing (odds ratio increases by $e^{8.52} = `r round(exp(8.52), 1)`$).

On the other hand, the missingness of the `floor_area` variable does not seem to be dependent on the other variables, which means that this variable is missing *completely* at random (MCAR).

```{r}
hsp24 |>
  mutate(across(everything(), is.na)) |>
  glm(formula = floor_area ~ plot_area + beds + baths, family = binomial) |>
  summary()
```

Let's visualise the missing points as a scatter plot.

```{r}
ggmice(hsp24, aes(y = price / 1000, x = floor_area)) +
  geom_point() +
  geom_smooth(method = "lm", col = "black") +
  scale_y_continuous(labels = scales::dollar_format()) +
  labs(y = "Price (BND 1,000)", x = "Floor area (sq. ft.)")
```

## Simulating missingness mechanism

Suppose we have a full data set and we want to simulate a missingness mechanism.
For this purpose, we have the following data sets:

1. DATA SET A: The original data set containing missing values.
2. DATA SET B: The "complete cases" data set, i.e. subsetting DATA SET A containing no missing values whatsoever.

Suppose we want to induce missingness in B with the same pattern as A.
Here's the code to do it:

```{r}
set.seed(456)
datA <- hsp24
datB <- drop_na(hsp24)

# Step 1: Calculate the proportion of missing values for each variable in the original data
pat <-
  mice::md.pattern(datA, plot = FALSE) |>
  as.data.frame() |>
  rownames_to_column(var = "freq") |>
  select(-V7) |>
  slice_head(n = -1) |>
  unite("pattern", beds:floor_area, sep = "", remove = FALSE) |>
  mutate(
    freq = as.numeric(freq),
    prop = freq / sum(freq),
    id = row_number()
  ) |> 
  as_tibble()
pat

# Step 2: Randomly sample from this multinomial distribution
mis <- sample(x = pat$pattern, size = nrow(datB), prob = pat$prop, replace = TRUE)
# Check that it matches the original pattern
round(prop.table(table(mis)), 3)
rev(round(pat$prop, 3))

# Step 3: Introduce missing values into the complete dataset based on these proportions
for (i in 1:nrow(datB)) {
  na_flags <- as.integer(strsplit(mis[i], "")[[1]]) == 0L
  datB[, c("beds", "baths", "plot_area", "floor_area")][i, na_flags] <- NA
}
```

Let's visualise the missing data patterns in the simulated data set.

```{r}
plot_pattern(datB, square = !TRUE, rotate = !TRUE) 
```

Some patterns are there, but some are not. This is expected when some of the missing patterns are rare.

### 2025-02-22 manuscript.qmd
Update manuscript

@@
 {{< embed analysis.qmd#fig-corr >}}
+
+## LLM Accuracy Test
+
+To test the accuracy of the LLM data cleaning, we created a test data set of 100 house advertisements in the style of the web scraped data.
+Several popular models from Ollama were used, namely the Llama 3.2 (3B), Mistral (7B), Phi4 (14B), and DeepSeek-R1 distilled reasoning models based on Llama (8B) and Qwen (14B).
+Additionally, two models from OpenAI were included for comparison. 
+These were the GPT-4o and the o1-mini, with the latter being a reasoning model.
+
+The metric used to assess accuracy is a similarity measure within a tolerance of 1% of the true value. 
+For numeric variables, the absolute difference is used.
+For non-numeric variables, the normalised Levenshtein distance is used.
+The code to replicate the analysis is available on the GitHub repository.
+
+The results show that reasoning models outperform the non-reasoning models, with OpenAI's o1-mini model performing the best (98.2% accuracy) followed by the locally run deepseek-r1:14b Ollama model (92.5% accuracy).
+Most inaccuracies are seen in the `status` variable, where the models had a difficult time parsing the correct build status from the advertisement.
+However, key variables such as `price`, `type`, `plot_area`, `floor_area`, `beds`, and `baths` are generally reliable (>90% accuracy).
+
+{{< embed analysis.qmd#fig-llmtest >}}
+
+The run time statistics for each model is shown in the table below.
+Running OpenAI's models are much faster than running models locally, though a paid API key is required.
+
+```{r}
+#| label: tbl-llmtest-time
+#| tbl-cap: Single run time statistics for LLM data cleaning for each model in seconds.
+llmtest_time <-
+  tibble(
+    model = c("llama3.2", "mistral", "phi4", "deepseek-r1:8b", "deepseek-r1:14b", "gpt-4o", "o1-mini"),
+    min = c(4.705968, 2.695677, 7.763636, 49.028515, 97.197804, 1.279267, 5.968378),
+    mean = c(6.136084, 8.385252, 21.278234, 77.494729, 146.424187, 2.457973, 7.945925),
+    median = c(6.278579, 9.302804, 25.710515, 69.055948, 149.651830, 1.733497, 7.506522),
+    max = c(7.830766, 13.328297, 28.309253, 138.477761, 212.098819, 5.379483, 9.943231)
+  )
+
+gt(llmtest_time) |>
+  fmt_number(decimals = 2) |>
+  cols_label(
+    model = "Model",
+    min = "Minimum",
+    mean = "Mean",
+    median = "Median",
+    max = "Maximum"
+  ) |>
+  tab_spanner(
+    label = "Time (seconds)",
+    columns = min:max
+  )
+```
+
+<!-- Unit: seconds -->
+<!--             expr       min         lq       mean     median         uq        max neval cld -->
+<!--         llama3.2  4.705968   5.343346   6.136084   6.278579   6.521761   7.830766     5 a   -->
+<!--          mistral  2.695677   4.423615   8.385252   9.302804  12.175866  13.328297     5 a   -->
+<!--             phi4  7.763636  17.141029  21.278234  25.710515  27.466739  28.309253     5 a   -->
+<!--   deepseek-r1:8b 49.028515  53.375558  77.494729  69.055948  77.535864 138.477761     5  b  -->
+<!--  deepseek-r1:14b 97.197804 119.387742 146.424187 149.651830 153.784741 212.098819     5   c -->
+<!--           gpt-4o  1.279267   1.502509   2.457973   1.733497   2.395108   5.379483     5 a   -->
+<!--          o1-mini  5.968378   6.551901   7.945925   7.506522   9.759592   9.943231     5 a   -->

### 2025-02-22 llm.R
Update manuscript

@@ -3,7 +3,7 @@ library(tidyverse)
 library(tidychatmodels)
 
 # Note: Before starting, ensure to install Ollama (https://ollama.com), and use
-# the terminal to download the model you wish to use. Here, we use llama3.1.
+# the terminal to download the model you wish to use. Here, we use llama3.2.
 
 # Sample description (artificially created)
 x <- "
@@ -77,7 +77,7 @@ Further instructions:
 # Function to clean the descriptions
 clean_desc <- function(caption) {
   create_chat("ollama") |>
-    add_model("llama3.1") |>
+    add_model("llama3.2") |>
     add_message(paste0(the_prompt, caption)) |>
     perform_chat() |>
     extract_chat(silent = TRUE) |>
@@ -87,7 +87,7 @@ clean_desc <- function(caption) {
 
 # Test Ollama works
 create_chat("ollama") |>
-  add_model("llama3.1") |>
+  add_model("llama3.2") |>
   add_message("Hello, how are you?") |>
   perform_chat() |>
   extract_chat()

### 2025-02-22 _submission/Revision 1/_response.qmd
Update figure llm

---
title: 'Review of "Random Item Response Data Generation Using a Limited-
Information Approach: Applications to Assessing Model
Complexity"'
subtitle: 'Response to reviewers'
date: today
format: 
  pdf:
    papersize: a4
    colorlinks: true
    citecolor: blue
    link-citations: true
bibliography: ../../refs-HJ.bib
csl: ../../data-in-brief.csl
---

## Reviewer 1

## Reviewer 2

## References

### 2025-02-22 manuscript.qmd
Update figure

@@
 ---
-title: "From Archives to AI: Residential Property Data Across Three Decades in Brunei Darussalam"
+title: 'From Archives to AI: Residential Property Data Across Three Decades in Brunei Darussalam'
 authors:
@@
     email: haziq.jamil@ubd.edu.bn
-    url: "https://haziqj.ml"
+    url: 'https://haziqj.ml'
     corresponding: true

### 2025-02-22 _submission/Revision 1/_response.qmd
Response to reviewers

@@
 ---
-title: 'Review of "Random Item Response Data Generation Using a Limited-
-Information Approach: Applications to Assessing Model
-Complexity"'
-subtitle: 'Response to reviewers'
+subtitle: 'From Archives to AI: Residential Property Data Across Three Decades in Brunei Darussalam (Data in Brief)'
+title: 'Response to Reviewers'
+authors: 
+  - Haziq Jamil
+  - Amira Barizah Noorosmawie
+  - Hafeezul Waezz Rabu
+  - Lutfi Abdul Razak
 date: today
@@
     link-citations: true
+    output-file: 'response_to_reviwers.pdf'
 bibliography: ../../refs-HJ.bib
@@
 
-## Reviewer 1
+Reviewer #1: The manuscript presents a valuable dataset covering Brunei's residential property market from 1993 to 2024, which is likely to serve as an important resource for researchers in economics, urban planning, and real estate.
+I have some thoughts on improvement that could be implemented to highlight and make clear the limitations and applications of the data created.
 
-## Reviewer 2
+Firstly, the data collection approach combines manual transcription from newspaper archives, web scraping, and LLM-based cleaning.
+While this multifaceted method is innovative, the reliance on manual processes and Excel for spatial harmonisation raises concerns about reproducibility and scalability.
+Wondering if the author has thought about this - not just in terms of introducing human error - but also how it can contribute the longevity of the data source moving forward.
 
-## References
+Second, since the dataset is predominantly derived from newspaper listings and online property advertisements, there is a risk that certain segments of the market—particularly properties not advertised through these channels—may be under-represented.
+Incorporating additional sources, such as government records (for example, land registries or records of land transactions), along with validation from real estate agents, could contribute to a more representative sampling of the residential property market.
+
+Thirdly, the LLM-based cleaning process is a notable innovation in this study.
+However, with an accuracy rate of 93%, there is potential for errors to propagate in the final dataset.
+A more detailed error analysis or cross-validation with alternative cleaning methods would enhance confidence in the dataset.
+In addition, the operational and computational costs associated with employing LLMs should be taken into account, as these may affect the scalability of the approach.
+
+Finally, it is important to note that the dataset relies on listing prices as a proxy for market values.
+Listing prices do not always reflect actual sold prices due to negotiation dynamics and marketing strategies.
+A factual discussion of this limitation is recommended, particularly if market trends or policy implications are to be derived from the analysis.
+
+Handling editor -
+
+- The LLM-based data cleaning introduces subjectivity and potential bias. Some elaboration here is required. 
+- The paper claims significance for policy applications, but the dataset is specific to Brunei, limiting generalizability. some elaboration would be appreciated. 
+- How was data accuracy validated (especially for manually transcribed entries)? What are the error margins for web-scraped data?
+- How consistent is the extraction across different property descriptions?  LLM outputs may suffer from data hallucination—was there a manual verification step?
+- The LLM model and parameters are not fully described (e.g., temperature setting, prompt structure). The dataset is not fully independent of subjective processing.
+- and finally: focus on data curation, not economic analysis!
+
+Scientific Editor -
+
+1. Specifications table/data accessibility: Please make the data citable via zenodo and include a link here.
+
+Reviewer's Responses to Questions
+
+1) Are these data original and produced by the authors?
+
+Please respond with Yes OR No OR N/A.
+
+Reviewer #1: Yes
+
+2) Are these data secondary (e.g. censuses, government databases, organizational records)?
+
+Please respond with Yes OR No OR N/A. If YES, please answer 2a, 2b & 2c; if NO go to 3
+
+Reviewer #1: Yes - though data has been sourced from existing records, such as newspaper advertisements and online property listings, not census or records.
+
+2a) Secondary Data Only: were these data collected using variables that make the study unique?
+
+Please respond with Yes OR No OR N/A.
+
+Reviewer #1: Yes
+
+2b) Secondary Data Only: is this collection of secondary data of value to the research community?
+
+Please respond with Yes OR No OR N/A.
+
+Reviewer #1: Yes
+
+2c) Secondary Data Only: do the authors provide the protocol for collecting/creating these data?
+
+Please respond with Yes OR No OR N/A.
+
+Reviewer #1: Yes
+
+3) Have the authors used a questionnaire or survey?
+
+Please respond with Yes OR No OR N/A. If YES, please answer 3a; if NO go to 4.
+
+Reviewer #1: No
+
+3a) Is the sampling representative of the population and rigorously following a scientific method?
+
+Please comment on the rigor of the sampling method and if additional sampling or a different sampling method is required.
+Please also mention if the questionnaire/survey being used is direct, unambiguous and unbiased.
+
+Reviewer #1: The sampling method primarily relies on collecting property listings from newspaper archives and online platforms, which essentially constitutes a form of convenience sampling.
+
+It is hard to tell if the sampling is biased to agents that actively list their properties, long-standing RE companies, and whether there are missing listings that make an impact to the overall usability and generalisability of the data produced.
+
+If/wherever possible, it would be beneficial to incorporate additional data sources.
+Government records—such as those from land registries or records of land transactions—could provide an official baseline.
+Also, engaging with real estate agents for corroboration could help to identify any systematic biases in the listings and ensure that the data reflects actual market conditions, rather than merely the prices at which properties were initially advertised.
+
+4) Do the authors adequately explain to the research community the utility of these data in the “Value of data” section?
+
+Please include a comment on the validity of this section. Include notes on how this can be improved, if necessary.
+
+Reviewer #1: Yes, though could have more meat on the bones.
+
+5) Are these data described clearly in the “Data description” section?
+
+Please provide suggestions to the author(s) on how to further clarify the presentation and description of the dataset.
+
+Reviewer #1: Yes
+
+6) Is the protocol/method for generating these data adequately described in “Experimental design, materials, and methods” section?
+
+Please include suggestions on how the section can be improved to aid reproducibility/reusability.
+
+Reviewer #1: Authors should consider the following:
+
+Authors describe several methods for data collection, the reliance on manual transcription and Excel-based spatial harmonisation raises concerns regarding reproducibility and scalability.
+Perhaps we need to discuss this.
+
+The integration of historical data is a notable strength, yet differences between manually collected early data and later web-scraped data may introduce inconsistencies.
+The manuscript would benefit from further discussion on how these differences might affect comparability over time.
+
+The use of an LLM-based cleaning method is innovative; however, with a reported accuracy of 93%, some errors may persist.
+A more detailed error analysis or cross-validation with alternative cleaning methods would provide additional assurance regarding the data’s accuracy.
+
+Another important aspect to consider is the reliance on LLMs for data cleaning.
+The cost associated with deploying LLMs—both in terms of computational resources and the expertise required to maintain and update these systems—should not be underestimated.
+The financial and operational costs may impact the scalability of the workflow, particularly if ongoing adjustments are needed to accommodate changes in data sources or to improve model performance.
+
+7) Have the authors provided all the raw data related to all the tables, graphs, images and charts, etc. and are they freely accessible?
+
+Please provide suggestions to the author(s) on how to improve data accessibility for wider usage. Please mention missing raw data, if any.
+
+Reviewer #1: Yes
+
+8) If this data article is related to an existing primary research article is there any duplication? If yes, please comment on this.
+
+Please mention any overlapping text, images, etc.
+
+Reviewer #1: Not known
+
+# Reviewer 1
+
+# Reviewer 2
+
+# References

### 2025-03-03 analysis.qmd
Update manuscript
Update figure
Update new data

@@
     count = n(),
-    spatial = length(unique(mukim)) / nrow(bruneimap::mkm_sf),
+    spatial = length(unique(mukim)) / length(unique(hsp$mukim)),
     # price = sum(missing_price),
@@
     `online-archive` = map_chr(source, ~ ifelse("online-archive" %in% .x, "✔", "")),
-    `web-scrape` = map_chr(source, ~ ifelse("web-scrape" %in% .x, "✔", "")),
+    `web-scrape` = map_chr(source, ~ ifelse("web-scrape" %in% .x | "web-scrape-llm" %in% .x, "✔", "")),
     llm = map_chr(source, ~ ifelse("web-scrape-llm" %in% .x, "✔", ""))
@@
   tab_footnote(
-    footnote = paste0("Total number of mukims in Brunei = ", nrow(bruneimap::mkm_sf), "."),
+    footnote = paste0("Of Brunei’s 39 mukims, only 27 are considered transactable—excluding water villages and remote, non-developable areas."),
     locations = cells_column_labels(columns = spatial)
@@
     data = tibble(
-      quarter = c(2024.3, 2024.3),
+      quarter = c(2024.3 + 0.25, 2024.3 + 0.25),
       series = c("index", "rppi"),
-      value = c(0.941, 0.955),
+      value = c(0.941, 0.955) - 0.02,
       label = c("Median PPSF", "RPPI (BDCB)")
@@
   ) +
-  coord_cartesian(xlim = c(2015, 2025.5))
+  coord_cartesian(xlim = c(2015, 2025.75))
 ```
+
+## LLM Test
+
+```{r}
+#| label: fig-llmtest
+#| fig-cap: Model accuracy comparison using the LLM test data set.
+#| fig-height: 4.5
+#| fig-width: 9
+#| out-width: 100%
+load("experiments/llm_test.RData")
+p_llm_test
+```

### 2025-03-03 manuscript.qmd
Update new data

@@
     affiliations:
-      - ref: ubd              
+      - name: UBD School of Business and Economics
+        id: ubdsbe
+        # department: Mathematical Sciences, Faculty of Science
+        address: Universiti Brunei Darussalam, Jalan Tungku Link
+        city: Bandar Seri Begawan
+        country: Brunei
+        postal-code: BE 1410         
 date-modified: last-modified
 abstract: |
-  This article introduces the first publicly available data set for analyzing the Brunei housing market, covering 31,495 property listings from 1993 to 2024.
+  This article introduces the first publicly available data set for analyzing the Brunei housing market, covering 32,104 property listings from 1993 to early 2025.
 The data set, curated from property advertisements in newspapers and online platforms, includes key attributes such as price, location, property type, and physical characteristics, enriched with area-level spatial information.
@@
 In this subsection, we detail the data cleaning process using a pre-trained large language model (LLM) to extract structured information from the unstructured text. 
-The LLM used was Llama 3.1 with 8B parameters [@grattafiori2024llama], accessed using the `{tidychatmodels}` R package [@rapp2024tidychatmodels] via the Ollama[^1] API, a local interface platform to the LLM.
+The LLM used was the cloud-based OpenAI o1-mini reasoning model[^1], accessed using the `{ellmer}` R package [@wickham2025ellmer] via an API.
+<!-- The LLM used was a DeepSeek R1 distilled Qwen 14B [@deepseek2025deepseekr1;@qwen2025qwen25], accessed using the `{ellmer}` R package [@wickham2025ellmer] via the Ollama[^2] API, a local interface platform to the LLM.
+-->
 
-[^1]: <https://github.com/ollama/ollama>
+[^1]: <https://openai.com/index/openai-o1-mini-advancing-cost-efficient-reasoning/>
+[^2]: <https://github.com/ollama/ollama>
 
@@
 The verbose descriptions were fed into the model one at a time using a loop, with the LLM extracting and returning the relevant details. 
-Note that this loop was not parallelised due to the computational resources required by the LLM. 
+Note that this loop was not parallelised, as the LLM already utilises multiple cores, and further parallelisation would not yield significant efficiency gains due to resource constraints.
 The cleaned results were then parsed and stored in a data frame, which was then subjected to manual data-type validation to ensure conformity with the existing data set. 
-It takes, on average, 2.12 seconds to process a single description running on Apple MacBook Air M2 Silicon on Chip (SoC) and System in Chip (SiP) processors with 16GB RAM. 
-We processed 4,820 descriptions in total from 2020 to 2024 using this method, with a runtime of approximately three hours.
+We processed 5,429 descriptions in total from 2020 to 2025 using this method.
+It takes, on average, 7.51 seconds to process a single description.
 
-To test the accuracy of the LLM, a random sample of 329 descriptions was selected and manually verified for correctness. 
-Of these, 306 were deemed correct (correct entries or identified "non-listings" correctly), resulting in an accuracy rate of 93.0%. 
-Rare errors were spotted due to model hallucinations (despite setting the LLM temperature to the lowest setting), but these are typically minor and unlikely to significantly impact the overall analysis.
-Large errors on the other hand were corrected manually, by filtering for outliers (values exceeding three standard deviations from the mean in magnitude) or inconsistencies in the variables. 
-Overall, the LLM was found to be a valuable tool for extracting structured information from unstructured text, significantly reducing the time and effort required for data cleaning. 
-Users may wish to exclude these records from their analysis if they are concerned about the accuracy of the extracted data.
+To test the accuracy of the LLM data extraction, a test data set of 100 artificially generated descriptions was created, with each description written in the style of a typical property listing.
+The test data also contained missing information in selected property characteristics, which the LLM was expected to handle correctly.
+For each house characteristic, the accuracy of the LLM was calculated by comparing the extracted value to the ground truth.
+For numeric variables, values were considered accurate if they fell within 2% of the corresponding ground truth value. 
+For character variables, accuracy was determined using the normalized Levenshtein distance, ensuring differences remained within a set threshold. 
+Missing values were counted as correct if both the extracted and ground truth values were missing. 
+Accuracy was then averaged both per characteristic and across all characteristics.
+
+Our experiments show that the LLM data extraction process achieved an overall accuracy rate of 98.2%.
+Errors mostly stemmed from incorrect status classification, most likely due to the vagueness of the descriptions.
+In fact, excluding the `status` variable and the `location` variable, which will be processed further, the accuracy rate increases to 99.1%.
+
+In conclusion, we found the LLM to be a valuable tool for extracting structured information from unstructured text, significantly reducing the time and effort required for data cleaning.
+Large errors were still able to be corrected manually, by filtering for outliers (values exceeding three standard deviations from the mean in magnitude) or inconsistencies in the variables, which may be a result of model hallucinations.
+We note that the data cleaning procedure may also be run on local hardware, for example using the Ollama[^2] API, a local interface platform to the LLM.
+See the appendix for further details.
 
@@
 To test the accuracy of the LLM data cleaning, we created a test data set of 100 house advertisements in the style of the web scraped data.
-Several popular models from Ollama were used, namely the Llama 3.2 (3B), Mistral (7B), Phi4 (14B), and DeepSeek-R1 distilled reasoning models based on Llama (8B) and Qwen (14B).
+Several popular models from Ollama were used, namely the Llama3.2 (3B), Mistral (7B), Phi 4 (14B), and DeepSeek-R1 distilled reasoning models based on Llama (8B) and Qwen (14B).
 Additionally, two models from OpenAI were included for comparison. 
@@
 
-The metric used to assess accuracy is a similarity measure within a tolerance of 1% of the true value. 
-For numeric variables, the absolute difference is used.
-For non-numeric variables, the normalised Levenshtein distance is used.
-The code to replicate the analysis is available on the GitHub repository.
+<!-- The metric used to assess accuracy is a similarity measure within a tolerance of 1% of the true value.  -->
+<!-- For numeric variables, the absolute difference is used. -->
+<!-- For non-numeric variables, the normalised Levenshtein distance is used. -->
+<!-- The code to replicate the analysis is available on the GitHub repository. -->
 
 The results show that reasoning models outperform the non-reasoning models, with OpenAI's o1-mini model performing the best (98.2% accuracy) followed by the locally run deepseek-r1:14b Ollama model (92.5% accuracy).
-Most inaccuracies are seen in the `status` variable, where the models had a difficult time parsing the correct build status from the advertisement.
+Most inaccuracies are seen in the `status` variable, where the models had a difficult time parsing the correct build status from the vague verbose advertisement.
 However, key variables such as `price`, `type`, `plot_area`, `floor_area`, `beds`, and `baths` are generally reliable (>90% accuracy).
@@
 The run time statistics for each model is shown in the table below.
+The computer used Apple MacBook Air M2 Silicon on Chip (SoC) and System in Chip (SiP) processors with 16GB RAM.
 Running OpenAI's models are much faster than running models locally, though a paid API key is required.
+Faster local running times are, of course, a function of compute power.
 

### 2025-03-03 missing.qmd
Update missing.qmd
Update new data

@@
   hsp |>
-  filter(year(date) == 2024, district == "Brunei Muara") |>
+  filter(year(date) == 2024, district == "Brunei-Muara") |>
   select(price, mukim, plot_area, floor_area, beds, baths)
@@
 ```{r}
-set.seed(456)
+set.seed(123)
 datA <- hsp24

### 2025-03-03 data.R

@@ -7,7 +7,7 @@ library(GGally)
 
 # Main data set
 hsp <- 
-  read_csv("data/hspbn_2024-12-12.csv") |>
+  read_csv("data/hspbn_2025-03-03.csv") |>
   mutate(
     type = factor(type, levels = c("Detached", "Semi-Detached", "Terrace",
                                    "Apartment", "Land")),

### 2025-03-03 manuscript.qmd
Update LLM results

@@
 In this subsection, we detail the data cleaning process using a pre-trained large language model (LLM) to extract structured information from the unstructured text. 
-The LLM used was the cloud-based OpenAI o1-mini reasoning model[^1], accessed using the `{ellmer}` R package [@wickham2025ellmer] via an API.
-<!-- The LLM used was a DeepSeek R1 distilled Qwen 14B [@deepseek2025deepseekr1;@qwen2025qwen25], accessed using the `{ellmer}` R package [@wickham2025ellmer] via the Ollama[^2] API, a local interface platform to the LLM.
--->
+<!-- The LLM used was the cloud-based OpenAI o1-mini reasoning model[^1], accessed using the `{ellmer}` R package [@wickham2025ellmer] via an API. -->
+The LLM used was a DeepSeek R1 distilled Qwen 14B [@deepseek2025deepseekr1;@qwen2025qwen25], accessed using the `{ellmer}` R package [@wickham2025ellmer] via the Ollama[^2] API, a local interface platform to the LLM.
 
-[^1]: <https://openai.com/index/openai-o1-mini-advancing-cost-efficient-reasoning/>
+<!-- [^1]: <https://openai.com/index/openai-o1-mini-advancing-cost-efficient-reasoning/> -->
 [^2]: <https://github.com/ollama/ollama>
@@
 The cleaned results were then parsed and stored in a data frame, which was then subjected to manual data-type validation to ensure conformity with the existing data set. 
-We processed 5,429 descriptions in total from 2020 to 2025 using this method.
-It takes, on average, 7.51 seconds to process a single description.
+We processed 5,429 descriptions in total from 2020 to 2025 using this method, with a run time of approximately 20 hours spread over 3 machines.
+It takes, on average, 150 seconds to process a single description.
 
@@
 Accuracy was then averaged both per characteristic and across all characteristics.
+For further details, please consult the appendix.
 
-Our experiments show that the LLM data extraction process achieved an overall accuracy rate of 98.2%.
+Our experiments show that the LLM data extraction process with the deepseek-r1:14b model achieved an overall accuracy rate of 96.9%.
 Errors mostly stemmed from incorrect status classification, most likely due to the vagueness of the descriptions.
-In fact, excluding the `status` variable and the `location` variable, which will be processed further, the accuracy rate increases to 99.1%.
-
-In conclusion, we found the LLM to be a valuable tool for extracting structured information from unstructured text, significantly reducing the time and effort required for data cleaning.
-Large errors were still able to be corrected manually, by filtering for outliers (values exceeding three standard deviations from the mean in magnitude) or inconsistencies in the variables, which may be a result of model hallucinations.
-We note that the data cleaning procedure may also be run on local hardware, for example using the Ollama[^2] API, a local interface platform to the LLM.
-See the appendix for further details.
+<!-- In fact, excluding the `status` variable and the `location` variable, which will be processed further, the accuracy rate increases to 97.3%. -->
+As for the rest of the variables, obvious errors were able to be corrected manually, by filtering for outliers (values exceeding three standard deviations from the mean in magnitude) or inconsistencies in the variables, which may be a result of model hallucinations.
+Overall, the LLM was found to be a valuable tool for extracting structured information from unstructured text, significantly reducing the time and effort required for data cleaning. 
+<!-- Users may wish to exclude these records from their analysis if they are concerned about the accuracy of the extracted data. -->
 
@@
 The spatial data coverage is also heavily skewed towards the Brunei-Muara district, which accounts for `{r} scales::percent(prop.table(table(hsp$district))[2], accuracy = 0.1)` of the listings. 
-This is a reflection of the district’s higher population and greater volume of property transactions [@jamil2024spatiotemporal], which may bias analyses toward this region. 
+This is a reflection of the district’s higher population and greater volume of property transactions [@jamil2025spatiotemporal], which may bias analyses toward this region. 
 Furthermore, while we have confidence in the data quality from 2015 to 2024, property price trends between 1993 and 2014 cannot be fully verified.

### 2025-03-03 manuscript.qmd
Update LLM section again

@@
 The cleaned results were then parsed and stored in a data frame, which was then subjected to manual data-type validation to ensure conformity with the existing data set. 
-We processed 5,429 descriptions in total from 2020 to 2025 using this method, with a run time of approximately 20 hours spread over 3 machines.
-It takes, on average, 150 seconds to process a single description.
+It takes, on average, 41.1 seconds to process a single description using a Mac Pro 3.2GHz 16 core Intel Xeon W.
+We processed 5,429 descriptions in total from 2020 to 2025 using this method, with a run time of approximately 20 hours in total (spread over 3 machines).
 
-To test the accuracy of the LLM data extraction, a test data set of 100 artificially generated descriptions was created, with each description written in the style of a typical property listing.
-The test data also contained missing information in selected property characteristics, which the LLM was expected to handle correctly.
+To evaluate the accuracy of the LLM data extraction, a test data set of 100 artificially generated descriptions was created, with each description written in the style of a typical property listing.
 For each house characteristic, the accuracy of the LLM was calculated by comparing the extracted value to the ground truth.
@@
 For character variables, accuracy was determined using the normalized Levenshtein distance, ensuring differences remained within a set threshold. 
-Missing values were counted as correct if both the extracted and ground truth values were missing. 
-Accuracy was then averaged both per characteristic and across all characteristics.
-For further details, please consult the appendix.
+The test data also contained missing information in certain property characteristics, which the LLM was expected to handle correctly.
+A correct handling was counted if both the extracted and ground truth values were missing. 
+Accuracy was then averaged per characteristic as well as across all characteristics.
 
-Our experiments show that the LLM data extraction process with the deepseek-r1:14b model achieved an overall accuracy rate of 96.9%.
+Our experiments show that the LLM data extraction process with the deepseek-r1:14b model achieved an overall accuracy rate of 96.9% (see the appendix for complete results).
 Errors mostly stemmed from incorrect status classification, most likely due to the vagueness of the descriptions.
-<!-- In fact, excluding the `status` variable and the `location` variable, which will be processed further, the accuracy rate increases to 97.3%. -->
 As for the rest of the variables, obvious errors were able to be corrected manually, by filtering for outliers (values exceeding three standard deviations from the mean in magnitude) or inconsistencies in the variables, which may be a result of model hallucinations.
@@
     model = c("llama3.2", "mistral", "phi4", "deepseek-r1:8b", "deepseek-r1:14b", "gpt-4o", "o1-mini"),
-    min = c(4.705968, 2.695677, 7.763636, 49.028515, 97.197804, 1.279267, 5.968378),
-    mean = c(6.136084, 8.385252, 21.278234, 77.494729, 146.424187, 2.457973, 7.945925),
-    median = c(6.278579, 9.302804, 25.710515, 69.055948, 149.651830, 1.733497, 7.506522),
-    max = c(7.830766, 13.328297, 28.309253, 138.477761, 212.098819, 5.379483, 9.943231)
+    min = c(4.705968, 2.695677, 7.763636, 49.028515, 70.27092, 1.279267, 5.968378),
+    mean = c(6.136084, 8.385252, 21.278234, 77.494729, 122.0068, 2.457973, 7.945925),
+    median = c(6.278579, 9.302804, 25.710515, 69.055948, 81.71249, 1.733497, 7.506522),
+    max = c(7.830766, 13.328297, 28.309253, 138.477761, 283.8539, 5.379483, 9.943231)
   )

### 2025-03-04 manuscript.qmd
Update LLM timing and accuracy

@@
 The cleaned results were then parsed and stored in a data frame, which was then subjected to manual data-type validation to ensure conformity with the existing data set. 
-It takes, on average, 41.1 seconds to process a single description using a Mac Pro 3.2GHz 16 core Intel Xeon W.
+It takes, on average, 81.7 seconds to process a single description using a Mac Pro 3.2GHz 16 core Intel Xeon W.
 We processed 5,429 descriptions in total from 2020 to 2025 using this method, with a run time of approximately 20 hours in total (spread over 3 machines).
@@
 
-The results show that reasoning models outperform the non-reasoning models, with OpenAI's o1-mini model performing the best (98.2% accuracy) followed by the locally run deepseek-r1:14b Ollama model (92.5% accuracy).
+The results show that reasoning models outperform the non-reasoning models, with OpenAI's o1-mini model performing the best (99.2% accuracy) followed by the locally run deepseek-r1:14b Ollama model (96.9% accuracy).
 Most inaccuracies are seen in the `status` variable, where the models had a difficult time parsing the correct build status from the vague verbose advertisement.
@@
     model = c("llama3.2", "mistral", "phi4", "deepseek-r1:8b", "deepseek-r1:14b", "gpt-4o", "o1-mini"),
-    min = c(4.705968, 2.695677, 7.763636, 49.028515, 70.27092, 1.279267, 5.968378),
-    mean = c(6.136084, 8.385252, 21.278234, 77.494729, 122.0068, 2.457973, 7.945925),
-    median = c(6.278579, 9.302804, 25.710515, 69.055948, 81.71249, 1.733497, 7.506522),
-    max = c(7.830766, 13.328297, 28.309253, 138.477761, 283.8539, 5.379483, 9.943231)
+    min = c(1.077457, 2.661627, 3.722881, 36.829881, 40.8939, 1.279267, 5.968378),
+    mean = c(6.396146, 10.437078, 14.108101, 65.973720, 117.666112, 2.457973, 7.945925),
+    median = c(9.595035, 2.907932, 4.267815, 54.605889, 81.71249, 1.733497, 7.506522),
+    max = c(10.16348, 22.21225, 38.01499, 112.77667, 151.2027, 5.379483, 9.943231)
   )
@@
 <!-- Unit: seconds -->
-<!--             expr       min         lq       mean     median         uq        max neval cld -->
-<!--         llama3.2  4.705968   5.343346   6.136084   6.278579   6.521761   7.830766     5 a   -->
-<!--          mistral  2.695677   4.423615   8.385252   9.302804  12.175866  13.328297     5 a   -->
-<!--             phi4  7.763636  17.141029  21.278234  25.710515  27.466739  28.309253     5 a   -->
-<!--   deepseek-r1:8b 49.028515  53.375558  77.494729  69.055948  77.535864 138.477761     5  b  -->
-<!--  deepseek-r1:14b 97.197804 119.387742 146.424187 149.651830 153.784741 212.098819     5   c -->
+ <!--            expr       min         lq       mean     median         uq       max neval -->
+ <!--        llama3.2  1.077457   1.168078   6.396146   9.595035   9.881765  10.16348    10 -->
+ <!--         mistral  2.661627   2.854717  10.437078   2.907932  21.778689  22.21225    10 -->
+ <!--            phi4  3.722881   3.925309  14.108101   4.267815  36.986746  38.01499    10 -->
+ <!--  deepseek-r1:8b 36.829881  46.254848  65.973720  54.605889  85.101693 112.77667    10 -->
+ <!-- deepseek-r1:14b 59.400884   74.62474 117.666112  81.71249   99.57201  283.8539  10 -->
+ <!-- deepseek-r1:14b 40.8939 67.19222 127.0108 93.09138 151.2027 541.1301   100 -->
 <!--           gpt-4o  1.279267   1.502509   2.457973   1.733497   2.395108   5.379483     5 a   -->

### 2025-03-05 manuscript.qmd
Update manuscript for revision

@@
 
+```{r}
+#| include: false
+years <- lubridate::year(hsp$date)
+max(years) - min(years) + 1
+```
+
 <!-- > Data articles describe research data that the authors have made publicly available through a repository.
@@
 - **First of its kind for Brunei**.
+This data set is the first publicly available compilation of Brunei’s residential property data, covering `{r} scales::comma(nrow(hsp))` listings from `r min(years)` to early `r max(years)`.
+Previous studies on Brunei's housing have been limited to recent or non-spatial data [@ng2022characterising;@jamil2025leveraging], or qualitative in nature due to the lack of structured data [@hassan2011cultural;@hassan2023sociocultural].
+Researchers may use this data to explore temporal variations in property listings and to compare housing characteristics across different regions within Brunei.
+
+<!-- - **First of its kind for Brunei**.
 This data set enables comprehensive spatial and temporal analysis of the Brunei housing market.
@@
 This aligns with the growing trend of using data analytics in the real estate industry [@braesemann2020proptech; @delisle2020big].
+-->
 
 - **Historical and spatial insights**.
-Covering data from 1993 to 2024, this data set allows for the study of long-term housing trends in Brunei.
-The spatial information available enables analysis at various administrative levels, providing insights into local patterns and urban development over time.
+Spanning over three decades, this data set allows for the study of long-term housing trends in Brunei.
+The spatial information available enables analysis at various administrative levels, providing insights into urban development patterns, regional differences, and the evolution of housing characteristics over time.
 This historical depth is particularly valuable given the lack of previous data before the establishment of the Residential Property Price Index (RPPI) [@bdcb2021technical] in 2015.
 
-- **Influence on economic and monetary policies**.
+- **Methodological innovation in data curation**.
+The data collection process employs a unique combination of manual transcription from archival sources, automated web scraping, and AI-based data cleaning using Large Language Models (LLMs).
+This open source and multi-method approach enhances reproducibility and transparency in data curation.
+The present work provides a reproducible framework for assembling complex datasets, which can be adapted for similar data collection efforts in other other domains, thereby advancing best practices in the field.
+
+<!-- - **Influence on economic and monetary policies**.
 Analysing the real estate market is crucial because the RPPI can potentially play a key role in shaping monetary policy and assessing economic stability.
@@
 This data set demonstrates how computational methods can automate what is typically a time-consuming and labour-intensive process.
+-->
 
 - **Opportunities for handling of missing data**.
-While the data set has complete information for key variables such as price, date, and spatial variables, missing information on house characteristics creates opportunities for further research.
-Evidently, house characteristics are inherently correlated (see [@fig-corr]), so imputation from observed correlations seems highly promising.
-With the spatial information present, this opens avenues for developing methodological approaches for handling missing data, encouraging innovation and exploration in this area.
+The dataset includes instances of missing or inconsistent data, particularly in house characteristics, which present opportunities for further research on data imputation techniques.
+Researchers may explore advanced statistical and machine learning methods to address missing values and improve data reliability.
+The structured format and detailed documentation of the dataset support such methodological investigations, making it a valuable testbed for developing and evaluating new approaches to handling incomplete data in real-world datasets.
 
-- **Application of Large Language Models (LLMs)**.
+<!-- - **Application of Large Language Models (LLMs)**.
 This project highlights an innovative use of Large Language Models (LLMs) for data cleaning.
-The LLM was employed to extract structured information from unstructured text descriptions, achieving an accuracy rate of 93%.
+The LLM was employed to extract structured information from unstructured text descriptions with great accuracy.
 This method significantly reduced the time and effort required for data cleaning.
 It can also be applied to other data sets with unstructured text, such as social media or document archives, to extract valuable information for analysis.
+-->
 
@@
 <!-- Please use visual aids (such as tables, graphs, or figures with captions) to familiarize the reader with your data set, but do not offer background, interpretations, or conclusions. -->
-
-```{r}
-#| include: false
-years <- lubridate::year(hsp$date)
-max(years) - min(years) + 1
-```
 
@@
 
-## Comparison to RPPI Data
-
-To demonstrate the quality of the data set, we compared it with the Residential Property Price Index (RPPI) [@bdcb2021technical] published by the Brunei Darussalam Central Bank (BDCB). 
-A simple median price per square foot (PPSF) index can be calculated by aggregating the data by quarters. 
-<!-- @fig-rppi shows the median smoothed PPSF by property type using a 24-month (8-quarter) rolling window. --> 
-<!-- Generally the property price trends reflect macroeconomic conditions. --> 
-This approach minimises the impact of missing values, as the index is based on aggregated data. 
-@fig-rppi shows the comparison between the RPPI and the PPSF index calculated from our data set. 
-The mean absolute error (MAE) between the two indices is calculated to be `{r} scales::percent(rppi_mae[1], accuracy = 0.01)`, indicating a good level of agreement between the two data sets.
-
-{{< embed analysis.qmd#fig-rppi >}}
-
 # Experimental Design, Materials and Methods
@@
 Early years data collection was conducted manually, involving the transcription of property listing details from advertisements into a digital tabular format. 
-This process was carried out by two of the authors over a period of nine months, from October 2023 to July 2024. 
+This process was carried out by two of the authors over a period of nine months, from October 2023 to July 2024, working at a manageable pace.
+A total of `{r} scales::comma(sum(hsp$method %in% c("nat-archive", "online-archive")))` data points were collected in this manner, which translates to processing approximately 150 entries per week per person.
+Spreading the task over such an extended period ensured that transcribers were never under undue time pressure, which could have led to errors due to fatigue.
+
 The primary sources of the property listings were local newspapers and magazines. 
@@
 
-## LLM Data Cleaning
+## LLM Data Extraction
 
@@
 It takes, on average, 81.7 seconds to process a single description using a Mac Pro 3.2GHz 16 core Intel Xeon W.
-We processed 5,429 descriptions in total from 2020 to 2025 using this method, with a run time of approximately 20 hours in total (spread over 3 machines).
+We processed `{r} scales::comma(sum(hsp$method %in% c("web-scrape-llm")))` descriptions from 2020 to 2025 using this method, with a run time of approximately 20 hours in total (spread over three machines).
 
@@
 For each house characteristic, the accuracy of the LLM was calculated by comparing the extracted value to the ground truth.
-For numeric variables, values were considered accurate if they fell within 2% of the corresponding ground truth value. 
-For character variables, accuracy was determined using the normalized Levenshtein distance, ensuring differences remained within a set threshold. 
+For numeric variables, values were considered accurate if they fell within 1% of the corresponding ground truth value. 
+For character variables, accuracy was determined using the normalised Levenshtein distance, ensuring differences remained within a set threshold. 
 The test data also contained missing information in certain property characteristics, which the LLM was expected to handle correctly.
@@
 
-Our experiments show that the LLM data extraction process with the deepseek-r1:14b model achieved an overall accuracy rate of 96.9% (see the appendix for complete results).
-Errors mostly stemmed from incorrect status classification, most likely due to the vagueness of the descriptions.
-As for the rest of the variables, obvious errors were able to be corrected manually, by filtering for outliers (values exceeding three standard deviations from the mean in magnitude) or inconsistencies in the variables, which may be a result of model hallucinations.
-Overall, the LLM was found to be a valuable tool for extracting structured information from unstructured text, significantly reducing the time and effort required for data cleaning. 
+Our experiments show that the LLM data extraction process with the deepseek-r1:14b model achieved an overall accuracy rate of 96.9% (see [Appendix](#sec-apx-llm) for complete results).
+Errors mostly stemmed from incorrect `status` classification, most likely due to the vagueness of the advertisement listing.
+As for the rest of the variables, obvious errors were flagged and corrected manually during our data validation process (described in the subsection following the next one).
+Overall, the LLM was found to be a valuable tool for extracting structured information from unstructured text, significantly reducing the time and effort required for data extraction. 
 <!-- Users may wish to exclude these records from their analysis if they are concerned about the accuracy of the extracted data. -->
@@
 
+## Data Validation
+
+To ensure data quality, a series of consistency and validity checks were performed on the data set, especially after manual transcription and LLM data cleaning.
+These checks include
+
+1.
+**Outlier detection.** Summary statistics analyses to identify and flag anomalous values.
+For instance, a built-up area recorded as 0.1 square feet or beds and baths exceeding 20 is suspect, and highly likely points towards human error or model hallucinations.
+Such anomalies were flagged and manually reviewed for correction.
+
+2.
+**Internal consistency checks.** This made use of substantive knowledge about Brunei's housing market [@jamil2025spatiotemporal].
+An example is using the price per square foot indicator, whose value typically falls within a known range.
+Therefore any deviations were scrutinised to ensure that variables such as price and floor area were correctly recorded.
+This was similarly applied to other variables such as plot area, beds, and baths.
+
+3.	**Duplicate records detection.** We also performed duplicate record detection to identify any repeated entries that might have arisen from overlapping data sources or transcription errors.
+Any duplicates that were identified were carefully reviewed and removed to ensure that each property listing was uniquely represented in the span of one calendar month.
+
+These data validation procedures collectively contribute to a robust and reliable dataset, providing a solid foundation for subsequent analysis.
+
 # Limitations
@@
 
-Despite efforts to ensure data quality, some limitations remain.
-Duplicate listings were carefully reviewed and removed, though there remains a slight possibility that duplicated records still exist in the data set.
-The spatial data coverage is also heavily skewed towards the Brunei-Muara district, which accounts for `{r} scales::percent(prop.table(table(hsp$district))[2], accuracy = 0.1)` of the listings. 
-This is a reflection of the district’s higher population and greater volume of property transactions [@jamil2025spatiotemporal], which may bias analyses toward this region. 
-Furthermore, while we have confidence in the data quality from 2015 to 2024, property price trends between 1993 and 2014 cannot be fully verified.
+Listing prices in our data set serve as a proxy for market values, capturing advertised trends rather than final sale outcomes. 
+This enables timely analysis of market sentiment, even though factors such as negotiation dynamics, seller strategies, and market conditions may cause deviations from actual transaction prices.
+
+Despite significant efforts to ensure data quality, some limitations remain. 
+First, integrating historical data from manually transcribed sources with later web-scraped data may introduce inconsistencies affecting comparability over time. 
+Second, although duplicate listings were carefully reviewed and removed, there remains a slight possibility of residual duplicates in the data set.
+<!-- Thirdly, the spatial distribution is heavily skewed toward the Brunei-Muara district--reflecting its higher population and transaction volume [@jamil2025spatiotemporal]--which may bias regional analyses.
+-->
+Thirdly, while we have confidence in the data quality from 2015 to 2024, property price trends between 1993 and 2014 cannot be fully verified. 
 Nonetheless, this study serves as a valuable starting point.
 Future research could benefit greatly from access to administrative transaction data, which would allow for more comprehensive and accurate analyses.
-
-Missing data in house characteristics is another limitation, although this should be seen as an opportunity for further research to develop imputation methods or alternative analytical approaches. 
-Minor inaccuracies were also observed in the LLM-based data cleaning process, but these issues are infrequent and can be mitigated by subsetting or refining the affected entries.
 
@@
 The authors gratefully acknowledge the contributions of Atikah Farhain Yahya, Nurulhanisah Abdul Manan, and Nina Zuhairi towards the collection and processing of the data contained within.
+We also thank the Brunei Darussalam Central Bank (BDCB) for the engaging discussions and support, which were instrumental in the inception of this project.
 
@@
 
-## LLM Accuracy Test
+## Comparison to RPPI Data
 
-To test the accuracy of the LLM data cleaning, we created a test data set of 100 house advertisements in the style of the web scraped data.
+To demonstrate the quality of the data set, we compared it with the Residential Property Price Index (RPPI) [@bdcb2021technical] published by the Brunei Darussalam Central Bank (BDCB). 
+A simple median price per square foot (PPSF) index can be calculated by aggregating the data by quarters. 
+This approach minimises the impact of missing values, as the index is based on aggregated data. 
+@fig-rppi shows the comparison between the RPPI and the PPSF index calculated from our data set. 
+The mean absolute error (MAE) between the two indices is calculated to be `{r} scales::percent(rppi_mae[1], accuracy = 0.01)`, indicating a good level of agreement between the two data sets.
+
+{{< embed analysis.qmd#fig-rppi >}}
+
+## LLM Accuracy Test {#sec-apx-llm}
+
+To test the accuracy of the LLM data extraction, we created a test data set of 100 house advertisements in the style of the web scraped data.
 Several popular models from Ollama were used, namely the Llama3.2 (3B), Mistral (7B), Phi 4 (14B), and DeepSeek-R1 distilled reasoning models based on Llama (8B) and Qwen (14B).
@@
 These were the GPT-4o and the o1-mini, with the latter being a reasoning model.
-
-<!-- The metric used to assess accuracy is a similarity measure within a tolerance of 1% of the true value.  -->
-<!-- For numeric variables, the absolute difference is used. -->
-<!-- For non-numeric variables, the normalised Levenshtein distance is used. -->
-<!-- The code to replicate the analysis is available on the GitHub repository. -->
 
@@
 #| label: tbl-llmtest-time
-#| tbl-cap: Single run time statistics for LLM data cleaning for each model in seconds.
+#| tbl-cap: Single run time statistics for LLM data extraction for each model in seconds.
 llmtest_time <-

### 2025-03-05 manuscript.qmd
Update folder structure of manuscript

@@
 abstract: |
-  This article introduces the first publicly available data set for analyzing the Brunei housing market, covering 32,104 property listings from 1993 to early 2025.
+  This article introduces the first publicly available data set for analyzing the Brunei housing market, covering 31,150 property listings from 1993 to early 2025.
 The data set, curated from property advertisements in newspapers and online platforms, includes key attributes such as price, location, property type, and physical characteristics, enriched with area-level spatial information.
@@
 #| eval: true 
-#| file: data.R
+#| file: notebooks/data.R
 ```
@@
 ::: column-page
-{{< embed analysis.qmd#tbl-summary >}}
+{{< embed notebooks/analysis.qmd#tbl-summary >}}
 :::
@@
 ::: landscape
-{{< embed analysis.qmd#tbl-summary >}}
+{{< embed notebooks/analysis.qmd#tbl-summary >}}
 :::
@@
 
-{{< embed analysis.qmd#fig-spatial >}}
+{{< embed notebooks/analysis.qmd#fig-spatial >}}
 
@@
 
-{{< embed analysis.qmd#fig-price-evolution >}}
+{{< embed notebooks/analysis.qmd#fig-price-evolution >}}
 
@@
 
-{{< embed analysis.qmd#tbl-avail >}}
+{{< embed notebooks/analysis.qmd#tbl-avail >}}
 
@@
 
-{{< embed analysis.qmd#fig-corr >}}
+{{< embed notebooks/analysis.qmd#fig-corr >}}
 
@@
 
-{{< embed analysis.qmd#fig-rppi >}}
+{{< embed notebooks/analysis.qmd#fig-rppi >}}
 
@@
 
-{{< embed analysis.qmd#fig-llmtest >}}
+{{< embed notebooks/analysis.qmd#fig-llmtest >}}
 

### 2025-03-05 notebooks/analysis.qmd
Update folder structure of manuscript

--- 2025-03-03 analysis.qmd
@@
     name = NULL, 
-    breaks = seq(2015, 2024.5, by = 0.25)
+    breaks = seq(2015, 2024.75, by = 0.25)
   ) +
@@
 #| label: fig-llmtest
-#| fig-cap: Model accuracy comparison using the LLM test data set.
+#| fig-cap: Comparison of data extraction accuracy across multiple LLM models on the test dataset. Each bar represents the percentage of correctly extracted fields for a given model.
 #| fig-height: 4.5
@@
 #| out-width: 100%
-load("experiments/llm_test.RData")
+load(here::here("experiments/llm_test.RData"))
 p_llm_test

### 2025-03-05 notebooks/data.R

@@ -4,10 +4,11 @@ library(gt)
 library(gtsummary)
 library(lubridate)
 library(GGally)
+here::i_am("notebooks/data.R")
 
 # Main data set
 hsp <- 
-  read_csv("data/hspbn_2025-03-03.csv") |>
+  read_csv(here::here("data/hspbn_2025-03-03.csv")) |>
   mutate(
     type = factor(type, levels = c("Detached", "Semi-Detached", "Terrace",
                                    "Apartment", "Land")),
@@ -19,7 +20,7 @@ hsp <-
 
 # RPPI from BDCB
 rppi <- 
-  read_csv("data/rppi.csv") |>
+  read_csv(here::here("data/rppi.csv")) |>
   mutate(
     quarter = zoo::as.yearqtr(quarter),
     rppi = rppi / 100

### 2025-03-05 manuscript.qmd
Update manuscript

@@
 abstract: |
-  This article introduces the first publicly available data set for analyzing the Brunei housing market, covering 31,150 property listings from 1993 to early 2025.
+  This article introduces the first publicly available data set for analyzing the Brunei housing market, covering more than 30,000 property listings from 1993 to early 2025.
 The data set, curated from property advertisements in newspapers and online platforms, includes key attributes such as price, location, property type, and physical characteristics, enriched with area-level spatial information.
@@
 The data set enables spatial and temporal analysis, with potential applications in economics, urban planning, and real estate research.
-While minor limitations exist, such as missing values and spatial coverage bias toward the Brunei-Muara district, this data set provides a robust foundation for exploring housing market trends and informing policy decisions.
+Although listing prices serve only as a proxy for market values and may deviate from actual sale prices due to negotiation dynamics and other factors, this data set still provides a valuable resource for reproducible analysis of housing market trends and for informing policy decisions.
 keywords:
@@
 This open source and multi-method approach enhances reproducibility and transparency in data curation.
-The present work provides a reproducible framework for assembling complex datasets, which can be adapted for similar data collection efforts in other other domains, thereby advancing best practices in the field.
+The present work provides a reproducible framework for assembling complex data sets, which can be adapted for similar data collection efforts in other other domains, thereby advancing best practices in the field.
 
@@
 - **Opportunities for handling of missing data**.
-The dataset includes instances of missing or inconsistent data, particularly in house characteristics, which present opportunities for further research on data imputation techniques.
+The data set includes instances of missing or inconsistent data, particularly in house characteristics, which present opportunities for further research on data imputation techniques.
 Researchers may explore advanced statistical and machine learning methods to address missing values and improve data reliability.
-The structured format and detailed documentation of the dataset support such methodological investigations, making it a valuable testbed for developing and evaluating new approaches to handling incomplete data in real-world datasets.
+The structured format and detailed documentation of the data set support such methodological investigations, making it a valuable testbed for developing and evaluating new approaches to handling incomplete data in real-world data sets.
 
@@
 
+```{r}
+#| include: false
+tbl_summary <- 
+  hsp |>
+  mutate(
+    price = price / 1000,
+    storeys = factor(
+      ifelse(storeys >= 3, "3+", as.character(storeys)),
+      levels = c("1", "2", "3+")
+    ),
+    district = gsub("Brunei Muara", "Brunei-Muara", district),
+    district = factor(district, levels = c("Brunei-Muara", "Belait", "Tutong", "Temburong"))
+  ) |>
+  tbl_summary(
+    include = c(price:baths),
+    by = district,
+    missing = "no", 
+    type = all_continuous() ~ "continuous2",
+    statistic = list(
+      all_continuous2() ~ c("{mean} ({sd})", Range = "{min} - {max}", "{median} ({p25}, {p75})")
+    ),
+    label = list(
+      price = "Price (BND 1,000)",
+      type = "Property type",
+      plot_area = "Plot area (acres)",
+      floor_area = "Floor area (sq. ft.)",
+      storeys = "Number of storeys",
+      status = "Development status",
+      tenure = "Land tenure",    
+      beds = "Number of bedrooms",
+      baths = "Number of bathrooms"
+    ),
+    digits = list(
+      baths = 1,
+      beds = 1
+    )
+  ) |>
+  add_overall() |>
+  add_n() |>
+  modify_header(label ~ "**Variable**") |>
+  as_gt()
+```
+
 :::: {.content-visible when-format="html"}
 ::: column-page
-{{< embed notebooks/analysis.qmd#tbl-summary >}}
+::: {#tbl-summary}
+```{r}
+#| html-table-processing: none
+tbl_summary
+```
+Summary of housing data.
+:::
 :::
@@
 ::: landscape
-{{< embed notebooks/analysis.qmd#tbl-summary >}}
+::: {#tbl-summary}
+```{r}
+#| html-table-processing: none
+tbl_summary |>
+  tab_options(table.font.size = "9px")
+```
+Summary of housing data.
+:::
 :::
@@
 
-These data validation procedures collectively contribute to a robust and reliable dataset, providing a solid foundation for subsequent analysis.
+These data validation procedures collectively contribute to a robust and reliable data set, providing a solid foundation for subsequent analysis.
 

### 2025-03-05 manuscript.qmd
Final tweaks manuscript

@@
 abstract: |
-  This article introduces the first publicly available data set for analyzing the Brunei housing market, covering more than 30,000 property listings from 1993 to early 2025.
+  This article introduces the first publicly available data set for analysing the Brunei housing market, covering more than 30,000 property listings from 1993 to early 2025.
 The data set, curated from property advertisements in newspapers and online platforms, includes key attributes such as price, location, property type, and physical characteristics, enriched with area-level spatial information.
 Comprehensive and historical, it complements the Brunei Darussalam Central Bank’s Residential Property Price Index (RPPI), addressing the limitations of restricted access to raw RPPI data and its relatively short timeline since its inception in 2015.
-Data collection involved manual transcription from archival sources and automated web scraping using programmatic methods, supported by innovative cleaning with Large Language Models (LLMs) to structure unformatted text.
+Data collection involved manual transcription from archival sources and automated web scraping using programmatic methods, supported by innovative processing with Large Language Models (LLMs) to codify unstructured text.
 The data set enables spatial and temporal analysis, with potential applications in economics, urban planning, and real estate research.
@@
 This data set is the first publicly available compilation of Brunei’s residential property data, covering `{r} scales::comma(nrow(hsp))` listings from `r min(years)` to early `r max(years)`.
-Previous studies on Brunei's housing have been limited to recent or non-spatial data [@ng2022characterising;@jamil2025leveraging], or qualitative in nature due to the lack of structured data [@hassan2011cultural;@hassan2023sociocultural].
+Previous studies on Brunei's housing have either relied on recent or non-spatial data [@ng2022characterising;@jamil2025leveraging], or have primarily employed qualitative methods due to the absence of structured data [@hassan2011cultural;@hassan2023sociocultural].
 Researchers may use this data to explore temporal variations in property listings and to compare housing characteristics across different regions within Brunei.
-
-<!-- - **First of its kind for Brunei**.
-This data set enables comprehensive spatial and temporal analysis of the Brunei housing market.
-To our knowledge, no other publicly available data set exists for this purpose, making it a significant contribution to housing market research.
-Previous studies on Brunei's housing have been limited to recent or non-spatial data [@shabunko2014developing; @ng2022characterising; @jamil2025leveraging], or qualitative in nature due to the lack of a structured data set [@hassan2011cultural; @hassan2023sociocultural].
-This aligns with the growing trend of using data analytics in the real estate industry [@braesemann2020proptech; @delisle2020big].
--->
 
@@
 The spatial information available enables analysis at various administrative levels, providing insights into urban development patterns, regional differences, and the evolution of housing characteristics over time.
-This historical depth is particularly valuable given the lack of previous data before the establishment of the Residential Property Price Index (RPPI) [@bdcb2021technical] in 2015.
+This historical depth is particularly valuable given the lack of data before the establishment of the Residential Property Price Index (RPPI) [@bdcb2021technical] in 2015.
 
@@
 - **Opportunities for handling of missing data**.
-The data set includes instances of missing or inconsistent data, particularly in house characteristics, which present opportunities for further research on data imputation techniques.
+The data set includes instances of missing data, particularly in house characteristics, which present opportunities for further research on data imputation techniques.
 Researchers may explore advanced statistical and machine learning methods to address missing values and improve data reliability.
 The structured format and detailed documentation of the data set support such methodological investigations, making it a valuable testbed for developing and evaluating new approaches to handling incomplete data in real-world data sets.
-
-<!-- - **Application of Large Language Models (LLMs)**.
-This project highlights an innovative use of Large Language Models (LLMs) for data cleaning.
-The LLM was employed to extract structured information from unstructured text descriptions with great accuracy.
-This method significantly reduced the time and effort required for data cleaning.
-It can also be applied to other data sets with unstructured text, such as social media or document archives, to extract valuable information for analysis.
--->
 
@@
 Finally, metadata about the property is included for transparency and informational purposes. 
-The variable agent specifies the (anonymised) identifier of the real estate agent or agency responsible for the listing, while source identifies the platform or medium from which the listing was obtained, such as a newspaper, magazine, or website.
-The method variable details the data collection approach, which is further elaborated in the section below.
+The variable `agent` specifies the (anonymised) identifier of the real estate agent or agency responsible for the listing, while `source` identifies the platform or medium from which the listing was obtained, such as a newspaper, magazine, or website.
+The `method` variable details the data collection approach, which is further elaborated in the section below.
 
@@
 The date variable in the data set refers to the date on which the property listing was obtained. 
-It is important to note that this is not the date the property was sold, nor does it necessarily reflect the precise timing of other transactions related to the property. 
+It is important to note that this is not the date the property was sold, nor does it necessarily reflect the precise timing of any transactions related to the property. 
 Users should set their expectations accordingly, as the primary purpose of the date is to capture the state of the housing market at a specific point in time.
 
-For analysis, we recommend aggregating data by quarters, as represented by the quarter variable. 
+For analysis, we recommend aggregating data by quarters, as represented by the `quarter` variable. 
 This aggregation helps address potential issues like missing data (see subsection below) and provides a more stable and robust representation of market trends, making it suitable for temporal analysis of the housing market.
@@
 
-This data set endeavours to provide complete information regarding the listing date, spatial information, advertised price, and metadata. 
-Nonetheless, we hereby report that missing values are present across various **property characteristics**, including type, tenure, status, plot area, floor area, storeys, beds, and baths. 
-The reason for this is due to the nature of the property advertisements, which may not always include complete information when advertised by the real estate agents. 
-Missing values are represented by blank cells in the CSV file, and the severity of missing values is summarised in @tbl-avail. 
-In summary, 10.5% of the records contain missing values for all key house characteristics (i.e.
-plot area, floor area, beds, and baths), which, depending on the research question, may necessitate imputation or exclusion of these records.
+In any data collection effort, it is not surprising to encounter missing data. 
+Likewise for our data set, we faced the challenge of missing values across several property characteristics--such as plot area, floor area, beds, baths, and others.
+A preliminary analysis of the missing data patterns indicates that the missingness is not completely random, with certain variables displaying dependencies on others.
+Advertisers often include only the information they deem most marketable or necessary, while other details may be omitted if they are considered standard or implied. 
+For instance, a listing might specify the square footage and price but leave out the number of bedrooms and bathrooms, assuming that prospective buyers can infer these details.
 
-# Experimental Design, Materials and Methods
+{{< embed notebooks/missing.qmd#fig-missing-pattern >}}
+
+Missing values are represented by blank cells in the CSV file, and the severity of missingness is summarized in @tbl-avail. 
+In total, 10.1% of the records contain missing values for all key house characteristics (i.e.
+plot area, floor area, beds, and baths), which, depending on the research question, may require imputation or the exclusion of these records.
+
+# Experimental Design, Materials and Methods {#sec-method}
 
@@
 - `date` variables were formatted properly as `Date` objects.
-- Locations were stored as text strings. See the subsection below on spatial data harmonisation for more details.
+- Locations were stored as text strings. See the subsection below on spatial data harmonisation.
 - Any additional information was extracted from the property descriptions and saved as a character vector. This very often contained valuable insights not captured in the primary fields.
 
-Data from 2012 up until the present (December 2024) were managed to be collected using this method, averaging around 1,500 listings per year. 
+Data from 2012 up until the present (January 2025) were managed to be collected using this method, averaging around 1,500 listings per year. 
 While highly efficient, this process relied heavily on the consistency of the site structure of the source webpages.
@@
 As previously mentioned, the web scraping process also captured unstructured information from the property descriptions, which often contained valuable details not captured in the primary fields. 
-In this subsection, we detail the data cleaning process using a pre-trained large language model (LLM) to extract structured information from the unstructured text. 
+In this subsection, we detail the data extraction process using a pre-trained Large Language Model (LLM) to extract structured information from the unstructured text. 
 <!-- The LLM used was the cloud-based OpenAI o1-mini reasoning model[^1], accessed using the `{ellmer}` R package [@wickham2025ellmer] via an API. -->
-The LLM used was a DeepSeek R1 distilled Qwen 14B [@deepseek2025deepseekr1;@qwen2025qwen25], accessed using the `{ellmer}` R package [@wickham2025ellmer] via the Ollama[^2] API, a local interface platform to the LLM.
+The LLM used was the DeepSeek R1 distilled Qwen 14B [@deepseek2025deepseekr1;@qwen2025qwen25], accessed using the `{ellmer}` R package [@wickham2025ellmer] via the Ollama[^2] API, a local interface platform to the LLM.
 
@@
 Each description was processed with a carefully designed prompt (@fig-llm-prompt) to ensure consistent output. 
-This prompt instructed the model to return only the required information in a semicolon-separated format, while handling edge cases such as missing descriptions, non-residential (commercial) properties, or rental property advertisements.
+This prompt instructed the model to return only the required information in a semicolon-separated format, while handling edge cases such as missing descriptions or non-residential (commercial) properties.
 
@@
 Note that this loop was not parallelised, as the LLM already utilises multiple cores, and further parallelisation would not yield significant efficiency gains due to resource constraints.
-The cleaned results were then parsed and stored in a data frame, which was then subjected to manual data-type validation to ensure conformity with the existing data set. 
-It takes, on average, 81.7 seconds to process a single description using a Mac Pro 3.2GHz 16 core Intel Xeon W.
+The cleaned results were then parsed and stored in a data frame, which was then subjected to manual data-type validation to ensure conformity with the existing data set (see the last subsection). 
+It takes, on average, 81.7 seconds to process a single description using a Mac Pro 3.2GHz 16 core Intel Xeon W with 48GB of DDR4 RAM.
 We processed `{r} scales::comma(sum(hsp$method %in% c("web-scrape-llm")))` descriptions from 2020 to 2025 using this method, with a run time of approximately 20 hours in total (spread over three machines).
@@
 
-Our experiments show that the LLM data extraction process with the deepseek-r1:14b model achieved an overall accuracy rate of 96.9% (see [Appendix](#sec-apx-llm) for complete results).
-Errors mostly stemmed from incorrect `status` classification, most likely due to the vagueness of the advertisement listing.
+Our experiments show that the LLM data extraction process with the deepseek-r1:14b model achieved an overall accuracy rate of 96.9% (see Appendix for complete results).
+Errors mostly stemmed from incorrect `status` classification, likely due to the vagueness of the advertisement listing.
 As for the rest of the variables, obvious errors were flagged and corrected manually during our data validation process (described in the subsection following the next one).
@@
 
-## Spatial Data Harmonisation
+## Spatial Data Harmonisation {#sec-spatial-harm}
 
@@
 This is the same format used by the R package `{bruneimap}` [@jamil2024bruneimap].
-The CSV file `bn_kpg_level_data.csv` obtained from this package was used as a reference to standardise the kampong names in the data set, which conveniently also included the mukim and district names for each kampong.
+The CSV file `bn_kpg_level_data.csv` obtained from this package was used as a reference to standardise the kampong names in the data set, which conveniently also includes the mukim and district names for each kampong.
 
@@
 
-## Data Validation
+## Data Validation {#sec-data-validation}
 
@@
 Such anomalies were flagged and manually reviewed for correction.
-
 2.
@@
 This was similarly applied to other variables such as plot area, beds, and baths.
-
 3.	**Duplicate records detection.** We also performed duplicate record detection to identify any repeated entries that might have arisen from overlapping data sources or transcription errors.
@@
 The authors gratefully acknowledge the contributions of Atikah Farhain Yahya, Nurulhanisah Abdul Manan, and Nina Zuhairi towards the collection and processing of the data contained within.
-We also thank the Brunei Darussalam Central Bank (BDCB) for the engaging discussions and support, which were instrumental in the inception of this project.
+We also thank the Brunei Darussalam Central Bank (BDCB) for the engaging discussions and support, which were instrumental in the initiation of this project.
 
@@
 
-The results show that reasoning models outperform the non-reasoning models, with OpenAI's o1-mini model performing the best (99.2% accuracy) followed by the locally run deepseek-r1:14b Ollama model (96.9% accuracy).
-Most inaccuracies are seen in the `status` variable, where the models had a difficult time parsing the correct build status from the vague verbose advertisement.
+OpenAI's models topped the accuracy charts, with the o1-mini and gpt-40 models achieving the accuracy scores of 99.2% and 98.9% respectively.
+The reasoning model deepseek-r1:14b was the best performing locally run model, scoring 96.9% accuracy.
+Evidently, the smaller the model, the less accurate the extraction process (cf. llama3.2 70.8%).
+Most inaccuracies were seen in the `status` variable, where the models had a difficult time parsing the correct build status from the vague verbose advertisement.
 However, key variables such as `price`, `type`, `plot_area`, `floor_area`, `beds`, and `baths` are generally reliable (>90% accuracy).
@@
 The run time statistics for each model is shown in the table below.
-The computer used Apple MacBook Air M2 Silicon on Chip (SoC) and System in Chip (SiP) processors with 16GB RAM.
-Running OpenAI's models are much faster than running models locally, though a paid API key is required.
-Faster local running times are, of course, a function of compute power.
+The computer used was a Mac Pro 3.2GHz 16 core Intel Xeon W with 48GB of DDR4 RAM. 
+At the time of running the tests, graphics card support was not available for the LLM models, which would have significantly reduced the run time.
+Certainly cloud-based models such as OpenAI's models are much faster than running models locally, though a paid API key is required.
 
@@
 ```
-
-<!-- Unit: seconds -->
- <!--            expr       min         lq       mean     median         uq       max neval -->
- <!--        llama3.2  1.077457   1.168078   6.396146   9.595035   9.881765  10.16348    10 -->
- <!--         mistral  2.661627   2.854717  10.437078   2.907932  21.778689  22.21225    10 -->
- <!--            phi4  3.722881   3.925309  14.108101   4.267815  36.986746  38.01499    10 -->
- <!--  deepseek-r1:8b 36.829881  46.254848  65.973720  54.605889  85.101693 112.77667    10 -->
- <!-- deepseek-r1:14b 59.400884   74.62474 117.666112  81.71249   99.57201  283.8539  10 -->
- <!-- deepseek-r1:14b 40.8939 67.19222 127.0108 93.09138 151.2027 541.1301   100 -->
-<!--           gpt-4o  1.279267   1.502509   2.457973   1.733497   2.395108   5.379483     5 a   -->
-<!--          o1-mini  5.968378   6.551901   7.945925   7.506522   9.759592   9.943231     5 a   -->

### 2025-03-05 manuscript.qmd
Final cleanups

@@
 The data set enables spatial and temporal analysis, with potential applications in economics, urban planning, and real estate research.
-Although listing prices serve only as a proxy for market values and may deviate from actual sale prices due to negotiation dynamics and other factors, this data set still provides a valuable resource for reproducible analysis of housing market trends and for informing policy decisions.
+Although listing prices are only a proxy for market values and may deviate from actual sale prices due to negotiation dynamics and other factors, this data set still provides a valuable resource for quantitative analyses of housing market trends and for informing policy decisions.
 keywords:
@@
 
-- **First of its kind for Brunei**.
+- **A first-of-its-kind data set for Brunei**.
 This data set is the first publicly available compilation of Brunei’s residential property data, covering `{r} scales::comma(nrow(hsp))` listings from `r min(years)` to early `r max(years)`.
@@
 - **Historical and spatial insights**.
-Spanning over three decades, this data set allows for the study of long-term housing trends in Brunei.
-The spatial information available enables analysis at various administrative levels, providing insights into urban development patterns, regional differences, and the evolution of housing characteristics over time.
-This historical depth is particularly valuable given the lack of data before the establishment of the Residential Property Price Index (RPPI) [@bdcb2021technical] in 2015.
+Spanning over three decades, this data set enables analysis of long-term housing trends at various administrative levels in Brunei, providing insights into urban development patterns, regional differences, and the evolution of housing characteristics over time.
+This historical depth is particularly valuable given the lack of data prior to the establishment of the Residential Property Price Index (RPPI) [@bdcb2021technical] in 2015.
 
@@
 The data collection process employs a unique combination of manual transcription from archival sources, automated web scraping, and AI-based data cleaning using Large Language Models (LLMs).
-This open source and multi-method approach enhances reproducibility and transparency in data curation.
-The present work provides a reproducible framework for assembling complex data sets, which can be adapted for similar data collection efforts in other other domains, thereby advancing best practices in the field.
+This multi-method approach offers a reproducible framework for assembling complex data sets, which can be adapted for similar data collection efforts in other other domains, thereby advancing best practices in the field.
 
@@
 The housing market is a key indicator of economic health and social well-being, yet comprehensive and publicly accessible data sets in Brunei remain limited. 
-As far as we are aware, this is the first data set of its kind in Brunei, motivated by the need to fill the gap in publicly available data on the local housing market.
+To the best of our knowledge, this is the first data set of its kind in Brunei, motivated by the need to fill the gap in publicly available local housing market data.
 
@@
 Brunei’s private residential property market offers a variety of options, including detached houses, townhouses, and apartments [@hassan2023sociocultural]. 
-Based on this, property types have been categorised into four main groups–Detached, Semi-Detached, Terrace, and Apartment–to accurately reflect the diversity of property types in Brunei.
+Based on this diversity, property types have been categorised into four main groups--Detached, Semi-Detached, Terrace, and Apartment--to accurately reflect the range of residential properties in Brunei.
 Additionally, there are a small number of records that reflect listings for land, which are categorised accordingly as "Land".
@@
 
-The date variable in the data set refers to the date on which the property listing was obtained. 
-It is important to note that this is not the date the property was sold, nor does it necessarily reflect the precise timing of any transactions related to the property. 
-Users should set their expectations accordingly, as the primary purpose of the date is to capture the state of the housing market at a specific point in time.
-
+The `date` variable represents the date on which the property listing was obtained, rather than the date of sale or transaction, and should be interpreted as a snapshot of market conditions at a given point in time.
 For analysis, we recommend aggregating data by quarters, as represented by the `quarter` variable. 
@@
 
-In any data collection effort, it is not surprising to encounter missing data. 
-Likewise for our data set, we faced the challenge of missing values across several property characteristics--such as plot area, floor area, beds, baths, and others.
+In any data collection effort, it is unsurprising to encounter missing data. 
+Likewise in our data set, missing values occur across several property characteristics--such as plot area, floor area, beds, baths, and others.
 A preliminary analysis of the missing data patterns indicates that the missingness is not completely random, with certain variables displaying dependencies on others.
 Advertisers often include only the information they deem most marketable or necessary, while other details may be omitted if they are considered standard or implied. 
-For instance, a listing might specify the square footage and price but leave out the number of bedrooms and bathrooms, assuming that prospective buyers can infer these details.
+For instance, a listing might specify the square footage and price but leave out the number of bedrooms and bathrooms, assuming that prospective buyers are able to infer these details.
 
@@
 **Outlier detection.** Summary statistics analyses to identify and flag anomalous values.
-For instance, a built-up area recorded as 0.1 square feet or beds and baths exceeding 20 is suspect, and highly likely points towards human error or model hallucinations.
+For instance, a built-up area recorded as 0.1 square feet or an implausibly high number of beds and baths (e.g., >20) would highly likely indicate a possible error, prompting manual review.
 Such anomalies were flagged and manually reviewed for correction.
@@
 Evidently, the smaller the model, the less accurate the extraction process (cf. llama3.2 70.8%).
-Most inaccuracies were seen in the `status` variable, where the models had a difficult time parsing the correct build status from the vague verbose advertisement.
+Most inaccuracies occurred in the `status` variable, where models struggled to parse the correct build status from vague advertisement descriptions.
 However, key variables such as `price`, `type`, `plot_area`, `floor_area`, `beds`, and `baths` are generally reliable (>90% accuracy).

### 2025-03-06 manuscript.qmd
Update manuscript

@@
   - Large Language Models
+editor_options: 
+  chunk_output_type: console
 ---
@@
 The data collection process employs a unique combination of manual transcription from archival sources, automated web scraping, and AI-based data cleaning using Large Language Models (LLMs).
-This multi-method approach offers a reproducible framework for assembling complex data sets, which can be adapted for similar data collection efforts in other other domains, thereby advancing best practices in the field.
+This multi-method approach offers a reproducible framework for assembling complex data sets, which can be adapted for similar data collection efforts in other domains, thereby advancing best practices in the field.
 

### 2025-03-06 notebooks/_tables.qmd
Update manuscript

---
title: Tables for word document
author: Haziq Jamil
editor_options: 
  chunk_output_type: console
html-table-processing: none
output: docx
execute:
  echo: false
  message: false
---

```{r}
#| echo: false
#| message: false
#| eval: true 
#| file: data.R
```

## Codebook

```{r}
library(gt)
library(tidyverse)
readxl::read_xlsx(here::here("data/codebook.xlsx")) |>
  rownames_to_column("No.") |>
  gt(rowname_col = "No.") |>
  fmt_markdown(c("Variable", "Details"))
```

## Summary of variables

```{r}
hsp |>
  mutate(
    price = price / 1000,
    storeys = factor(
      ifelse(storeys >= 3, "3+", as.character(storeys)),
      levels = c("1", "2", "3+")
    ),
    district = gsub("Brunei Muara", "Brunei-Muara", district),
    district = factor(district, levels = c("Brunei-Muara", "Belait", "Tutong", "Temburong"))
  ) |>
  tbl_summary(
    include = c(price:baths),
    by = district,
    missing = "no", 
    type = all_continuous() ~ "continuous2",
    statistic = list(
      all_continuous2() ~ c("{mean} ({sd})", Range = "{min} - {max}", "{median} ({p25}, {p75})")
    ),
    label = list(
      price = "Price (BND 1,000)",
      type = "Property type",
      plot_area = "Plot area (acres)",
      floor_area = "Floor area (sq. ft.)",
      storeys = "Number of storeys",
      status = "Development status",
      tenure = "Land tenure",    
      beds = "Number of bedrooms",
      baths = "Number of bathrooms"
    ),
    digits = list(
      baths = 1,
      beds = 1
    )
  ) |>
  add_overall() |>
  add_n() |>
  modify_header(label ~ "**Variable**")
```

## Data availability by year

```{r}
hsp |>
  mutate(
    year = year(date),
    missing_price = is.na(price),
    missing_type = is.na(type),
    missing_tenure = is.na(tenure),
    missing_status = is.na(status),
    missing_plot_area = is.na(plot_area),
    missing_floor_area = is.na(floor_area),
    missing_storeys = is.na(storeys),
    missing_beds = is.na(beds),
    missing_baths = is.na(baths),
    missing_housechar = missing_plot_area & missing_floor_area & missing_beds & missing_baths,
    year = year(quarter),
  ) |>
  summarise(
    count = n(),
    spatial = length(unique(mukim)) / length(unique(hsp$mukim)),
    # price = sum(missing_price),
    type = sum(missing_type),
    house_char = sum(missing_housechar),
    source = list(unique(method)),
    .by = year
  ) |>
  mutate(
    `nat-archive` = map_chr(source, ~ ifelse("nat-archive" %in% .x, "✔", "")),
    `online-archive` = map_chr(source, ~ ifelse("online-archive" %in% .x, "✔", "")),
    `web-scrape` = map_chr(source, ~ ifelse("web-scrape" %in% .x | "web-scrape-llm" %in% .x, "✔", "")),
    llm = map_chr(source, ~ ifelse("web-scrape-llm" %in% .x, "✔", ""))
  ) |> 
  select(-source) |>
  mutate(across(type:house_char, \(x) x / count)) |>
  gt(rowname_col = "year") |>
  cols_align(
    align = "center",
    columns = `nat-archive`:llm
  ) |>
  tab_spanner(
    label = "Data source",
    columns = `nat-archive`:`web-scrape`
  ) |>
  tab_spanner(
    label = "Missing data severity",
    columns = type:house_char
  ) |>
  fmt_percent(
    spatial:house_char,
    decimals = 1
  ) |>
  cols_label(
    year ~ "Year",
    count ~ "Count",
    spatial ~ "Spatial coverage (mukim)",
    type ~ "Property Type",
    house_char ~ "Property Characteristics",
    `nat-archive` ~ "National Archive",
    `online-archive` ~ "Online Archive",
    `web-scrape` ~ "Web Scraping",
    llm ~ "LLM post-processing"
  ) |>
  grand_summary_rows(
    columns = count:house_char,
    fns = list(Mean = "mean"),
    fmt = list(
      ~ fmt_number(., decimals = 0, columns = "count"),
      ~ fmt_percent(., decimals = 1, columns = c("spatial", "type", "house_char"))
    )
  ) |>
  tab_footnote(
    footnote = paste0("Of Brunei’s 39 mukims, only 27 are considered transactable—excluding water villages and remote, non-developable areas."),
    locations = cells_column_labels(columns = spatial)
  ) |>
  tab_footnote(
    footnote = "Unknown property type.",
    locations = cells_column_labels(columns = type)
  ) |>
  tab_footnote(
    footnote = "Missing all of plot area, floor area, beds, and baths variables.",
    locations = cells_column_labels(columns = house_char)
  ) |>
  tab_options(
    quarto.disable_processing = TRUE,
    grand_summary_row.text_transform = "capitalize"
  ) 
```

## LLM Test

```{r}
llmtest_time <-
  tibble(
    model = c("llama3.2", "mistral", "phi4", "deepseek-r1:8b", "deepseek-r1:14b", "gpt-4o", "o1-mini"),
    min = c(1.077457, 2.661627, 3.722881, 36.829881, 40.8939, 1.279267, 5.968378),
    mean = c(6.396146, 10.437078, 14.108101, 65.973720, 117.666112, 2.457973, 7.945925),
    median = c(9.595035, 2.907932, 4.267815, 54.605889, 81.71249, 1.733497, 7.506522),
    max = c(10.16348, 22.21225, 38.01499, 112.77667, 151.2027, 5.379483, 9.943231)
  )

gt(llmtest_time) |>
  fmt_number(decimals = 2) |>
  cols_label(
    model = "Model",
    min = "Minimum",
    mean = "Mean",
    median = "Median",
    max = "Maximum"
  ) |>
  tab_spanner(
    label = "Time (seconds)",
    columns = min:max
  )
```

### 2025-03-06 manuscript.qmd
Fix links

@@
 Several popular models from Ollama were used, namely the Llama3.2 (3B), Mistral (7B), Phi 4 (14B), and DeepSeek-R1 distilled reasoning models based on Llama (8B) and Qwen (14B).
+For the locally run Ollama models, the settings were set to the default values, with the exception of a lowered temperature setting: `temperature = 0.1`, `top-p=0.9` (nucleus sampling), `top-k=40` (top-k sampling), `max-tokens=128`, and `repeat-penalty=1.1`.
 Additionally, two models from OpenAI were included for comparison.
@@
 
-OpenAI's models topped the accuracy charts, with the o1-mini and gpt-40 models achieving the accuracy scores of 99.2% and 98.9% respectively.
+OpenAI's models topped the accuracy charts, with the o1-mini and gpt-4o models achieving the accuracy scores of 99.2% and 98.9% respectively.
 The reasoning model deepseek-r1:14b was the best performing locally run model, scoring 96.9% accuracy.

### 2025-03-06 _cleanup.R
Update _cleanup.R

@@ -16,7 +16,7 @@ for (file in files_to_remove) {
 # Fix the alignment of tfoot in the Quarto-generated HTML
 
 # Path to the HTML file
-html_file <- "docs/index.html"
+html_file <- "_manuscript/index.html"
 
 # Check if the file exists
 if (file.exists(html_file)) {
@@ -36,3 +36,10 @@ if (file.exists(html_file)) {
 } else {
   cat("File not found:", html_file, "\n")
 }
+
+# Copy over the docx manuscript
+source_file <- "_submission/Revision 1/article_rev1.docx"
+destination_file <- "_manuscript/jamil2025archives.docx"
+
+# Copy the file, replacing the destination if it exists
+file.copy(source_file, destination_file, overwrite = TRUE)

### 2025-03-06 notebooks/webscrape.R
Add renv

@@ -36,7 +36,7 @@ location <-
 
 # Put it all in a data frame
 hsp_df <- tibble(
-  location = location
+  location = location,
   price = prices,
   beds = beds,
   baths = baths,

### 2025-03-06 _cleanup.R
Re-add docs/ folder

@@ -16,7 +16,7 @@ for (file in files_to_remove) {
 # Fix the alignment of tfoot in the Quarto-generated HTML
 
 # Path to the HTML file
-html_file <- "_manuscript/index.html"
+html_file <- "docs/index.html"
 
 # Check if the file exists
 if (file.exists(html_file)) {
@@ -39,7 +39,7 @@ if (file.exists(html_file)) {
 
 # Copy over the docx manuscript
 source_file <- "_submission/Revision 1/article_rev1.docx"
-destination_file <- "_manuscript/jamil2025archives.docx"
+destination_file <- "docs/jamil2025archives.docx"
 
 # Copy the file, replacing the destination if it exists
 file.copy(source_file, destination_file, overwrite = TRUE)

### 2025-03-06 notebooks/analysis.qmd
Initialising gh-pages branch

@@
   tab_footnote(
-    footnote = paste0("Of Brunei’s 39 mukims, only 27 are considered transactable—excluding water villages and remote, non-developable areas."),
+    footnote = paste0("Of Brunei’s 39 mukims, only 27 are considered transactable--excluding water villages and remote, non-developable areas."),
     locations = cells_column_labels(columns = spatial)

### 2025-03-06 notebooks/missing.qmd
Initialising gh-pages branch

--- 2025-03-03 missing.qmd
@@
 Some patterns are there, but some are not. This is expected when some of the missing patterns are rare.
+
+## Main article
+
+```{r}
+#| message: false
+#| warning: false
+#| echo: false
+#| label: fig-missing-pattern
+#| fig-cap: Missing data patterns for key house characteristics.
+#| out-width: 100%
+#| fig-width: 9
+#| fig-height: 4
+hsp |>
+  dplyr::select(price, plot_area, floor_area, beds, baths) |>
+  plot_pattern(npat = 16) +
+  coord_flip() +
+  theme(aspect.ratio = 0.3)
+```

### 2025-03-06 _cleanup.R

@@ -1,0 +1,45 @@
+# Cleanup script for Quarto
+files_to_remove <- list.files(
+  pattern = "\\.(bst|spl|cls|ipynb)$"
+)
+
+# Iterate over files and delete them if they exist
+for (file in files_to_remove) {
+  if (file.exists(file)) {
+    file.remove(file)
+    cat("Deleted:", file, "\n")
+  } else {
+    cat("File not found:", file, "\n")
+  }
+}
+
+# Fix the alignment of tfoot in the Quarto-generated HTML
+
+# Path to the HTML file
+html_file <- "docs/index.html"
+
+# Check if the file exists
+if (file.exists(html_file)) {
+  # Read the file content
+  html_content <- readLines(html_file)
+  
+  # Locate the line with <tfoot class="gt_footnotes">
+  html_content <- gsub(
+    pattern = '<tfoot class="gt_footnotes">',
+    replacement = '<tfoot class="gt_footnotes" style="text-align: left;">',
+    x = html_content
+  )
+  
+  # Write the updated content back to the file
+  writeLines(html_content, html_file)
+  cat("Updated text alignment in:", html_file, "\n")
+} else {
+  cat("File not found:", html_file, "\n")
+}
+
+# Copy over the docx manuscript
+source_file <- "_submission/Revision 1/article_rev1.docx"
+destination_file <- "docs/jamil2025archives.docx"
+
+# Copy the file, replacing the destination if it exists
+file.copy(source_file, destination_file, overwrite = TRUE)

### 2025-03-06 notebooks/data.R

@@ -1,0 +1,79 @@
+library(tidyverse)
+library(bruneimap)
+library(gt)
+library(gtsummary)
+library(lubridate)
+library(GGally)
+here::i_am("notebooks/data.R")
+
+# Main data set
+hsp <- 
+  read_csv(here::here("data/hspbn_2025-03-03.csv")) |>
+  mutate(
+    type = factor(type, levels = c("Detached", "Semi-Detached", "Terrace",
+                                   "Apartment", "Land")),
+    tenure = factor(tenure, levels = c("Freehold", "Leasehold", "Strata")),
+    status = factor(status, levels = c("Proposed", "Under Construction", "New", "Resale")),
+    date = as.Date(date, format = "%d/%m/%y"),
+    quarter = zoo::as.yearqtr(quarter)
+  )
+
+# RPPI from BDCB
+rppi <- 
+  read_csv(here::here("data/rppi.csv")) |>
+  mutate(
+    quarter = zoo::as.yearqtr(quarter),
+    rppi = rppi / 100
+  )
+
+# To create median price per square foot, need to filter out "Land" types as
+# well as missing property types. Then create an "Overall" type.
+hsp_all <- 
+  bind_rows(
+    hsp, 
+    mutate(hsp, type = "Overall")
+  ) |> 
+  arrange(date) 
+
+# Create a median price per square foot index
+hsp_rppi <-
+  slider::slide_period_dfr(hsp, hsp$date, "month", \(df) {
+    df |>
+      filter(type != "Land") |>
+      drop_na(floor_area) |>
+      summarise(
+        quarter = first(quarter),
+        price = median(price, na.rm = TRUE),
+        # plot_area = median(plot_area, na.rm = TRUE),
+        floor_area = median(floor_area, na.rm = TRUE)
+      )
+  }, .before = 1, .after = 1) |>
+  summarise(across(price:floor_area, \(x) median(x, na.rm = TRUE)), .by = quarter) |> 
+  drop_na(quarter) |>
+  mutate(
+    price_per_sqft = price / floor_area,
+    index = price_per_sqft / price_per_sqft[quarter == "2015 Q1"],
+  ) |>
+  right_join(rppi, by = join_by(quarter)) 
+
+rppi_mae <-
+  hsp_rppi |>
+  summarise(
+    rmse = (mean( abs(rppi - index) ^ 1)),
[…]

### 2025-03-06 notebooks/llm.R

@@ -1,0 +1,120 @@
+library(tidyverse)
+# remotes::install_github("AlbertRapp/tidychatmodels")
+library(tidychatmodels)
+
+# Note: Before starting, ensure to install Ollama (https://ollama.com), and use
+# the terminal to download the model you wish to use. Here, we use llama3.2.
+
+# Sample description (artificially created)
+x <- "
+🌟 MODERN DOUBLE STOREY DETACHED HOUSE FOR SALE — TUNGKU 🌟
+
+🏡 Prime Location: Nestled in the heart of Kampong Tungku, just a 5-minute drive to The Mall Gadong, this property offers a blend of modern design and urban convenience.
+
+✨ Property Details:
+	•	Land Title: In-Perpetuity
+	•	Selling Price: $350,000
+	•	Land Size: 0.15 acre
+	•	House Size: 3,000 sq. ft
+	•	Bedrooms: 4
+	•	Bathrooms: 4
+	
+✨ House Features:
+	•	Ground Floor: Spacious Living & Dining Area, Wet & Dry Kitchen, 1 Guest Bedroom (en-suite), Guest Toilet, Laundry Room.
+	•	First Floor: Master Bedroom (en-suite with walk-in closet + balcony), 2 Bedrooms (en-suite).
+	
+🚗 Parking: Car porch fits 2 cars.
+🌳 Nearby Amenities: Schools, hospitals, cafes, and parks all within a 10-minute radius.
+
+📲 Contact Us Today!
+For viewing and further details, please contact:
+📞 +673 xxxxxxx | 📱 WhatsApp: +673 xxxxxxx
+📧 email@example.com
+
+🛠️ Services We Provide:
+	•	🏦 Bank Loan Application Assistance
+	•	📑 Legal Documentation Support
+	
+AGENT 🏘️ – Your Trusted Real Estate Partner
+"
+
+# The prompt
+the_prompt <- "
+The following is the description from a property sale listing in Brunei. This description will contain the information about the property, including its characteristics, price, and location. However, some of these descriptions may not contain property listings, and instead contain other or no information at all.
+
+In the case where this description is in fact a property listing, I would like you to extract the following information:
+
+1. Location / area of the property in Brunei, CHARACTER.
+2. Price of the property in Brunei Dollars, NUMERIC.
[…]

### 2025-03-06 notebooks/webscrape.R

@@ -1,0 +1,66 @@
+library(tidyverse)
+library(rvest)
+
+# This is how you get read the HTML into R
+url <- "https://BRUNEIPROPERTYLISTINGWEBSITE.COM/blablabla"  # change this to the actual URL
+html <- read_html(url)
+
+# Extract the house prices
+prices <-
+  html |>
+  html_elements(".property-price") |>
+  html_text2()
+
+# Clean up
+prices <- 
+  str_remove_all(prices, "[^0-9]") |>  # Remove non-numeric characters
+  as.integer()
+
+# Do same thing for number of beds, baths, location, and other remarks
+beds <-
+  html |>
+  html_elements(".property-bed") |>
+  html_text2() |>
+  as.integer()
+
+baths <-
+  html |>
+  html_elements(".property-bath") |>
+  html_text2() |>
+  as.integer()
+
+location <-
+  html |>
+  html_elements(".property-address") |>
+  html_text2()
+
+# Put it all in a data frame
+hsp_df <- tibble(
+  location = location,
+  price = prices,
+  beds = beds,
+  baths = baths,
+)
+
+# Some pages require you to click a "load more" button to see more data
+links <-
+  html |>
+  html_elements(".property-link") |>
+  html_attr("href")
+
+# Create a function that can extract the info I want from a single page
+extract_info <- function(i) {
+  link <- paste0("https://BRUNEIPROPERTYLISTINGWEBSITE.COM", properties[i])  # change this URL
+  html <- read_html(link)
+  out <-
+    html |>
+    html_elements("p") |>  # The descriptions are the .p element
+    html_text2()
+  out[1]
+}
+
+res <- map(
+  .x = seq_along(properties),
+  .f = extract_info,
+  .progress = TRUE
+)

### 2025-03-06 _tex/manuscript.tex
Built site for gh-pages

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  number]{elsarticle}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{241,243,245}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother

\usepackage{booktabs}
\usepackage{caption}
\usepackage{longtable}
\usepackage{colortbl}
\usepackage{array}
\usepackage{anyfontsize}
\usepackage{multirow}
\usepackage[a4paper, margin=1in]{geometry}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\usepackage{pdflscape}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\journal{Data in Brief}

\usepackage[]{natbib}
\bibliographystyle{elsarticle-num}
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={From Archives to AI: Residential Property Data Across Three Decades in Brunei Darussalam},
  pdfkeywords={Housing Market, Brunei, Property Listings, Spatial
Data, Web Scraping, Large Language Models},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\setlength{\parindent}{6pt}
\begin{document}

\begin{frontmatter}
\title{From Archives to AI: Residential Property Data Across Three
Decades in Brunei Darussalam}
\author[1]{Haziq Jamil%
\corref{cor1}%
}
 \ead{haziq.jamil@ubd.edu.bn} 
\author[1]{Amira Barizah Noorosmawie%
%
}

\author[1]{Hafeezul Waezz Rabu%
%
}

\author[2]{Lutfi Abdul Razak%
%
}
 \ead{lutfi.razak@ubd.edu.bn}

\affiliation[1]{organization={Universiti Brunei Darussalam, Mathematical
Sciences, Faculty of Science},addressline={Universiti Brunei Darussalam,
Jalan Tungku Link},city={Bandar Seri
Begawan},country={Brunei},countrysep={,},postcode={BE
1410},postcodesep={}}
\affiliation[2]{organization={UBD School of Business and
Economics},addressline={Universiti Brunei Darussalam, Jalan Tungku
Link},city={Bandar Seri
Begawan},country={Brunei},countrysep={,},postcode={BE
1410},postcodesep={}}

\cortext[cor1]{Corresponding author}

\begin{abstract}
This article introduces the first publicly available data set for
analysing the Brunei housing market, covering more than 30,000 property
listings from 1993 to early 2025. The data set, curated from property
advertisements in newspapers and online platforms, includes key
attributes such as price, location, property type, and physical
characteristics, enriched with area-level spatial information.
Comprehensive and historical, it complements the Brunei Darussalam
Central Bank's Residential Property Price Index (RPPI), addressing the
limitations of restricted access to raw RPPI data and its relatively
short timeline since its inception in 2015. Data collection involved
manual transcription from archival sources and automated web scraping
using programmatic methods, supported by innovative processing with
Large Language Models (LLMs) to codify unstructured text. The data set
enables spatial and temporal analysis, with potential applications in
economics, urban planning, and real estate research. Although listing
prices are only a proxy for market values and may deviate from actual
sale prices due to negotiation dynamics and other factors, this data set
still provides a valuable resource for quantitative analyses of housing
market trends and for informing policy decisions.
\end{abstract}

\begin{keyword}
    Housing Market \sep Brunei \sep Property Listings \sep Spatial
Data \sep Web Scraping \sep 
    Large Language Models
\end{keyword}
\end{frontmatter}

\section{Value of the Data}\label{value-of-the-data}

\begin{itemize}
\item
  \textbf{A first-of-its-kind data set for Brunei}. This data set is the
  first publicly available compilation of Brunei's residential property
  data, covering 31,116 listings from 1993 to early 2025. Previous
  studies on Brunei's housing have either relied on recent or
  non-spatial data \citep{ng2022characterising, jamil2025leveraging}, or
  have primarily employed qualitative methods due to the absence of
  structured data \citep{hassan2011cultural, hassan2023sociocultural}.
  Researchers may use this data to explore temporal variations in
  property listings and to compare housing characteristics across
  different regions within Brunei.
\item
  \textbf{Historical and spatial insights}. Spanning over three decades,
  this data set enables analysis of long-term housing trends at various
  administrative levels in Brunei, providing insights into urban
  development patterns, regional differences, and the evolution of
  housing characteristics over time. This historical depth is
  particularly valuable given the lack of data prior to the
  establishment of the Residential Property Price Index (RPPI)
  \citep{bdcb2021technical} in 2015.
\item
  \textbf{Methodological innovation in data curation}. The data
  collection process employs a unique combination of manual
  transcription from archival sources, automated web scraping, and
  AI-based data cleaning using Large Language Models (LLMs). This
  multi-method approach offers a reproducible framework for assembling
  complex data sets, which can be adapted for similar data collection
  efforts in other domains, thereby advancing best practices in the
  field.
\end{itemize}

\begin{itemize}
\tightlist
\item
  \textbf{Opportunities for handling of missing data}. The data set
  includes instances of missing data, particularly in house
  characteristics, which present opportunities for further research on
  data imputation techniques. Researchers may explore advanced
  statistical and machine learning methods to address missing values and
  improve data reliability. The structured format and detailed
  documentation of the data set support such methodological
  investigations, making it a valuable testbed for developing and
  evaluating new approaches to handling incomplete data in real-world
  data sets.
\end{itemize}

\section{Background}\label{background}

The housing market is a key indicator of economic health and social
well-being, yet comprehensive and publicly accessible data sets in
Brunei remain limited. To the best of our knowledge, this is the first
data set of its kind in Brunei, motivated by the need to fill the gap in
publicly available local housing market data.

Currently, the Brunei Darussalam Central Bank (BDCB) produces a
Residential Property Price Index (RPPI) \citep{bdcb2021technical} using
data sourced from financial institutions, such as bank loan data sets.
While the RPPI is published quarterly, the underlying raw data is not
publicly available due to privacy restrictions. This limits research
opportunities and transparency in understanding broader housing market
trends. Furthermore, since the RPPI only began in 2015, historical
housing data for Brunei is lacking.

We address these challenges by providing a cost-effective and timely
means to collect and analyse housing market data. Covering records from
1993 onward, it offers historical depth that complements--and extends
beyond--the RPPI. It is valuable not only for tracking property price
trends but also for advancing research in economics, urban planning, and
real estate, supporting informed decision-making across sectors.

\section{Data Description}\label{data-description}

The data has been curated into a single Comma-Separated Values (CSV)
file named \texttt{hspbn\_2024-12-12.csv}. The data set contains 31,116
property listing records which are enriched with area-level geotagged
spatial information, spanning a period of 33 years from Mar 1993 to Feb
2025. The 18 columns of this data set capture information for each
property listing as detailed in Table~\ref{tbl-codebook} below.

\begin{table}

\caption{\label{tbl-codebook}Codebook for the house price data set.}

\centering{

\fontsize{9.0pt}{10.8pt}\selectfont
\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}}l|ll>{\raggedright\arraybackslash}p{\dimexpr 300.00pt -2\tabcolsep-1.5\arrayrulewidth}}
\toprule
 & Variable & Type & Details \\ 
\midrule\addlinespace[2.5pt]
1 & \texttt{id} & Integer & Unique identifier for each property listing. \\ 
2 & \texttt{date} & Date & Date when the property listing was collected. \\ 
3 & \texttt{quarter} & Date & Quarter of the listing date in the format \texttt{YYYY Qq} (e.g., 2016 Q3). \\ 
4 & \texttt{kampong} & Spatial Area & The village where the property is located. \\ 
5 & \texttt{mukim} & Spatial Area & The sub-district administrative area where the property is located. \\ 
6 & \texttt{district} & Spatial Area & The main district where the property is located. \\ 
7 & \texttt{price} & Numeric & Listing price of the property in Brunei Dollars (BND). \\ 
8 & \texttt{type} & Character & Type of property. One of ``Detached'', ``Semi-Detached'', ``Terrace'', ``Apartment'', or ``Land''. \\ 
9 & \texttt{tenure} & Character & The land tenure for the property. One of ``Freehold'', ``Leasehold'', or ``Strata''. \\ 
10 & \texttt{status} & Character & Current status of the listing. One of ``Proposed'', ``Under Construction'', ``New'', or ``Resale''. \\ 
11 & \texttt{plot\_area} & Numeric & Total area of the land plot in acres. \\ 
12 & \texttt{floor\_area} & Numeric & Built up floor area of the property in square feet. \\ 
13 & \texttt{storeys} & Integer & Number of storeys or floors in the property. \\ 
14 & \texttt{beds} & Integer & Number of bedrooms in the property. \\ 
15 & \texttt{baths} & Integer & Number of bathrooms in the property. \\ 
16 & \texttt{agent} & Character & Anonymised identifier of the real estate agent or agency handling the listing. \\ 
17 & \texttt{source} & Character & Source of the listing. \\ 
18 & \texttt{method} & Character & Method of data collection. \\ 
\bottomrule
\end{tabular*}

\textsubscript{Source:
\href{https://Bruneiverse.github.io/house-data/manuscript.qmd.html}{Article
Notebook}}

}

\end{table}%

\subsection{Property Characteristics}\label{property-characteristics}

The data set includes a range of property characteristics suitable for
exploring the relationship between property attributes and prices. This
section clarifies and provides context for the key variables in the data
set.

Brunei's private residential property market offers a variety of
options, including detached houses, townhouses, and apartments
\citep{hassan2023sociocultural}. Based on this diversity, property types
have been categorised into four main groups--Detached, Semi-Detached,
Terrace, and Apartment--to accurately reflect the range of residential
properties in Brunei. Additionally, there are a small number of records
that reflect listings for land, which are categorised accordingly as
``Land''.

Property tenure refers to the legal terms under which a person holds
ownership or occupancy rights to a property. In Brunei, property tenure
can be classified into three main categories: Freehold (in perpetuity),
Leasehold, and Strata. The latter two refer to a limited time-limited
ownership, although details about the remaining duration of the tenure
are almost never included in property listings. Strata titles differ
from Leasehold titles in that they grant ownership of a specific portion
of a property, such as an apartment, while sharing ownership of common
areas.

The data set also includes information on the status of the property
listing, indicating whether the advertisement refers to a proposed
development, a newly completed development, or a property being resold.
This categorical variable may be useful for analysing price differences
across different types of listings. While the exact age of properties
being resold would be invaluable for such analyses, this information is
rarely included in advertisements. Instead, the listing status may serve
as a useful proxy for property age.

The numerical variables in the data set are plot area, floor area,
storeys, beds, and baths, each providing information on the physical
attributes of the property. Note that plot area is measured in acres,
while floor area in square feet, as these are the units most familiar
and commonly used in Brunei. Users of this data set may choose to
convert these units as needed for their analysis.

Finally, metadata about the property is included for transparency and
informational purposes. The variable \texttt{agent} specifies the
(anonymised) identifier of the real estate agent or agency responsible
for the listing, while \texttt{source} identifies the platform or medium
from which the listing was obtained, such as a newspaper, magazine, or
website. The \texttt{method} variable details the data collection
approach, which is further elaborated in the section below.

\begin{landscape}

\begin{table}

\caption{\label{tbl-summary}Summary of housing data.}

\centering{

\fontsize{6.8pt}{8.1pt}\selectfont
\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}}lcccccc}
\toprule
\textbf{Variable} & \textbf{N} & \textbf{Overall}  N = 31,116\textsuperscript{\textit{1}} & \textbf{Brunei-Muara}  N = 28,570\textsuperscript{\textit{1}} & \textbf{Belait}  N = 1,484\textsuperscript{\textit{1}} & \textbf{Tutong}  N = 767\textsuperscript{\textit{1}} & \textbf{Temburong}  N = 295\textsuperscript{\textit{1}} \\ 
\midrule\addlinespace[2.5pt]
Price (BND 1,000) & 31,116 &  &  &  &  &  \\ 
    Mean (SD) &  & 340 (381) & 340 (393) & 372 (208) & 259 (87) & 421 (324) \\ 
    Min - Max &  & 70 - 13,800 & 70 - 13,800 & 98 - 2,800 & 116 - 680 & 118 - 1,800 \\ 
    Median (Q1, Q3) &  & 288 (230, 380) & 285 (230, 380) & 320 (268, 400) & 245 (198, 310) & 390 (250, 430) \\ 
Property type & 27,231 &  &  &  &  &  \\ 
    Detached &  & 17,416 (64\%) & 16,307 (65\%) & 520 (42\%) & 509 (74\%) & 80 (56\%) \\ 
    Semi-Detached &  & 3,823 (14\%) & 3,591 (14\%) & 97 (7.8\%) & 128 (19\%) & 7 (4.9\%) \\ 
    Terrace &  & 4,449 (16\%) & 4,134 (16\%) & 213 (17\%) & 48 (7.0\%) & 54 (38\%) \\ 
    Apartment &  & 1,527 (5.6\%) & 1,106 (4.4\%) & 414 (33\%) & 4 (0.6\%) & 3 (2.1\%) \\ 
    Land &  & 16 (<0.1\%) & 11 (<0.1\%) & 4 (0.3\%) & 1 (0.1\%) & 0 (0\%) \\ 
Land tenure & 12,877 &  &  &  &  &  \\ 
    Freehold &  & 9,296 (72\%) & 8,405 (76\%) & 368 (33\%) & 381 (80\%) & 142 (97\%) \\ 
    Leasehold &  & 2,783 (22\%) & 2,221 (20\%) & 467 (41\%) & 91 (19\%) & 4 (2.7\%) \\ 
    Strata &  & 798 (6.2\%) & 504 (4.5\%) & 291 (26\%) & 3 (0.6\%) & 0 (0\%) \\ 
Development status & 22,481 &  &  &  &  &  \\ 
    Proposed &  & 4,004 (18\%) & 3,660 (18\%) & 103 (8.8\%) & 197 (33\%) & 44 (31\%) \\ 
    Under Construction &  & 9,420 (42\%) & 8,600 (42\%) & 535 (46\%) & 244 (41\%) & 41 (29\%) \\ 
    New &  & 7,724 (34\%) & 7,122 (35\%) & 413 (35\%) & 132 (22\%) & 57 (40\%) \\ 
    Resale &  & 1,333 (5.9\%) & 1,186 (5.8\%) & 120 (10\%) & 26 (4.3\%) & 1 (0.7\%) \\ 
Plot area (acres) & 23,368 &  &  &  &  &  \\ 
    Mean (SD) &  & 0.16 (0.12) & 0.15 (0.11) & 0.19 (0.15) & 0.18 (0.17) & 0.23 (0.21) \\ 
    Min - Max &  & 0.01 - 2.00 & 0.01 - 1.69 & 0.01 - 1.01 & 0.04 - 2.00 & 0.05 - 0.96 \\ 
    Median (Q1, Q3) &  & 0.13 (0.08, 0.19) & 0.13 (0.08, 0.19) & 0.13 (0.06, 0.27) & 0.14 (0.10, 0.21) & 0.16 (0.13, 0.26) \\ 
Floor area (sq. ft.) & 16,665 &  &  &  &  &  \\ 
    Mean (SD) &  & 2,602 (1,047) & 2,629 (1,062) & 2,423 (913) & 2,133 (651) & 2,786 (751) \\ 
    Min - Max &  & 500 - 14,411 & 500 - 14,411 & 600 - 7,500 & 1,093 - 7,000 & 950 - 3,700 \\ 
    Median (Q1, Q3) &  & 2,427 (2,000, 3,000) & 2,465 (2,000, 3,000) & 2,218 (1,800, 2,800) & 2,013 (1,826, 2,450) & 3,016 (2,790, 3,229) \\ 
Number of storeys & 13,644 &  &  &  &  &  \\ 
    1 &  & 1,700 (12\%) & 1,462 (12\%) & 160 (35\%) & 71 (17\%) & 7 (4.2\%) \\ 
    2 &  & 11,266 (83\%) & 10,493 (83\%) & 280 (61\%) & 348 (83\%) & 145 (87\%) \\ 
    3+ &  & 678 (5.0\%) & 642 (5.1\%) & 19 (4.1\%) & 2 (0.5\%) & 15 (9.0\%) \\ 
Number of bedrooms & 26,631 &  &  &  &  &  \\ 
    Mean (SD) &  & 4.2 (0.9) & 4.2 (0.9) & 4.0 (1.1) & 3.9 (0.7) & 4.7 (1.0) \\ 
    Min - Max &  & 0.0 - 12.0 & 0.0 - 12.0 & 1.0 - 10.0 & 2.0 - 7.0 & 2.0 - 7.0 \\ 
    Median (Q1, Q3) &  & 4.0 (4.0, 5.0) & 4.0 (4.0, 5.0) & 4.0 (3.0, 4.0) & 4.0 (3.0, 4.0) & 5.0 (4.0, 5.0) \\ 
Number of bathrooms & 19,694 &  &  &  &  &  \\ 
    Mean (SD) &  & 3.7 (1.2) & 3.7 (1.2) & 3.3 (1.1) & 3.3 (1.0) & 3.2 (1.5) \\ 
    Min - Max &  & 1.0 - 11.0 & 1.0 - 11.0 & 1.0 - 8.0 & 1.0 - 7.0 & 1.0 - 5.0 \\ 
    Median (Q1, Q3) &  & 3.0 (3.0, 4.0) & 3.0 (3.0, 4.0) & 3.0 (3.0, 4.0) & 3.0 (2.0, 4.0) & 2.0 (2.0, 5.0) \\ 
\bottomrule
\end{tabular*}
\begin{minipage}{\linewidth}
\textsuperscript{\textit{1}}n (\%)\\
\end{minipage}

\textsubscript{Source:
\href{https://Bruneiverse.github.io/house-data/manuscript.qmd.html}{Article
Notebook}}

}

\end{table}%

\end{landscape}

\subsection{Spatial Information}\label{spatial-information}

In Brunei Darussalam, the administrative areas are organised
hierarchically into three levels. At the smallest level is the
\emph{kampong}, the Malay word for village. While a typical village
refers to a traditional rural settlement, it is also used to describe an
urbanised area located within or near the capital city or a town. It may
even refer to a part of public housing estates. Several kampongs grouped
together form a \emph{mukim}, which serves as a sub-district
administrative area. Finally, multiple mukims are nested within a
\emph{district}, the largest administrative unit, of which Brunei has
four: Brunei-Muara, Belait, Tutong, and Temburong. In our data set, each
property listing is associated with a specific kampong, mukim, and
district, allowing for spatial analysis at different scales.

Importantly, the names of the kampongs, mukims, and districts have been
harmonised with a standardised naming convention to ensure consistency
across the data set. This also allows for ease of integration into
Geographic Information Systems (GIS) software for spatial analysis and
visualisation, namely the \texttt{\{bruneimap\}} R package
\citep{jamil2024bruneimap}.

\begin{figure}[H]

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/notebooks-analysis-fig-spatial-output-2.png}}

}

\caption{\label{fig-spatial}Spatial distribution of median property
prices by mukim.}

\end{figure}%

\textsubscript{Source:
\href{https://Bruneiverse.github.io/house-data/notebooks/analysis-preview.html\#cell-fig-spatial}{Plots
and Data Summaries}}

\subsection{Listing Dates}\label{listing-dates}

The \texttt{date} variable represents the date on which the property
listing was obtained, rather than the date of sale or transaction, and
should be interpreted as a snapshot of market conditions at a given
point in time. For analysis, we recommend aggregating data by quarters,
as represented by the \texttt{quarter} variable. This aggregation helps
address potential issues like missing data (see subsection below) and
provides a more stable and robust representation of market trends,
making it suitable for temporal analysis of the housing market.

\begin{figure}[H]

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/notebooks-analysis-fig-price-evolution-output-2.png}}

}

\caption{\label{fig-price-evolution}Median smoothed prices per square
foot by property type using a 24-month (8-quarter) rolling window.}

\end{figure}%

\textsubscript{Source:
\href{https://Bruneiverse.github.io/house-data/notebooks/analysis-preview.html\#cell-fig-price-evolution}{Plots
and Data Summaries}}

\subsection{Missing Values}\label{missing-values}

In any data collection effort, it is unsurprising to encounter missing
data. Likewise in our data set, missing values occur across several
property characteristics--such as plot area, floor area, beds, baths,
and others. A preliminary analysis of the missing data patterns
indicates that the missingness is not completely random, with certain
variables displaying dependencies on others. Advertisers often include
only the information they deem most marketable or necessary, while other
details may be omitted if they are considered standard or implied. For
instance, a listing might specify the square footage and price but leave
out the number of bedrooms and bathrooms, assuming that prospective
buyers are able to infer these details.

\begin{figure}[H]

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/notebooks-missing-fig-missing-pattern-output-2.png}}

}

\caption{\label{fig-missing-pattern}Missing data patterns for key house
characteristics.}

\end{figure}%

\textsubscript{Source:
\href{https://Bruneiverse.github.io/house-data/notebooks/missing-preview.html\#cell-fig-missing-pattern}{Missing
Data Patterns}}

Missing values are represented by blank cells in the CSV file, and the
severity of missingness is summarized in Table~\ref{tbl-avail}. In
total, 10.1\% of the records contain missing values for all key house
characteristics (i.e.~plot area, floor area, beds, and baths), which,
depending on the research question, may require imputation or the
exclusion of these records.

\section{Experimental Design, Materials and Methods}\label{sec-method}

In this section we describe the data collection process, which involved
either a manual transcription of property listings from newspapers, or
web scraping of online property agent listings. The data collection
method varied over the years due to the availability of data sources and
the evolution of technology. For the later years, a large language model
(LLM) was also employed to perform data cleaning on the web scraped
data. Table~\ref{tbl-avail} details which method was used for each year
in the data set, and whether the data was subjected to LLM
post-processing.

All analyses were conducted using the R programming language
\citep{rcoreteam2024language}, with specific packages used described in
each subsection below.

\begin{table}

\caption{\label{tbl-avail}Data availability by year.}

\centering{

}

\end{table}%

\textsubscript{Source:
\href{https://Bruneiverse.github.io/house-data/notebooks/analysis-preview.html\#cell-tbl-avail}{Plots
and Data Summaries}}

\subsection{Manual Data Collection}\label{manual-data-collection}

Early years data collection was conducted manually, involving the
transcription of property listing details from advertisements into a
digital tabular format. This process was carried out by two of the
authors over a period of nine months, from October 2023 to July 2024,
working at a manageable pace. A total of 12,092 data points were
collected in this manner, which translates to processing approximately
150 entries per week per person. Spreading the task over such an
extended period ensured that transcribers were never under undue time
pressure, which could have led to errors due to fatigue.

The primary sources of the property listings were local newspapers and
magazines. Physical copies were accessed through the National Archive of
Brunei Darussalam, while digital versions, which are digitised replicas
of the physical newspapers, were obtained online. These digital formats
could not be scraped due to their lack of structured data, necessitating
manual transcription.

Although daily newspapers from 1993 onward were available at the
National Archive, the classified sections were not always present. From
1993 to 1999, property advertisements were found only in Friday
editions, and occasionally on Saturdays. Thus, newspapers from both
these days were reviewed weekly to capture the listings data. This
yielded roughly between 300 and 700 listings per year.

From the year 2000 onwards, property advertisements were published daily
in the classifieds section. However, reviewing every single daily
edition was not practical and would increase the likelihood of recording
duplicate listings, thus necessitating a sampling strategy. The sampling
was done as follows. Three newspaper editions per week were selected,
and the classifieds section was reviewed for property listings. When a
listing was found, it was recorded after careful filtering to ensure it
was unique. This manual filtering process involved cross-checking based
on the real estate agent, house characteristics, price, location, and
date proximity. To avoid duplication, the same house listing was not
recorded more than once within a quarter. This process yielded roughly
the same number of listings per year as the earlier years.

\subsection{Web Scraping}\label{web-scraping}

To compile additional property data for the study beyond manual data
collection, web scraping was employed using the R programming language,
making use of the \texttt{\{rvest\}} package \citep{wickham2024rvest}.
This method enabled the systematic extraction of structured information
from various local property listing websites such as panvilla.com (now
defunct), bruhome.com, and bruneiproperty.com.bn. Such websites provide
extensive details on properties listed as ``for sale'' in Brunei,
aggregating advertisements from real estate agents and property
developers.

\begin{figure}

\begin{minipage}{\linewidth}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{figures/house-mockup1.png}}

}

\subcaption{\label{fig-mockup-listing}}

\subcaption{\label{}A mockup of the structure of property listing
showing various HTML elements.}
\end{minipage}%
\newline
\begin{minipage}{\linewidth}

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{figures/house-mockup2.png}}

}

\subcaption{\label{fig-mockup-table}}

\subcaption{\label{}Example paragraph containing description within the
``See Details'' link for each property.}
\end{minipage}%

\caption{\label{fig-web-scrape}Illustration of a property listing from a
typical Bruneian property portal. Attribution: Freepik.}

\end{figure}%

The process began by identifying the structure of the target websites,
focusing on the HTML tags and classes containing the relevant
information. The goal here is to programmatically pinpoint and collect
specific information like text, links, or attributes. For example,
elements such as property prices, number of bedrooms, bathrooms,
location, and other features were enclosed within specific HTML
elements, which \texttt{\{rvest\}} functions like
\texttt{html\_elements()} and \texttt{html\_text2()} could target and
extract efficiently. Figure~\ref{fig-mockup-listing} illustrates the
structure of a typical property listing showing the various HTML
elements to target. Example code to perform this task in available in
the repository.

Each webpage displayed a fixed number of listings (e.g.~128 per page).
To scrape all pages, a loop was created to iterate through each page by
modifying the URL (such as with an
\texttt{\&offset=\textless{}number\textgreater{}} parameter, where
\texttt{\textless{}number\textgreater{}} represents the cumulative
number of listings already scraped).

Extracted data required some cleaning to standardise formats for
analysis. Specifically:

\begin{itemize}
\tightlist
\item
  \texttt{price} variables were cleaned by removing non-numeric
  characters and converted to integers.
\item
  \texttt{beds} and \texttt{baths} were converted to integers.
\item
  \texttt{date} variables were formatted properly as \texttt{Date}
  objects.
\item
  Locations were stored as text strings. See the subsection below on
  spatial data harmonisation.
\item
  Any additional information was extracted from the property
  descriptions and saved as a character vector. This very often
  contained valuable insights not captured in the primary fields.
\end{itemize}

Data from 2012 up until the present (January 2025) were managed to be
collected using this method, averaging around 1,500 listings per year.
While highly efficient, this process relied heavily on the consistency
of the site structure of the source webpages. Changes to website layouts
or closures over time required significant updates to the scraping
scripts. To overcome these issues, alternative approaches, such as using
Large Language Models (LLMs) were considered. This is explained in the
next subsection.

\subsection{LLM Data Extraction}\label{llm-data-extraction}

As previously mentioned, the web scraping process also captured
unstructured information from the property descriptions, which often
contained valuable details not captured in the primary fields. In this
subsection, we detail the data extraction process using a pre-trained
Large Language Model (LLM) to extract structured information from the
unstructured text. The LLM used was the DeepSeek R1 distilled Qwen 14B
\citep{deepseek2025deepseekr1, qwen2025qwen25}, accessed using the
\texttt{\{ellmer\}} R package \citep{wickham2025ellmer} via the
Ollama\footnote{\url{https://github.com/ollama/ollama}} API, a local
interface platform to the LLM.

The primary goal was to extract the house characteristics of interest,
specifically variables 7 to 15 as per Table~\ref{tbl-codebook}, from the
unstructured verbose descriptions scraped from property listing
websites. Each description was processed with a carefully designed
prompt (Figure~\ref{fig-llm-prompt}) to ensure consistent output. This
prompt instructed the model to return only the required information in a
semicolon-separated format, while handling edge cases such as missing
descriptions or non-residential (commercial) properties.

\begin{figure}

\centering{

\begin{Shaded}
\begin{Highlighting}[]
\StringTok{"The following is the description from a property sale listing in Brunei. This }
\StringTok{description will contain the information about the property, including its }
\StringTok{characteristics, price, and location. However, some of these descriptions may }
\StringTok{not contain property listings, and instead contain other or no information at }
\StringTok{all.}

\StringTok{In the case where this description is in fact a property listing, I would like }
\StringTok{you to extract the following information:}

\StringTok{1. Location / area of the property in Brunei, CHARACTER.}
\StringTok{2. Price of the property in Brunei Dollars, NUMERIC.}
\StringTok{3. Type of property, CHARACTER {-}{-} select from Detached, Semi{-}Detached, Terrace, }
\StringTok{Apartment, or Land.}
\StringTok{4. Land tenure, CHARACTER {-}{-} select from Freehold, Leasehold, or Strata. If }
\StringTok{other than this, return \textquotesingle{}NA\textquotesingle{}.}
\StringTok{5. Status of the property, CHARACTER {-}{-} select from Proposed, Under }
\StringTok{Construction, New, or Resale.}
\StringTok{6. Land area in acres, NUMERIC.}
\StringTok{7. Built up area in square feet, NUMERIC.}
\StringTok{8. Number of storeys, INTEGER.}
\StringTok{9. Number of bedrooms, INTEGER.}
\StringTok{10. Number of bathrooms, INTEGER.}

\StringTok{Further instructions:}

\StringTok{{-} Please return **semicolon** separated values like this:}

\StringTok{  Kg Tanah Jambu; 250000; Detached ; Freehold ; New     ; 0.3 ; 2500; 2;  3; 3}
\StringTok{  Kg Tungku     ; 300000; Terrace  ; Leasehold; Resale  ; 0.25; 1700; 2;  3; 2 }
\StringTok{  Kg Kiarong    ; 200000; Apartment; Strata   ; Proposed; 0.1 ; 1000; NA; 2; 2}
\StringTok{  etc.}
\StringTok{  NUMBERS SHOULD NOT CONTAIN comma (,) for thousands separator}

\StringTok{{-} If any of the 10 values are missing, please return \textquotesingle{}NA\textquotesingle{} for that value.}

\StringTok{{-} If the description does not contain a property listing (for example, it is a }
\StringTok{rental property advertisement), return \textquotesingle{}NA\textquotesingle{} for all 10 values.}

\StringTok{{-} DO NOT RESPOND WITH ANYTHING ELSE OTHER THAN THE REQUIRED INFORMATION."}
\end{Highlighting}
\end{Shaded}

\textsubscript{Source:
\href{https://Bruneiverse.github.io/house-data/manuscript.qmd.html}{Article
Notebook}}

}

\caption{\label{fig-llm-prompt}The LLM prompt to clean descriptions
obtained from web scraping.}

\end{figure}%

The verbose descriptions were fed into the model one at a time using a
loop, with the LLM extracting and returning the relevant details. Note
that this loop was not parallelised, as the LLM already utilises
multiple cores, and further parallelisation would not yield significant
efficiency gains due to resource constraints. The cleaned results were
then parsed and stored in a data frame, which was then subjected to
manual data-type validation to ensure conformity with the existing data
set (see the last subsection). It takes, on average, 81.7 seconds to
process a single description using a Mac Pro 3.2GHz 16 core Intel Xeon W
with 48GB of DDR4 RAM. We processed 5,055 descriptions from 2020 to 2025
using this method, with a run time of approximately 20 hours in total
(spread over three machines).

To evaluate the accuracy of the LLM data extraction, a test data set of
100 artificially generated descriptions was created, with each
description written in the style of a typical property listing. For each
house characteristic, the accuracy of the LLM was calculated by
comparing the extracted value to the ground truth. For numeric
variables, values were considered accurate if they fell within 1\% of
the corresponding ground truth value. For character variables, accuracy
was determined using the normalised Levenshtein distance, ensuring
differences remained within a set threshold. The test data also
contained missing information in certain property characteristics, which
the LLM was expected to handle correctly. A correct handling was counted
if both the extracted and ground truth values were missing. Accuracy was
then averaged per characteristic as well as across all characteristics.

Our experiments show that the LLM data extraction process with the
deepseek-r1:14b model achieved an overall accuracy rate of 96.9\% (see
Appendix for complete results). Errors mostly stemmed from incorrect
\texttt{status} classification, likely due to the vagueness of the
advertisement listing. As for the rest of the variables, obvious errors
were flagged and corrected manually during our data validation process
(described in the subsection following the next one). Overall, the LLM
was found to be a valuable tool for extracting structured information
from unstructured text, significantly reducing the time and effort
required for data extraction.

\subsection{Spatial Data Harmonisation}\label{sec-spatial-harm}

Whether the data was collected manually, through web scraping, or
cleaned using the LLM, the spatial information extracted was often
inconsistent in terms of naming conventions and granularity. To address
this, a spatial data harmonisation process was conducted to standardise
the names of the kampongs (villages) in the data set to the format used
by Department of Economic Planning and Statistics (DEPS), Ministry of
Finance and Economy, Brunei Darussalam as per the most recent census
\citep{deps2022population}. This is the same format used by the R
package \texttt{\{bruneimap\}} \citep{jamil2024bruneimap}. The CSV file
\texttt{bn\_kpg\_level\_data.csv} obtained from this package was used as
a reference to standardise the kampong names in the data set, which
conveniently also includes the mukim and district names for each
kampong.

The majority of house listings in Brunei specify the property location
using the kampong name, the smallest administrative unit in the country.
The task in hand was then to match these kampong names in the data set
with the standardised names in the reference file. Several challenges
were encountered during this process, including:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Spelling variations or misspellings, though these were relatively
  straightforward to correct.
\item
  Unknown entries, where the correct kampong could sometimes be inferred
  from the geographical context; otherwise, these were set to
  \texttt{NA}.
\item
  Multiple matches, occurring when two or more kampongs shared the same
  name (e.g., Kampong Panchor in Mukim Mentiri and Kampong Panchor in
  Mukim Lumapas). Additional information from the listing was used to
  determine the correct match, but where this was not possible, these
  entries were also set to \texttt{NA}.
\end{enumerate}

This process was carried out manually using data filtering features in
Microsoft Excel. Once completed, all entries marked as \texttt{NA} were
removed so as to provide complete spatial information for each listing.

\subsection{Data Validation}\label{sec-data-validation}

To ensure data quality, a series of consistency and validity checks were
performed on the data set, especially after manual transcription and LLM
data cleaning. These checks include

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Outlier detection.} Summary statistics analyses to identify
  and flag anomalous values. For instance, a built-up area recorded as
  0.1 square feet or an implausibly high number of beds and baths (e.g.,
  \textgreater20) would highly likely indicate a possible error,
  prompting manual review. Such anomalies were flagged and manually
  reviewed for correction.
\item
  \textbf{Internal consistency checks.} This made use of substantive
  knowledge about Brunei's housing market
  \citep{jamil2025spatiotemporal}. An example is using the price per
  square foot indicator, whose value typically falls within a known
  range. Therefore any deviations were scrutinised to ensure that
  variables such as price and floor area were correctly recorded. This
  was similarly applied to other variables such as plot area, beds, and
  baths.
\item
  \textbf{Duplicate records detection.} We also performed duplicate
  record detection to identify any repeated entries that might have
  arisen from overlapping data sources or transcription errors. Any
  duplicates that were identified were carefully reviewed and removed to
  ensure that each property listing was uniquely represented in the span
  of one calendar month.
\end{enumerate}

These data validation procedures collectively contribute to a robust and
reliable data set, providing a solid foundation for subsequent analysis.

\section{Limitations}\label{limitations}

Listing prices in our data set serve as a proxy for market values,
capturing advertised trends rather than final sale outcomes. This
enables timely analysis of market sentiment, even though factors such as
negotiation dynamics, seller strategies, and market conditions may cause
deviations from actual transaction prices.

Despite significant efforts to ensure data quality, some limitations
remain. First, integrating historical data from manually transcribed
sources with later web-scraped data may introduce inconsistencies
affecting comparability over time. Second, although duplicate listings
were carefully reviewed and removed, there remains a slight possibility
of residual duplicates in the data set. Thirdly, while we have
confidence in the data quality from 2015 to 2024, property price trends
between 1993 and 2014 cannot be fully verified. Nonetheless, this study
serves as a valuable starting point. Future research could benefit
greatly from access to administrative transaction data, which would
allow for more comprehensive and accurate analyses.

Finally, while significant effort was made to harmonise spatial data,
the matching of kampong names to standardised references may not be
entirely error-free. However, aggregation to the mukim level provides a
reliable alternative for spatial analyses, ensuring that the data set
remains valuable for research and analysis.

\section{Ethics}\label{ethics}

The authors confirm that the current work does not involve human
subjects, animal experiments, or data collected from social media
platforms. The data described in this article were obtained from
publicly available, non-personal, and factual sources, including
physical and digital newspapers and magazines.

Web scraping from local property listings websites was conducted in
compliance with ethical and legal considerations. Specifically, data
were not collected from behind login barriers, and the terms of service
(ToS) for the websites did not explicitly prohibit web scraping.
Furthermore, the \texttt{robots.txt} files for the websites were
reviewed, and any policies outlined there were adhered to.

The data collected consisted exclusively of non-copyrightable factual
information, such as property characteristics and spatial locations, and
excluded any potentially copyrighted content such as images. To ensure
privacy, no personally identifiable information, including specific
property addresses, was scraped nor included in the data set. To this
end, data from the description fields processed by the LLM are not
included in the data set, as they may contain sensitive information such
as contact details and names of companies. Furthermore, we have
anonymised the names of the real estate agents and companies in the data
set.

\section{CRediT Author Statement}\label{credit-author-statement}

\begin{itemize}
\tightlist
\item
  \textbf{Haziq Jamil}: Conceptualisation, Methodology, Software, Formal
  analysis, Data curation, Writing-Original Draft, Visualisation,
  Supervision, Project administration, Funding acquisition.
\item
  \textbf{Amira Barizah Noorosmawie}: Software, Data curation,
  Writing-Original Draft.
\item
  \textbf{Hafeezul Waezz Rabu}: Software, Data curation,
  Writing-Original Draft.
\item
  \textbf{Lutfi Abdul Razak}: Conceptualisation, Validation,
  Supervision, Funding acquisition.
\end{itemize}

\section{Acknowledgements}\label{acknowledgements}

The authors gratefully acknowledge the contributions of Atikah Farhain
Yahya, Nurulhanisah Abdul Manan, and Nina Zuhairi towards the collection
and processing of the data contained within. We also thank the Brunei
Darussalam Central Bank (BDCB) for the engaging discussions and support,
which were instrumental in the initiation of this project.

\section{Declaration of Competing
Interests}\label{declaration-of-competing-interests}

The authors declare that they have no known competing financial
interests or personal relationships that could have appeared to
influence the work reported in this paper.

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\renewcommand{\bibsection}{}
\bibliography{refs-HJ.bib}

\section{Appendix}\label{appendix}

\subsection{Pairwise Correlation Plot of Numeric
Variables}\label{pairwise-correlation-plot-of-numeric-variables}

\begin{figure}[H]

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/notebooks-analysis-fig-corr-output-2.png}}

}

\caption{\label{fig-corr}Pairwise correlation plot of continuous
variables.}

\end{figure}%

\textsubscript{Source:
\href{https://Bruneiverse.github.io/house-data/notebooks/analysis-preview.html\#cell-fig-corr}{Plots
and Data Summaries}}

\subsection{Comparison to RPPI Data}\label{comparison-to-rppi-data}

To demonstrate the quality of the data set, we compared it with the
Residential Property Price Index (RPPI) \citep{bdcb2021technical}
published by the Brunei Darussalam Central Bank (BDCB). A simple median
price per square foot (PPSF) index can be calculated by aggregating the
data by quarters. This approach minimises the impact of missing values,
as the index is based on aggregated data. Figure~\ref{fig-rppi} shows
the comparison between the RPPI and the PPSF index calculated from our
data set. The mean absolute error (MAE) between the two indices is
calculated to be 4.71\%, indicating a good level of agreement between
the two data sets.

\begin{figure}[H]

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/notebooks-analysis-fig-rppi-output-1.png}}

}

\caption{\label{fig-rppi}Comparison of quarterly median price per square
foot indices (Median PPSF) and the official Residential Property Price
Index (RPPI) from Brunei Darussalam Central Bank (BDCB).}

\end{figure}%

\textsubscript{Source:
\href{https://Bruneiverse.github.io/house-data/notebooks/analysis-preview.html\#cell-fig-rppi}{Plots
and Data Summaries}}

\subsection{LLM Accuracy Test}\label{sec-apx-llm}

To test the accuracy of the LLM data extraction, we created a test data
set of 100 house advertisements in the style of the web scraped data.
Several popular models from Ollama were used, namely the Llama3.2 (3B),
Mistral (7B), Phi 4 (14B), and DeepSeek-R1 distilled reasoning models
based on Llama (8B) and Qwen (14B). For the locally run Ollama models,
the settings were set to the default values, with the exception of a
lowered temperature setting: \texttt{temperature\ =\ 0.1},
\texttt{top-p=0.9} (nucleus sampling), \texttt{top-k=40} (top-k
sampling), \texttt{max-tokens=128}, and \texttt{repeat-penalty=1.1}.
Additionally, two models from OpenAI were included for comparison. These
were the GPT-4o and the o1-mini, with the latter being a reasoning
model.

OpenAI's models topped the accuracy charts, with the o1-mini and gpt-4o
models achieving the accuracy scores of 99.2\% and 98.9\% respectively.
The reasoning model deepseek-r1:14b was the best performing locally run
model, scoring 96.9\% accuracy. Evidently, the smaller the model, the
less accurate the extraction process (cf.~llama3.2 70.8\%). Most
inaccuracies occurred in the \texttt{status} variable, where models
struggled to parse the correct build status from vague advertisement
descriptions. However, key variables such as \texttt{price},
\texttt{type}, \texttt{plot\_area}, \texttt{floor\_area}, \texttt{beds},
and \texttt{baths} are generally reliable (\textgreater90\% accuracy).

\begin{figure}[H]

\centering{

\pandocbounded{\includegraphics[keepaspectratio]{manuscript_files/figure-latex/notebooks-analysis-fig-llmtest-output-1.png}}

}

\caption{\label{fig-llmtest}Comparison of data extraction accuracy
across multiple LLM models on the test dataset. Each bar represents the
percentage of correctly extracted fields for a given model.}

\end{figure}%

\textsubscript{Source:
\href{https://Bruneiverse.github.io/house-data/notebooks/analysis-preview.html\#cell-fig-llmtest}{Plots
and Data Summaries}}

The run time statistics for each model is shown in the table below. The
computer used was a Mac Pro 3.2GHz 16 core Intel Xeon W with 48GB of
DDR4 RAM. At the time of running the tests, graphics card support was
not available for the LLM models, which would have significantly reduced
the run time. Certainly cloud-based models such as OpenAI's models are
much faster than running models locally, though a paid API key is
required.

\begin{table}

\caption{\label{tbl-llmtest-time}Single run time statistics for LLM data
extraction for each model in seconds.}

\centering{

\fontsize{12.0pt}{14.4pt}\selectfont
\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}}lrrrr}
\toprule
 & \multicolumn{4}{c}{Time (seconds)} \\ 
\cmidrule(lr){2-5}
Model & Minimum & Mean & Median & Maximum \\ 
\midrule\addlinespace[2.5pt]
llama3.2 & 1.08 & 6.40 & 9.60 & 10.16 \\ 
mistral & 2.66 & 10.44 & 2.91 & 22.21 \\ 
phi4 & 3.72 & 14.11 & 4.27 & 38.01 \\ 
deepseek-r1:8b & 36.83 & 65.97 & 54.61 & 112.78 \\ 
deepseek-r1:14b & 40.89 & 117.67 & 81.71 & 151.20 \\ 
gpt-4o & 1.28 & 2.46 & 1.73 & 5.38 \\ 
o1-mini & 5.97 & 7.95 & 7.51 & 9.94 \\ 
\bottomrule
\end{tabular*}

}

\end{table}%

\textsubscript{Source:
\href{https://Bruneiverse.github.io/house-data/manuscript.qmd.html}{Article
Notebook}}

\end{document}

### 2025-03-06 _cleanup.R

@@ -1,45 +1,0 @@
-# Cleanup script for Quarto
-files_to_remove <- list.files(
-  pattern = "\\.(bst|spl|cls|ipynb)$"
-)
-
-# Iterate over files and delete them if they exist
-for (file in files_to_remove) {
-  if (file.exists(file)) {
-    file.remove(file)
-    cat("Deleted:", file, "\n")
-  } else {
-    cat("File not found:", file, "\n")
-  }
-}
-
-# Fix the alignment of tfoot in the Quarto-generated HTML
-
-# Path to the HTML file
-html_file <- "docs/index.html"
-
-# Check if the file exists
-if (file.exists(html_file)) {
-  # Read the file content
-  html_content <- readLines(html_file)
-  
-  # Locate the line with <tfoot class="gt_footnotes">
-  html_content <- gsub(
-    pattern = '<tfoot class="gt_footnotes">',
-    replacement = '<tfoot class="gt_footnotes" style="text-align: left;">',
-    x = html_content
-  )
-  
-  # Write the updated content back to the file
-  writeLines(html_content, html_file)
-  cat("Updated text alignment in:", html_file, "\n")
-} else {
-  cat("File not found:", html_file, "\n")
-}
-
-# Copy over the docx manuscript
-source_file <- "_submission/Revision 1/article_rev1.docx"
-destination_file <- "docs/jamil2025archives.docx"
-
-# Copy the file, replacing the destination if it exists
-file.copy(source_file, destination_file, overwrite = TRUE)

### 2025-03-06 notebooks/data.R

@@ -1,79 +1,0 @@
-library(tidyverse)
-library(bruneimap)
-library(gt)
-library(gtsummary)
-library(lubridate)
-library(GGally)
-here::i_am("notebooks/data.R")
-
-# Main data set
-hsp <- 
-  read_csv(here::here("data/hspbn_2025-03-03.csv")) |>
-  mutate(
-    type = factor(type, levels = c("Detached", "Semi-Detached", "Terrace",
-                                   "Apartment", "Land")),
-    tenure = factor(tenure, levels = c("Freehold", "Leasehold", "Strata")),
-    status = factor(status, levels = c("Proposed", "Under Construction", "New", "Resale")),
-    date = as.Date(date, format = "%d/%m/%y"),
-    quarter = zoo::as.yearqtr(quarter)
-  )
-
-# RPPI from BDCB
-rppi <- 
-  read_csv(here::here("data/rppi.csv")) |>
-  mutate(
-    quarter = zoo::as.yearqtr(quarter),
-    rppi = rppi / 100
-  )
-
-# To create median price per square foot, need to filter out "Land" types as
-# well as missing property types. Then create an "Overall" type.
-hsp_all <- 
-  bind_rows(
-    hsp, 
-    mutate(hsp, type = "Overall")
-  ) |> 
-  arrange(date) 
-
-# Create a median price per square foot index
-hsp_rppi <-
-  slider::slide_period_dfr(hsp, hsp$date, "month", \(df) {
-    df |>
-      filter(type != "Land") |>
-      drop_na(floor_area) |>
-      summarise(
-        quarter = first(quarter),
-        price = median(price, na.rm = TRUE),
-        # plot_area = median(plot_area, na.rm = TRUE),
-        floor_area = median(floor_area, na.rm = TRUE)
-      )
-  }, .before = 1, .after = 1) |>
-  summarise(across(price:floor_area, \(x) median(x, na.rm = TRUE)), .by = quarter) |> 
-  drop_na(quarter) |>
-  mutate(
-    price_per_sqft = price / floor_area,
-    index = price_per_sqft / price_per_sqft[quarter == "2015 Q1"],
-  ) |>
-  right_join(rppi, by = join_by(quarter)) 
-
-rppi_mae <-
-  hsp_rppi |>
-  summarise(
-    rmse = (mean( abs(rppi - index) ^ 1)),
[…]

### 2025-03-06 _cleanup.R
Update gitignore

@@ -16,7 +16,7 @@ for (file in files_to_remove) {
 # Fix the alignment of tfoot in the Quarto-generated HTML
 
 # Path to the HTML file
-html_file <- "docs/index.html"
+html_file <- "_manuscript/index.html"
 
 # Check if the file exists
 if (file.exists(html_file)) {
@@ -39,7 +39,7 @@ if (file.exists(html_file)) {
 
 # Copy over the docx manuscript
 source_file <- "_submission/Revision 1/article_rev1.docx"
-destination_file <- "docs/jamil2025archives.docx"
+destination_file <- "_manuscript/jamil2025archives.docx"
 
 # Copy the file, replacing the destination if it exists
 file.copy(source_file, destination_file, overwrite = TRUE)

### 2025-03-06 _cleanup.R
Update _cleanup.R

@@ -1,6 +1,6 @@
 # Cleanup script for Quarto
 files_to_remove <- list.files(
-  pattern = "\\.(bst|spl|cls|ipynb)$"
+  pattern = "\\.(bst|spl|cls|ipynb|DS_Store)$"
 )
 
 # Iterate over files and delete them if they exist

### 2025-03-06 experiments/llmtest.R
Create llmtest.R

@@ -1,0 +1,300 @@
+library(tidyverse)
+library(microbenchmark)
+library(ellmer)
+library(stringdist)
+set.seed(123) 
+hsp_test <- read_csv("experiments/llmtest.csv") 
+
+## ----- The prompt ------------------------------------------------------------
+# the_prompt <- "
+# The following is the description from a property sale listing in Brunei. This description will contain the information about the property, including its characteristics, price, and location. However, some of these descriptions may not contain property listings, and instead contain other or no information at all.
+# 
+# In the case where this description is in fact a property listing, I would like you to extract the following information:
+# 
+# 1. Location / area of the property in Brunei, CHARACTER.
+# 2. Price of the property in Brunei Dollars, NUMERIC.
+# 3. Type of property, CHARACTER -- select from Detached, Semi-Detached, Terrace, Apartment, or Land.
+# 4. Land tenure, CHARACTER -- select from Freehold, Leasehold, or Strata. If other than this, return 'NA'.
+# 5. Status of the property, CHARACTER -- select from Proposed, Under Construction, New, or Resale.
+# 6. Land area in acres, NUMERIC.
+# 7. Built up area in square feet, NUMERIC.
+# 8. Number of storeys, INTEGER.
+# 9. Number of bedrooms, INTEGER.
+# 10. Number of bathrooms, INTEGER.
+# 
+# Further instructions:
+# 
+# - Please return **semicolon** separated values like this:
+# 
+#   Kg Tanah Jambu; 250000; Detached; Freehold; New; 0.3; 2500; 2;  3; 3
+#   Kg Tungku; 300000; Terrace; Leasehold; Resale; 0.25; 1700; 2;  3; 2
+#   Kg Kiarong; 200000; Apartment; Strata; Proposed; 0.1; 1000; NA; 2; 2
+#   etc.
+#   NUMBERS SHOULD NOT CONTAIN comma (,) for thousands separator
+# 
+# - If any of the 10 values are missing, please return 'NA' for that value.
+# 
+# - If the description does not contain a property listing (for example, it is a rental property advertisement), return 'NA' for all 10 values.
+# 
+# - DO NOT RESPOND WITH ANYTHING ELSE OTHER THAN THE REQUIRED INFORMATION.
+# 
[…]

### 2025-03-06 manuscript.qmd
Built site for gh-pages

@@
   - name: Hafeezul Waezz Rabu
+    orcid: 0009-0008-0937-0071
     affiliations:

### 2025-03-25 _cleanup.R
Minor revision grammar

@@ -38,8 +38,6 @@ if (file.exists(html_file)) {
 }
 
 # Copy over the docx manuscript
-source_file <- "_submission/Revision 1/article_rev1.docx"
-destination_file <- "_manuscript/jamil2025archives.docx"
-
-# Copy the file, replacing the destination if it exists
-file.copy(source_file, destination_file, overwrite = TRUE)
+# source_file <- "_submission/Revision 1/article_rev1.docx"
+# destination_file <- "_manuscript/jamil2025archives.docx"
+# file.copy(source_file, destination_file, overwrite = TRUE)

### 2025-03-25 _tex/manuscript.tex
Built site for gh-pages

@@
 manual transcription from archival sources and automated web scraping
-using programmatic methods, supported by innovative processing with
+using programmatic techniques, supported by innovative processing with
 Large Language Models (LLMs) to codify unstructured text. The data set
@@
   AI-based data cleaning using Large Language Models (LLMs). This
-  multi-method approach offers a reproducible framework for assembling
+  multimethod approach offers a reproducible framework for assembling
   complex data sets, which can be adapted for similar data collection
-  efforts in other domains, thereby advancing best practices in the
+  efforts in other domains, thereby advancing best practices within the
   field.
@@
 \textsubscript{Source:
-\href{https://Bruneiverse.github.io/house-data/manuscript.qmd.html}{Article
+\href{https://Bruneiverse.github.io/house-data/manuscript-preview.html}{Article
 Notebook}}
@@
 section clarifies and provides context for the key variables in the data
-set.
+set. A summary of the property characteristics is presented in
+Table~\ref{tbl-summary}.
 
@@
 can be classified into three main categories: Freehold (in perpetuity),
-Leasehold, and Strata. The latter two refer to a limited time-limited
-ownership, although details about the remaining duration of the tenure
-are almost never included in property listings. Strata titles differ
-from Leasehold titles in that they grant ownership of a specific portion
-of a property, such as an apartment, while sharing ownership of common
-areas.
+Leasehold, and Strata. The latter two refer to a time-limited ownership,
+although details about the remaining duration of the tenure are almost
+never included in property listings. Strata titles differ from Leasehold
+titles in that they grant ownership of a specific portion of a property,
+such as an apartment, while sharing ownership of common areas.
 
@@
 
-Finally, metadata about the property is included for transparency and
-informational purposes. The variable \texttt{agent} specifies the
-(anonymised) identifier of the real estate agent or agency responsible
-for the listing, while \texttt{source} identifies the platform or medium
-from which the listing was obtained, such as a newspaper, magazine, or
-website. The \texttt{method} variable details the data collection
-approach, which is further elaborated in the section below.
+Finally, metadata regarding each property are also included. The
+variable \texttt{agent} specifies the (anonymised) identifier of the
+real estate agent or agency responsible for the listing, while
+\texttt{source} identifies the platform or medium from which the listing
+was obtained, such as a newspaper, magazine, or website. The
+\texttt{method} variable details the data collection approach, which is
+further elaborated in the section below.
 
@@
 together form a \emph{mukim}, which serves as a sub-district
-administrative area. Finally, multiple mukims are nested within a
-\emph{district}, the largest administrative unit, of which Brunei has
-four: Brunei-Muara, Belait, Tutong, and Temburong. In our data set, each
-property listing is associated with a specific kampong, mukim, and
-district, allowing for spatial analysis at different scales.
+administrative area (see Figure~\ref{fig-spatial}). Finally, multiple
+mukims are nested within a \emph{district}, the largest administrative
+unit, of which Brunei has four: Brunei-Muara, Belait, Tutong, and
+Temburong. In our data set, each property listing is associated with a
+distinct kampong, mukim, and district, allowing for spatial analysis at
+different scales.
 
@@
 harmonised with a standardised naming convention to ensure consistency
-across the data set. This also allows for ease of integration into
+across the data set. This also allows for ease of integration with
 Geographic Information Systems (GIS) software for spatial analysis and
@@
 listing was obtained, rather than the date of sale or transaction, and
-should be interpreted as a snapshot of market conditions at a given
-point in time. For analysis, we recommend aggregating data by quarters,
-as represented by the \texttt{quarter} variable. This aggregation helps
-address potential issues like missing data (see subsection below) and
-provides a more stable and robust representation of market trends,
-making it suitable for temporal analysis of the housing market.
+should be interpreted as a snapshot of market conditions at a specific
+point in time. Figure~\ref{fig-price-evolution} illustrates the price
+evolution over time. For analysis, we recommend aggregating data by
+quarters, as represented by the \texttt{quarter} variable. This
+aggregation helps address potential issues like missing data (see
+subsection below) and provides a more stable and robust representation
+of market trends, making it suitable for temporal analysis of the
+housing market.
 
@@
 
-Missing values are represented by blank cells in the CSV file, and the
-severity of missingness is summarized in Table~\ref{tbl-avail}. In
-total, 10.1\% of the records contain missing values for all key house
+Missing values are represented by blank cells in the CSV file. The
+severity of missingness is summarised in Table~\ref{tbl-avail} and
+patterns visualised in Figure~\ref{fig-missing-pattern}. In total,
+10.1\% of the records contain missing values for all key house
 characteristics (i.e.~plot area, floor area, beds, and baths), which,
@@
 150 entries per week per person. Spreading the task over such an
-extended period ensured that transcribers were never under undue time
+extended period ensured that transcribers were never under time
 pressure, which could have led to errors due to fatigue.
@@
 of the physical newspapers, were obtained online. These digital formats
-could not be scraped due to their lack of structured data, necessitating
-manual transcription.
+were not structured in a way that allowed for automated scraping, hence
+the need for manual transcription.
 
@@
 
-Data from 2012 up until the present (January 2025) were managed to be
+Data from 2012 up until the present (February 2025) were managed to be
 collected using this method, averaging around 1,500 listings per year.
@@
 scripts. To overcome these issues, alternative approaches, such as using
-Large Language Models (LLMs) were considered. This is explained in the
+Large Language Models (LLMs), were considered. This is explained in the
 next subsection.
@@
 unstructured verbose descriptions scraped from property listing
-websites. Each description was processed with a carefully designed
-prompt (Figure~\ref{fig-llm-prompt}) to ensure consistent output. This
-prompt instructed the model to return only the required information in a
+websites. Each description was processed with a carefully crafted prompt
+(Figure~\ref{fig-llm-prompt}) to ensure consistent output. This prompt
+instructed the model to return only the required information in a
 semicolon-separated format, while handling edge cases such as missing
@@
 using this method, with a run time of approximately 20 hours in total
-(spread over three machines).
+spread over three machines.
 
@@
 \texttt{status} classification, likely due to the vagueness of the
-advertisement listing. As for the rest of the variables, obvious errors
+advertisement listing. As for the rest of the variables, clear errors
 were flagged and corrected manually during our data validation process
@@
 \item
-  Spelling variations or misspellings, though these were relatively
+  Spelling variations and misspellings, though these were relatively
   straightforward to correct.
@@
 Microsoft Excel. Once completed, all entries marked as \texttt{NA} were
-removed so as to provide complete spatial information for each listing.
+removed so as to provide complete spatial coverage for the data set.
 
@@
 performed on the data set, especially after manual transcription and LLM
-data cleaning. These checks include
+data cleaning. These checks include:
 
@@
 \item
-  \textbf{Outlier detection.} Summary statistics analyses to identify
-  and flag anomalous values. For instance, a built-up area recorded as
-  0.1 square feet or an implausibly high number of beds and baths (e.g.,
-  \textgreater20) would highly likely indicate a possible error,
-  prompting manual review. Such anomalies were flagged and manually
-  reviewed for correction.
+  \textbf{Outlier detection.} Statistical summaries were analysed to
+  identify and flag anomalous values. For instance, a built-up area
+  recorded as 0.1 square feet or an implausibly high number of beds and
+  baths (e.g., \textgreater20) would likely indicate an error, prompting
+  review. Such anomalies were flagged and manually reviewed for
+  correction.
 \item
@@
 
-\section{Limitations}\label{limitations}
+\section*{Limitations}\label{limitations}
+\addcontentsline{toc}{section}{Limitations}
 
 Listing prices in our data set serve as a proxy for market values,
-capturing advertised trends rather than final sale outcomes. This
-enables timely analysis of market sentiment, even though factors such as
-negotiation dynamics, seller strategies, and market conditions may cause
-deviations from actual transaction prices.
+capturing advertised trends rather than final sale outcomes. While this
+allows for timely analysis of market sentiment, actual transaction
+prices may differ due to negotiation dynamics, seller strategies, and
+broader market conditions.
 
@@
 remain. First, integrating historical data from manually transcribed
-sources with later web-scraped data may introduce inconsistencies
-affecting comparability over time. Second, although duplicate listings
-were carefully reviewed and removed, there remains a slight possibility
-of residual duplicates in the data set. Thirdly, while we have
-confidence in the data quality from 2015 to 2024, property price trends
-between 1993 and 2014 cannot be fully verified. Nonetheless, this study
-serves as a valuable starting point. Future research could benefit
-greatly from access to administrative transaction data, which would
-allow for more comprehensive and accurate analyses.
+sources with later web-scraped data may introduce inconsistencies,
+potentially affecting comparability over time. Second, although
+duplicate listings were carefully reviewed and removed, there remains a
+slight possibility of residual duplicates within the data set. Thirdly,
+while we have confidence in the data quality from 2015 to 2024, property
+price trends between 1993 and 2014 cannot be fully verified.
+Nonetheless, this study serves as a valuable starting point. Future
+research could benefit greatly from access to administrative transaction
+data, which would allow for more comprehensive and accurate analyses.
 
 Finally, while significant effort was made to harmonise spatial data,
-the matching of kampong names to standardised references may not be
-entirely error-free. However, aggregation to the mukim level provides a
-reliable alternative for spatial analyses, ensuring that the data set
-remains valuable for research and analysis.
-
-\section{Ethics}\label{ethics}
+matching kampong names to standardised references may not be entirely
+error-free. However, aggregation to the mukim level provides a reliable
+alternative for spatial analyses, ensuring that the data set remains
+valuable for research and analysis.
+
+\section*{Ethics}\label{ethics}
+\addcontentsline{toc}{section}{Ethics}
 
@@
 included in the data set, as they may contain sensitive information such
-as contact details and names of companies. Furthermore, we have
-anonymised the names of the real estate agents and companies in the data
-set.
-
-\section{CRediT Author Statement}\label{credit-author-statement}
+as contact details and company names. The names of real estate agents
+and companies have been anonymised to ensure privacy.
+
+\section*{CRediT Author Statement}\label{credit-author-statement}
+\addcontentsline{toc}{section}{CRediT Author Statement}
 
@@
 
-\section{Acknowledgements}\label{acknowledgements}
+\section*{Acknowledgements}\label{acknowledgements}
+\addcontentsline{toc}{section}{Acknowledgements}
 
 The authors gratefully acknowledge the contributions of Atikah Farhain
-Yahya, Nurulhanisah Abdul Manan, and Nina Zuhairi towards the collection
-and processing of the data contained within. We also thank the Brunei
-Darussalam Central Bank (BDCB) for the engaging discussions and support,
-which were instrumental in the initiation of this project.
-
-\section{Declaration of Competing
+Yahya, Nurulhanisah Abdul Manan, and Nina Zuhairi for their assistance
+in collecting and processing the data presented in this study. The
+authors also extend their thanks to the Brunei Darussalam Central Bank
+(BDCB) for engaging discussions and valuable support, which were
+instrumental in initiating this project.
+
+\section*{Declaration of Competing
 Interests}\label{declaration-of-competing-interests}
+\addcontentsline{toc}{section}{Declaration of Competing Interests}
 
@@
 
-\section{Appendix}\label{appendix}
+\section*{Appendix}\label{appendix}
+\addcontentsline{toc}{section}{Appendix}
 
@@
 Variables}\label{pairwise-correlation-plot-of-numeric-variables}
+
+Figure~\ref{fig-corr} shows the pairwise correlation plot of the numeric
+variables in the data set.
 
@@
 
-\subsection{Comparison to RPPI Data}\label{comparison-to-rppi-data}
+\subsection*{Comparison to RPPI Data}\label{comparison-to-rppi-data}
+\addcontentsline{toc}{subsection}{Comparison to RPPI Data}
 
@@
 
-\subsection{LLM Accuracy Test}\label{sec-apx-llm}
+\subsection*{LLM Accuracy Test}\label{llm-accuracy-test}
+\addcontentsline{toc}{subsection}{LLM Accuracy Test}
 
@@
 
-OpenAI's models topped the accuracy charts, with the o1-mini and gpt-4o
-models achieving the accuracy scores of 99.2\% and 98.9\% respectively.
-The reasoning model deepseek-r1:14b was the best performing locally run
-model, scoring 96.9\% accuracy. Evidently, the smaller the model, the
-less accurate the extraction process (cf.~llama3.2 70.8\%). Most
-inaccuracies occurred in the \texttt{status} variable, where models
-struggled to parse the correct build status from vague advertisement
-descriptions. However, key variables such as \texttt{price},
-\texttt{type}, \texttt{plot\_area}, \texttt{floor\_area}, \texttt{beds},
-and \texttt{baths} are generally reliable (\textgreater90\% accuracy).
+Figure~\ref{fig-llmtest} and Table~\ref{tbl-llmtest-time} show the
+accuracy results for each model. OpenAI's models topped the accuracy
+charts, with the o1-mini and gpt-4o models achieving the accuracy scores
+of 99.2\% and 98.9\% respectively. The reasoning model deepseek-r1:14b
+was the best performing locally run model, scoring 96.9\% accuracy.
+Evidently, the smaller the model, the less accurate the extraction
+process (cf.~llama3.2 70.8\%). Most inaccuracies occurred in the
+\texttt{status} variable, where models struggled to parse the correct
+build status from vague advertisement descriptions. However, key
+variables such as \texttt{price}, \texttt{type}, \texttt{plot\_area},
+\texttt{floor\_area}, \texttt{beds}, and \texttt{baths} are generally
+reliable (\textgreater90\% accuracy).
 

### 2025-03-25 manuscript.qmd
Built site for gh-pages

--- 2025-03-06 manuscript.qmd
@@
         postal-code: BE 1410
-  - name: Amira Barizah Noorosmawie
+  - name:
+      given: Amira Barizah
+      family: Noorosmawie
+    orcid: 0009-0008-9334-7615
     affiliations:
       - ref: ubd        
-  - name: Hafeezul Waezz Rabu
+  - name: 
+      given: Hafeezul Waezz
+      family: Rabu
+    orcid: 0009-0008-0937-0071
     affiliations:
       - ref: ubd
-  - name: Lutfi Abdul Razak
+  - name:
+      given: Lutfi
+      family: Abdul Razak
     orcid: 0000-0003-1681-0895
@@
         postal-code: BE 1410         
+date: 2025-03-23
 date-modified: last-modified
@@
 Comprehensive and historical, it complements the Brunei Darussalam Central Bank’s Residential Property Price Index (RPPI), addressing the limitations of restricted access to raw RPPI data and its relatively short timeline since its inception in 2015.
-Data collection involved manual transcription from archival sources and automated web scraping using programmatic methods, supported by innovative processing with Large Language Models (LLMs) to codify unstructured text.
+Data collection involved manual transcription from archival sources and automated web scraping using programmatic techniques, supported by innovative processing with Large Language Models (LLMs) to codify unstructured text.
 The data set enables spatial and temporal analysis, with potential applications in economics, urban planning, and real estate research.
@@
 The data collection process employs a unique combination of manual transcription from archival sources, automated web scraping, and AI-based data cleaning using Large Language Models (LLMs).
-This multi-method approach offers a reproducible framework for assembling complex data sets, which can be adapted for similar data collection efforts in other domains, thereby advancing best practices in the field.
+This multimethod approach offers a reproducible framework for assembling complex data sets, which can be adapted for similar data collection efforts in other domains, thereby advancing best practices within the field.
 
@@
 This section clarifies and provides context for the key variables in the data set.
+A summary of the property characteristics is presented in @tbl-summary.
 
@@
 In Brunei, property tenure can be classified into three main categories: Freehold (in perpetuity), Leasehold, and Strata. 
-The latter two refer to a limited time-limited ownership, although details about the remaining duration of the tenure are almost never included in property listings. 
+The latter two refer to a time-limited ownership, although details about the remaining duration of the tenure are almost never included in property listings. 
 Strata titles differ from Leasehold titles in that they grant ownership of a specific portion of a property, such as an apartment, while sharing ownership of common areas.
@@
 
-Finally, metadata about the property is included for transparency and informational purposes. 
+Finally, metadata regarding each property are also included. 
 The variable `agent` specifies the (anonymised) identifier of the real estate agent or agency responsible for the listing, while `source` identifies the platform or medium from which the listing was obtained, such as a newspaper, magazine, or website.
@@
 While a typical village refers to a traditional rural settlement, it is also used to describe an urbanised area located within or near the capital city or a town. 
-It may even refer to a part of public housing estates. Several kampongs grouped together form a *mukim*, which serves as a sub-district administrative area. 
+It may even refer to a part of public housing estates. Several kampongs grouped together form a *mukim*, which serves as a sub-district administrative area (see @fig-spatial). 
 Finally, multiple mukims are nested within a *district*, the largest administrative unit, of which Brunei has four:
 Brunei-Muara, Belait, Tutong, and Temburong. 
-In our data set, each property listing is associated with a specific kampong, mukim, and district, allowing for spatial analysis at different scales.
+In our data set, each property listing is associated with a distinct kampong, mukim, and district, allowing for spatial analysis at different scales.
 
 Importantly, the names of the kampongs, mukims, and districts have been harmonised with a standardised naming convention to ensure consistency across the data set. 
-This also allows for ease of integration into Geographic Information Systems (GIS) software for spatial analysis and visualisation, namely the `{bruneimap}` R package [@jamil2024bruneimap].
+This also allows for ease of integration with Geographic Information Systems (GIS) software for spatial analysis and visualisation, namely the `{bruneimap}` R package [@jamil2024bruneimap].
 
@@
 
-The `date` variable represents the date on which the property listing was obtained, rather than the date of sale or transaction, and should be interpreted as a snapshot of market conditions at a given point in time.
+The `date` variable represents the date on which the property listing was obtained, rather than the date of sale or transaction, and should be interpreted as a snapshot of market conditions at a specific point in time.
+@fig-price-evolution illustrates the price evolution over time.
 For analysis, we recommend aggregating data by quarters, as represented by the `quarter` variable. 
@@
 
-Missing values are represented by blank cells in the CSV file, and the severity of missingness is summarized in @tbl-avail. 
+Missing values are represented by blank cells in the CSV file. 
+The severity of missingness is summarised in @tbl-avail and patterns visualised in @fig-missing-pattern. 
 In total, 10.1% of the records contain missing values for all key house characteristics (i.e.
@@
 A total of `{r} scales::comma(sum(hsp$method %in% c("nat-archive", "online-archive")))` data points were collected in this manner, which translates to processing approximately 150 entries per week per person.
-Spreading the task over such an extended period ensured that transcribers were never under undue time pressure, which could have led to errors due to fatigue.
+Spreading the task over such an extended period ensured that transcribers were never under time pressure, which could have led to errors due to fatigue.
 
@@
 Physical copies were accessed through the National Archive of Brunei Darussalam, while digital versions, which are digitised replicas of the physical newspapers, were obtained online. 
-These digital formats could not be scraped due to their lack of structured data, necessitating manual transcription.
+These digital formats were not structured in a way that allowed for automated scraping, hence the need for manual transcription.
 
@@
 
-Data from 2012 up until the present (January 2025) were managed to be collected using this method, averaging around 1,500 listings per year. 
+Data from 2012 up until the present (February 2025) were managed to be collected using this method, averaging around 1,500 listings per year. 
 While highly efficient, this process relied heavily on the consistency of the site structure of the source webpages.
 Changes to website layouts or closures over time required significant updates to the scraping scripts.
-To overcome these issues, alternative approaches, such as using Large Language Models (LLMs) were considered. 
+To overcome these issues, alternative approaches, such as using Large Language Models (LLMs), were considered. 
 This is explained in the next subsection.
@@
 The primary goal was to extract the house characteristics of interest, specifically variables 7 to 15 as per @tbl-codebook, from the unstructured verbose descriptions scraped from property listing websites.
-Each description was processed with a carefully designed prompt (@fig-llm-prompt) to ensure consistent output. 
+Each description was processed with a carefully crafted prompt (@fig-llm-prompt) to ensure consistent output. 
 This prompt instructed the model to return only the required information in a semicolon-separated format, while handling edge cases such as missing descriptions or non-residential (commercial) properties.
@@
 It takes, on average, 81.7 seconds to process a single description using a Mac Pro 3.2GHz 16 core Intel Xeon W with 48GB of DDR4 RAM.
-We processed `{r} scales::comma(sum(hsp$method %in% c("web-scrape-llm")))` descriptions from 2020 to 2025 using this method, with a run time of approximately 20 hours in total (spread over three machines).
+We processed `{r} scales::comma(sum(hsp$method %in% c("web-scrape-llm")))` descriptions from 2020 to 2025 using this method, with a run time of approximately 20 hours in total spread over three machines.
 
@@
 Errors mostly stemmed from incorrect `status` classification, likely due to the vagueness of the advertisement listing.
-As for the rest of the variables, obvious errors were flagged and corrected manually during our data validation process (described in the subsection following the next one).
+As for the rest of the variables, clear errors were flagged and corrected manually during our data validation process (described in the subsection following the next one).
 Overall, the LLM was found to be a valuable tool for extracting structured information from unstructured text, significantly reducing the time and effort required for data extraction. 
@@
 
-1. Spelling variations or misspellings, though these were relatively straightforward to correct.
+1. Spelling variations and misspellings, though these were relatively straightforward to correct.
 2. Unknown entries, where the correct kampong could sometimes be inferred from the geographical context; otherwise, these were set to `NA`.
@@
 This process was carried out manually using data filtering features in Microsoft Excel. 
-Once completed, all entries marked as `NA` were removed so as to provide complete spatial information for each listing.
+Once completed, all entries marked as `NA` were removed so as to provide complete spatial coverage for the data set.
 
@@
 To ensure data quality, a series of consistency and validity checks were performed on the data set, especially after manual transcription and LLM data cleaning.
-These checks include
+These checks include:
 
 1.
-**Outlier detection.** Summary statistics analyses to identify and flag anomalous values.
-For instance, a built-up area recorded as 0.1 square feet or an implausibly high number of beds and baths (e.g., >20) would highly likely indicate a possible error, prompting manual review.
+**Outlier detection.** Statistical summaries were analysed to identify and flag anomalous values.
+For instance, a built-up area recorded as 0.1 square feet or an implausibly high number of beds and baths (e.g., >20) would likely indicate an error, prompting review.
 Such anomalies were flagged and manually reviewed for correction.
@@
 
-# Limitations
+# Limitations {.unnumbered}
 
@@
 Listing prices in our data set serve as a proxy for market values, capturing advertised trends rather than final sale outcomes. 
-This enables timely analysis of market sentiment, even though factors such as negotiation dynamics, seller strategies, and market conditions may cause deviations from actual transaction prices.
+While this allows for timely analysis of market sentiment, actual transaction prices may differ due to negotiation dynamics, seller strategies, and broader market conditions.
 
 Despite significant efforts to ensure data quality, some limitations remain. 
-First, integrating historical data from manually transcribed sources with later web-scraped data may introduce inconsistencies affecting comparability over time. 
-Second, although duplicate listings were carefully reviewed and removed, there remains a slight possibility of residual duplicates in the data set.
+First, integrating historical data from manually transcribed sources with later web-scraped data may introduce inconsistencies, potentially affecting comparability over time. 
+Second, although duplicate listings were carefully reviewed and removed, there remains a slight possibility of residual duplicates within the data set.
 <!-- Thirdly, the spatial distribution is heavily skewed toward the Brunei-Muara district--reflecting its higher population and transaction volume [@jamil2025spatiotemporal]--which may bias regional analyses.
@@
 
-Finally, while significant effort was made to harmonise spatial data, the matching of kampong names to standardised references may not be entirely error-free. 
+Finally, while significant effort was made to harmonise spatial data, matching kampong names to standardised references may not be entirely error-free. 
 However, aggregation to the mukim level provides a reliable alternative for spatial analyses, ensuring that the data set remains valuable for research and analysis.
 
-# Ethics
+# Ethics {.unnumbered}
 
@@
 To ensure privacy, no personally identifiable information, including specific property addresses, was scraped nor included in the data set. 
-To this end, data from the description fields processed by the LLM are not included in the data set, as they may contain sensitive information such as contact details and names of companies. 
-Furthermore, we have anonymised the names of the real estate agents and companies in the data set.
+To this end, data from the description fields processed by the LLM are not included in the data set, as they may contain sensitive information such as contact details and company names. 
+The names of real estate agents and companies have been anonymised to ensure privacy.
 
-# CRediT Author Statement
+# CRediT Author Statement {.unnumbered}
 
@@
 
-# Acknowledgements
+# Acknowledgements {.unnumbered}
 
@@
 
-The authors gratefully acknowledge the contributions of Atikah Farhain Yahya, Nurulhanisah Abdul Manan, and Nina Zuhairi towards the collection and processing of the data contained within.
-We also thank the Brunei Darussalam Central Bank (BDCB) for the engaging discussions and support, which were instrumental in the initiation of this project.
+The authors gratefully acknowledge the contributions of Atikah Farhain Yahya, Nurulhanisah Abdul Manan, and Nina Zuhairi for their assistance in collecting and processing the data presented in this study.
+The authors also extend their thanks to the Brunei Darussalam Central Bank (BDCB) for engaging discussions and valuable support, which were instrumental in initiating this project.
 
-# Declaration of Competing Interests
+# Declaration of Competing Interests {.unnumbered}
 
@@
 
-# Appendix {.unnunmbered}
+# Appendix {.unnumbered}
 
-## Pairwise Correlation Plot of Numeric Variables
+## Pairwise Correlation Plot of Numeric Variables {.unnunmbered}
+
+@fig-corr shows the pairwise correlation plot of the numeric variables in the data set.
 
@@
 
-## Comparison to RPPI Data
+## Comparison to RPPI Data {.unnumbered}
 
@@
 
-## LLM Accuracy Test {#sec-apx-llm}
+## LLM Accuracy Test {.unnumbered}
 
@@
 
+@fig-llmtest and @tbl-llmtest-time show the accuracy results for each model.
 OpenAI's models topped the accuracy charts, with the o1-mini and gpt-4o models achieving the accuracy scores of 99.2% and 98.9% respectively.
@@
 #| tbl-cap: Single run time statistics for LLM data extraction for each model in seconds.
+#| html-table-processing: none
 llmtest_time <-

### 2025-03-25 _extensions/quarto-journals/elsevier/partials/before-body.tex
Update pdf with url and citation

\begin{frontmatter}
\title{$title$$if(subtitle)$ \\\large{$subtitle$} $endif$}
$for(by-author)$\author[$for(by-author.affiliations)$$it.number$$sep$,$endfor$]{$by-author.name.literal$%
$if(by-author.attributes.corresponding)$\corref{cor1}$endif$%
$if(by-author.note.text)$\fnref{fn$by-author.note.number$}$endif$}
$if(by-author.email)$ \ead{$by-author.email$} $endif$
$endfor$
$for(by-affiliation)$
\affiliation[$it.number$]{organization={$it.name$$if(it.department)$, $it.department$$endif$},$if(it.address)$addressline={$it.address$}$endif$$if(it.city)$$if(it.address)$,$endif$city={$it.city$}$endif$$if(it.country)$$if(it.city)$,$elseif(it.address)$,$endif$country={$it.country$},countrysep={,}$endif$$if(it.postal-code)$$if(it.country)$,$elseif(it.city)$,$elseif(it.address)$,$endif$postcode={$it.postal-code$}$endif$,postcodesep={}}
$endfor$

\cortext[cor1]{Corresponding author}
$for(by-author)$
$if(by-author.note.text)$\fntext[fn$by-author.note.number$]{$by-author.note.text$}$endif$
$endfor$

% Add manuscript URL
$if(manuscript-url)$
\makeatletter
\def\@elsuads{\url{$manuscript-url$}}
\makeatother
$endif$

$if(abstract)$
\begin{abstract}
$abstract$
\end{abstract}
$endif$

$if(journal.graphical-abstract)$\begin{graphicalabstract}
$journal.graphical-abstract$
\end{graphicalabstract}
$endif$

$if(journal.highlights)$\begin{highlights}
$for(journal.highlights)$\item $it$$endfor$
\end{highlights}
$endif$

$if(keywords)$
\begin{keyword}
    $for(keywords/allbutlast)$$keywords$ \sep $endfor$
    $for(keywords/last)$$keywords$$endfor$
\end{keyword}
$endif$
\end{frontmatter}

### 2025-03-25 manuscript.qmd
Built site for gh-pages

@@
   - Large Language Models
+manuscript-url: https://bruneiverse.github.io/house-data
 editor_options: 
@@
 -->
+
+::: {.content-visible when-format="pdf"}
+
+# Citation
+
+For attribution, please cite this work as:
+
+> H.
+Jamil, A.B.
+Noorosmawie, H.W.
+Rabu, L.
+Abdul Razak, From Archives to AI: Residential Property Data Across Three Decades in Brunei Darussalam, Data in Brief (2025).
+<https://doi.org/10.1016/j.dib.2025.111505>.
+
+:::
 
